### 2018-01-04 _region_.tex
update readme

\message{ !name(<none>.tex)}
\message{ !name(<none>) !offset(27) }

\tableofcontents

\section{Each colom represent mean}
\label{sec:org0470bc1}
\begin{center}
\begin{tabular}{lll}
Column & Mean & remark\\
\hline
F (6) & ranking & \\
G (7) & Chinese origin data & \\
H (8) & Google translated data & \\
I (9) & Baidu Chinese sentiment analysis positive probability & base on Chinese origin data\\
J (10) & Baidu Chinese sentiment analysis confidence & base on Chinese origin data\\
K (11) & Baidu Chinese sentiment analysis Negative probability & base on Chinese origin data\\
L (12) & Baidu Chinese sentiment analysis the category & base on Chinese origin data\\
M (13) & Baidu English sentiment analysis positive probability & base on Google translated data\\
N (14) & Baidu English sentiment analysis confidence & base on Google translated data\\
O (15) & Baidu English sentiment analysis Negative probability & base on Google translated data\\
P (16) & Baidu English sentiment analysis the category & base on Google translated data\\
Q (17) & Google Chinese sentiment analysis score & base on Chinese origin data\\
R (18) & Google Chinese sentiment analysis manitude & base on Chinese origin data\\
S (19) & Google English sentiment analysis score & base on Google translated data\\
T (20) & Google English sentiment analysis manitude & base on Google translated data\\
U (21) & Yandex translated data & base on Chinese origin data\\
V (22) & Google English sentiment analysis score & base on Yandex translated data\\
W (23) & Google English sentiment analysis manitude & base on Yandex translated data\\
X (24) & Baidu translated data & \\
Y (25) & Google English sentiment analysis score & base on Baidu translated data\\
Z (26) & Google English sentiment analysis manitude & base on Baidu translated data\\
AA (27) & Baidu English sentiment analysis postitive probability & base on baidu translated data\\
AB (28) & Baidu English sentiment analysis confidence & base on baidu translated data\\
AC (29) & Baidu English sentiment analysis Negative probability & base on baidu translated data\\
AD (30) & Baidu English sentiment analysis the category & base on baidu translated data\\
AE (31) & Baidu postitive probability change to Google score standard & base on origin data Baidu sentiment analysis\\
AF (32) & Baidu postitive probability tranform to Google score standard & base on column M\\
\end{tabular}
\end{center}

\subsection{note}
\label{sec:orgbc09a97}
\begin{itemize}
\item Baidu sentiment analysis Category Note
\begin{itemize}
\item 2 mean to belong to the positive category, 1 mean to belong to the neutral category, and 0 mean to belong to the Negative category
\end{itemize}
\item Google sentiment analysis Note
\begin{itemize}
\item The score of a document's sentiment indicates the overall emotion of a document. The magnitude of a document's sentiment indicates how much emotional content is present within the document, and this value is often proportional to the length of the document.
\item A document with a neutral score (around 0.0) may indicate a low-emotion document, or may indicate mixed emotions, with both high positive and negative values which cancel each out. Generally, you can use magnitude values to disambiguate these cases, as truly neutral documents will have a low magnitude value, while mixed documents will have higher magnitude values.
\item "Clearly positive" and "clearly negative" sentiment varies for different use cases and customers. You might find differing results for your specific scenario. We recommend that you define a threshold that works for you, and then adjust the threshold after testing and verifying the results. For example, you may define a threshold of any score over 0.25 as clearly positive, and then modify the score threshold to 0.15 after reviewing your data and results and finding that scores from 0.15-0.25 should be considered positive as well.
\end{itemize}
\end{itemize}

\section{Baidu sentiment analysis}
\label{sec:org850032d}
\subsection{Baidu Chinese sentiment analysis}
\label{sec:org6947fd1}
\subsubsection{Baidu Chinese sentiment analysis positive probability histogram}
\label{sec:org749c9a0}
\begin{center}
\includegraphics[width=.9\linewidth]{./img/BaiduPositiveProbababilityHistogramForOriginData.jpg}
\end{center}

\subsubsection{Baidu Chinese sentiment analysis postitive probability compare with different ranking(origin data)}
\label{sec:org2a96a0f}
\begin{center}
\begin{tabular}{lrrrrrr}
Ranking & Mean & Valid N & std.deviation & Total N & Minimum & Maximum\\
\hline
Ranking 10 & 0.239365965000 & 8525 & 0.2219412270000 & 8572 & 0.000106 & 1.000000\\
Ranking 20 & 0.292751426000 & 13141 & 0.2357115580000 & 13226 & 0.000162 & 1.000000\\
Ranking 30 & 0.394234 & 18821 & 0.273685 & 18974 & 0.000214 & 1.000000\\
Ranking 40 & 0.511990 & 8717 & 0.300618 & 8790 & 0.001050 & 1.000000\\
Ranking 50 & 0.568988 & 4271 & 0.312815 & 4307 & 0.000536 & 1.000000\\
\end{tabular}
\end{center}

\begin{center}
\includegraphics[width=.9\linewidth]{./img/MarginalMeansOfBaiduPositiveProbabilityForOriginData.jpg}
\end{center}

\begin{itemize}
\item Baidu Chinese sentiment analysis positive probability values are valid.
\end{itemize}

\subsubsection{Baidu Chinese sentiment analysis postitive probability tranform to Google Score standard compare with different ranking (origin data)}
\label{sec:org738019a}
\begin{center}
\begin{tabular}{lrrrlrrr}
Ranking & Mean & Valid N & std.deviation & Total N & Minimum & Maximum & Variance\\
\hline
Ranking 10 & -0.598875 & 8525 & 0.557595 &  & -0.999894 & 1.000000 & 0.310912\\
Ranking 20 & -0.488772 & 13141 & 0.617021 &  & -0.999838 & 1.000000 & 0.380715\\
Ranking 30 & -0.236524 & 18821 & 0.728420 &  & -0.999786 & 1.000000 & 0.530596\\
Ranking 40 & 0.054493 & 8717 & 0.773410 &  & -0.998950 & 1.000000 & 0.598164\\
Ranking 50 & 0.188983 & 4271 & 0.774245 &  & -0.999464 & 1.000000 & 0.599456\\
Total & -0.274854 & 53475 & 0.733884 &  & -0.999894 & 1.000000 & 0.538586\\
\end{tabular}
\end{center}

\begin{center}
\includegraphics[width=.9\linewidth]{./img/MarginalMeansOfBaiduPositiveProbababilityToGoogleScoreStandardForOriginData.jpg}
\end{center}

\subsubsection{Baidu Chinese sentiment analysis category value compare with different ranking (origin data)}
\label{sec:org32005da}
\begin{center}
\includegraphics[width=.9\linewidth]{./img/MarginalMeansOfBaiduCategoryFroOriginData.jpg}
\end{center}

\begin{itemize}
\item Baidu Chinese sentiment analysis category values are valid.
\end{itemize}

\subsubsection{Chinese sentiment analysis Error Rate}
\label{sec:org6ed59fa}
\begin{center}
\begin{tabular}{lr}
Ranking & Error Rate\\
\hline
Ranking 10 & 0.0054829678\\
Ranking 20 & 0.0064267352\\
Ranking 30 & 0.0080636661\\
Ranking 40 & 0.0083048919\\
Ranking 50 & 0.0083584862\\
\end{tabular}
\end{center}

\begin{itemize}
\item Total Error Rate: 0.0073140396
\end{itemize}
\subsubsection{Baidu Chinese sentiment analysis Summary}
\label{sec:org1db4618}
\begin{itemize}
\item Baidu Chinese sentiment analysis positive probability values are valid.
\item Baidu Chinese sentiment analysis category values are valid.
\end{itemize}

\subsection{Baidu English sentiment analysis}
\label{sec:orgf18522b}
\subsubsection{Baidu English sentiment analysis postitive probability compare with different ranking (based on Google translated data)}
\label{sec:orgd634f3e}
\begin{center}
\begin{tabular}{lrrrlrrr}
Ranking & Mean & Valid N & Std.deviation & Total N & Minimum & Maximum & Variance\\
\hline
Ranking 10 & 0.517526 & 7968 & 0.134711 &  & 0.005045 & 1.000000 & 0.018147\\
Ranking 20 & 0.531020 & 12225 & 0.141214 &  & 0.037275 & 1.000000 & 0.019941\\
Ranking 30 & 0.540824 & 17457 & 0.137174 &  & 0.014443 & 1.000000 & 0.018817\\
Ranking 40 & 0.567782 & 8163 & 0.144971 &  & 0.051860 & 1.000000 & 0.021016\\
Ranking 50 & 0.589054 & 4006 & 0.150737 &  & 0.086614 & 1.000000 & 0.022722\\
\end{tabular}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{./img/MarginalMeansOfBaiduPositiveProbabilityForGoogleTranslatedData.jpg}
\end{center}

\begin{itemize}
\item Baidu English sentiment analysis positive probability values are valid.
\end{itemize}
\subsubsection{Baidu English sentiment analysis positive probability tranform to Google Score Standard (based on Google translated data)}
\label{sec:orge285725}
\begin{center}
\begin{tabular}{lrrrlrrr}
Ranking & Mean & Valid N & Std.deviation & Total N & Minimum & Maximum & Variance\\
\hline
Ranking 10 & 0.112029 & 7968 & 0.586700 &  & -0.994955 & 1.000000 & 0.344216\\
Ranking 20 & 0.150325 & 12225 & 0.587147 &  & -0.962725 & 1.000000 & 0.344742\\
Ranking 30 & 0.193858 & 17457 & 0.577416 &  & -0.985557 & 1.000000 & 0.333410\\
Ranking 40 & 0.276835 & 8163 & 0.564339 &  & -0.948140 & 1.000000 & 0.318479\\
Ranking 50 & 0.352409 & 4006 & 0.537822 &  & -0.913386 & 1.000000 & 0.289253\\
\end{tabular}
\end{center}

\begin{center}
\includegraphics[width=.9\linewidth]{./img/MarginalMeansOfBaiduPositiveProbabilityToGoogleStandardFroGoogleTranslatedData.jpg}
\end{center}

\subsubsection{Baidu English sentiment analysis category values compare with different ranking (based on Google translated data)}
\label{sec:org4297533}
\begin{center}
\includegraphics[width=.9\linewidth]{./img/MarginalMeansOfBaiduCategoryFroGoogleTranslatedData.jpg}
\end{center}
\begin{itemize}
\item Baidu English sentiment analysis category values are valid.
\end{itemize}

\subsection{Baidu Chinese sentiment analysis positive probability tranform to Google Score standard Method}
\label{sec:orgbecb070}
\begin{center}
\includegraphics[width=.9\linewidth]{./img/baiduPositiveProbabilityTranformToGoogleScoreStandard.png}
\end{center}

\section{Google sentiment analysis}
\label{sec:org94c30eb}
\subsection{Google Chinese sentiment analysis}
\label{sec:org11ae8ea}
\subsubsection{Google Chinese sentiment analysis scores compare with different ranking (origin data)}
\label{sec:org70ba0e4}
\begin{center}
\begin{tabular}{lrrrrrr}
Ranking & Mean & Valid N & std.deviation & Total N & Minimum & Maximum\\
\hline
Ranking 10 & -0.238742 & 8567 & 0.445384 & 8572 & -0.900000 & 0.900000\\
Ranking 20 & -0.118380 & 13210 & 0.448064 & 13226 & -0.900000 & 0.900000\\
Ranking 30 & 0.117291 & 18940 & 0.462095 & 18974 & -0.900000 & 0.900000\\
Ranking 40 & 0.315915 & 8778 & 0.458128 & 8790 & -0.900000 & 0.900000\\
Ranking 50 & 0.361626 & 4305 & 0.441309 & 4307 & -0.900000 & 0.900000\\
\end{tabular}
\end{center}

\begin{center}
\includegraphics[width=.9\linewidth]{./img/MarginalMeansOfGoogleScoreForOriginData.jpg}
\end{center}

\begin{itemize}
\item Google Chinese sentiment analysis score values are valid.
\end{itemize}

\subsubsection{Google Chinese sentiment analysis Error Rate}
\label{sec:orgc10477d}
\begin{center}
\begin{tabular}{lr}
Ranking & Error Rate\\
\hline
Ranking 10 & 0.0005832944\\
Ranking 20 & 0.0012097384\\
Ranking 30 & 0.0017919258\\
Ranking 40 & 0.0013651877\\
Ranking 50 & 0.0004643603\\
\end{tabular}
\end{center}

\begin{itemize}
\item Total Error Rate: 0.0012808851
\end{itemize}

\subsection{Google English sentiment analysis}
\label{sec:org1f9c9de}
\subsubsection{Google English sentiment analysis score compare with different ranking (based on Google translated data)}
\label{sec:orga9d4397}
\begin{center}
\begin{tabular}{lrrrlrrr}
Ranking & Mean & Valid N & Std.deviation & Total N & Minimum & Maximum & Variance\\
\hline
Ranking 10 & -0.338431 & 8566 & 0.430581 &  & -0.900000 & 0.900000 & 0.185400\\
Ranking 20 & -0.244312 & 13204 & 0.437549 &  & -0.900000 & 0.900000 & 0.191449\\
Ranking 30 & -0.057978 & 18940 & 0.447353 &  & -0.900000 & 0.900000 & 0.200125\\
Ranking 40 & 0.147830 & 8777 & 0.455342 &  & -0.900000 & 0.900000 & 0.207336\\
Ranking 50 & 0.225000 & 4304 & 0.453471 &  & -0.900000 & 0.900000 & 0.205636\\
\end{tabular}
\end{center}
\begin{center}
\includegraphics[width=.9\linewidth]{./img/MarginalMeansOfGoogleScoreFroGoogleTranslatedData.jpg}
\end{center}

\begin{itemize}
\item Google English sentiment analysis score values are valid based on Google translated data.
\end{itemize}

\subsubsection{Google English sentiment analysis score compare with different ranking (base on Yandex translated data)}
\label{sec:org946cd8b}
\begin{center}
\begin{tabular}{lrrrlrrr}
Ranking & Mean & Valid N & Std.deviation & Total N & Minimum & Maximum & Variance\\
\hline
Ranking 10 & -0.337873 & 8568 & 0.416416 &  & -0.900000 & 0.900000 & 0.173403\\
Ranking 20 & -0.233371 & 13221.000000 & 0.422133 &  & -0.900000 & 0.900000 & 0.178196\\
Ranking 30 & -0.055703 & 18972.000000 & 0.429758 &  & -0.900000 & 0.900000 & 0.184692\\
Ranking 40 & 0.138917 & 8788.000000 & 0.447876 &  & -0.900000 & 0.900000 & 0.200593\\
Ranking 50 & 0.208268 & 4306.000000 & 0.449598 &  & -0.900000 & 0.900000 & 0.202138\\
\end{tabular}
\end{center}

\begin{itemize}
\item Google English sentiment analysis score values are valid based on Yandex translated data.
\end{itemize}
\subsubsection{Google English sentiment analysis score compare with different ranking (base on Baidu translated data)}
\label{sec:org32a8312}
\begin{center}
\begin{tabular}{lrrrlrrr}
Ranking & Mean & Valid N & Std.deviation & Total N & Minimum & Maximum & Variance\\
\hline
Ranking 10 & -0.284984 & 8491.000000 & 0.416185 &  & -0.900000 & 0.900000 & 0.173210\\
Ranking 20 & -0.192064 & 13092.000000 & 0.417855 &  & -0.900000 & 0.900000 & 0.174603\\
Ranking 30 & -0.017125 & 18820.000000 & 0.429167 &  & -0.900000 & 0.900000 & 0.184185\\
Ranking 40 & 0.167667 & 8734.000000 & 0.432601 &  & -0.900000 & 0.900000 & 0.187144\\
Ranking 50 & 0.244657 & 4286.000000 & 0.430004 &  & -0.900000 & 0.900000 & 0.184904\\
\end{tabular}
\end{center}

\begin{itemize}
\item Google English sentiment analysis score values are valid based on Baidu translated data.
\end{itemize}

\subsubsection{Correlations Between Origin data, Google Translated data, Yandex Translated and Baidu Translated data (each element)}
\label{sec:org36da186}
\begin{center}
\includegraphics[width=.9\linewidth]{./img/correlationsBetweenOriginGoogleTranslatedYandexTranslatedBaiduTranslatedUsingGoogleSentiment.png}
\end{center}
\begin{itemize}
\item assumption Google English sentiment analysis tool and Google Chinese sentiment analysis tool are same
\begin{itemize}
\item Google translation sentence quality > Yandex translation sentence quality > baidu translation sentence quality
\item analysis same langeuage corrlations always bigger than cross langeuage corrlations
\end{itemize}
\end{itemize}

\subsubsection{Correlations between origin data Mean, Google translated data Mean, Yandex translated Mean and baidu translated data Mean}
\label{sec:org35a19ce}
\begin{center}
\includegraphics[width=.9\linewidth]{./img/correlationsBetweenOriginGoogleTranslatedYandexTranslatedBaiduTranslatedMeanUsingGoogleSentiment.png}
\end{center}
\begin{itemize}
\item translation sentence tools' quality have NOT significant impact sentiment analysis results
\item I guess translation key word quality more importance compare with sentence translation quality
\item Using sentiment analysis results compare different translation tools' quality are NOT reliable.
\end{itemize}

\section{Baidu sentiment analysis VS Google sentiment analysis}
\label{sec:org70a7cb7}
\subsection{Baidu Chinese sentiment analysis VS Google Chinese sentiment analysis}
\label{sec:orgd824a64}
\subsubsection{Mean Value Correlation}
\label{sec:org274133c}
\begin{itemize}
\item Pearson Correlation 0.991
\item sig. 0.001
\item N 5
\item Conclusion
Baidu Chinese sentiment analysis and Google Chinese sentiment analysis have higher liner relationship.
\end{itemize}

\subsubsection{Error Rate}
\label{sec:org39b131e}
\begin{itemize}
\item Baidu Chinese sentiment analysis Total Error Rate = 0.0073140396
\item Google Chinese sentiment analysis Total Error Rate = 0.0012808851
\item conclusion
\begin{itemize}
\item Baidu sentiment analysis error rate high than Google sentiment analysis error rate
\end{itemize}
\end{itemize}

\subsubsection{Tendency}
\label{sec:orgf129605}
\begin{itemize}
\item chinese sentiment analysis results given by both Baidu and Google are valid because when the ranking group ID increases from 11 to 50, the sentiment analysis score also strictly increases accordingly.
\end{itemize}

\subsection{Baidu English sentiment analysis VS Google English sentiment analysis}
\label{sec:org6a6efbc}
\subsubsection{Mean Value Correlation (based on Google translation)}
\label{sec:orgd406589}
\begin{itemize}
\item Pearson Correlation 0.978
\item sig. 0.004
\item N 5
\item Conclusion
Baidu English sentiment analysis and Google English sentiment analysis have higher liner relationship.
\end{itemize}
\subsubsection{Tendency}
\label{sec:org4fa1f32}
\begin{itemize}
\item English sentiment analysis results given by both Baidu and Google are valid because when the ranking group ID increases from 11 to 50, the sentiment analysis score also strictly increases accordingly.
\end{itemize}
\end{document}
\message{ !name(<none>.tex) !offset(-372) }

### 2018-08-11 submit/paper.tex
update

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage[style=authoryear-ibid,backend=biber]{biblatex}
\usepackage{csquotes}
\usepackage{xcolor}
\addbibresource{library.bib}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{\huge Cross-language Sentiment Analysis for Social Media}

\author{\IEEEauthorblockN{Boyang Yan}
\IEEEauthorblockA{\textit{School of Computing and Information Technology} \\
  \textit{University of Wollongong}\\
  Wollongong, Australia\\
  by932@uowmail.edu.au}
\and
\IEEEauthorblockN{Xiaoxia Pu}
\IEEEauthorblockA{\textit{School of Computing and Information Technology} \\
  \textit{University of Wollongong}\\
  Wollongong, Australia\\
  xp816@uowmail.edu.au
}
\and
\IEEEauthorblockN{Xudong Zhang}
\IEEEauthorblockA{\textit{School of Computing and Information Technology} \\
  \textit{University of Wollongong}\\
  Wollongong, Australia\\
  xz944@uowmail.edu.au}
\and
\IEEEauthorblockN{Helene Tran}
\IEEEauthorblockA{\textit{School of Computing and Information Technology} \\
  \textit{University of Wollongong}\\
  Wollongong, Australia\\
  ht185@uowmail.edu.au}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}
\begin{enumerate}
\item A citation command in parentheses: \parencite{b1}.
\item A citation command for use in the flow of text: As \textcite{b1} said \dots
\item A citation command which automatically switches style depending on location and the option setting in the package declaration (see line 12 in the LaTeX source code). In this case, it produces a citation in parentheses: \autocite{b1}.
\end{enumerate}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is .

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
%\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets . The
sentence punctuation follows the bracket . Refer simply to the reference
number, as in ---do not use ``Ref. '' or ``reference '' except at
the beginning of a sentence: ``Reference  was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' . Papers
that have been accepted for publication should be cited as ``in press'' .
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation .
\vspace{12pt}

\printbibliography
\end{document}

### 2018-08-11 oneSideWithAnotherSideOpposite.R

@@ -3,10 +3,142 @@ library(dplyr)
 library(rtf)
 library(NonCompart)
 library(ncar)
+install.packages('VennDiagram')
+library(VennDiagram)
 data <- read.csv(file="goodDataLatest.csv",head=TRUE,sep=",")
+data$ID <- seq.int(nrow(data))
+
+#Google sentiment analysis(Google translation)
+googleSentimentAnalysisGoogleTranslation <- data %>% select(ID, Chinese.origin.data, Google.translated.data, Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data., Google.English.sentiment.analysis.score.base.on.Google.translated.data.) %>%
+  filter( ((Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data. > 0.5) & (Google.English.sentiment.analysis.score.base.on.Google.translated.data. < -0.5)) | ((Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data. < -0.5) & (Google.English.sentiment.analysis.score.base.on.Google.translated.data. > 0.5)) )
+
+
+#Google sentiment analysis(Baidu translation)
+googleSentimentAnalysisBaiduTranslation <- data %>% select(ID, Chinese.origin.data, Baidu.translated.data, Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data., Google.English.sentiment.analysis.score.base.on.Baidu.translated.data.) %>%
+  filter( ((Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data. > 0.5) & (Google.English.sentiment.analysis.score.base.on.Baidu.translated.data. < -0.5)) | ((Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data. < -0.5) & (Google.English.sentiment.analysis.score.base.on.Baidu.translated.data. > 0.5)) )
+
+
+#Google sentiment analysis(Yandex translation)
+googleSentimentAnalysisYandexTranslation <- data %>% select(ID, Chinese.origin.data, Yandex.translated.data, Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data., Google.English.sentiment.analysis.score.base.on.Yandex.translated.data.) %>%
[…]

### 2018-08-29 print/paper.tex
backup

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{url}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{\huge Metamorphic Testing in cross-language Sentiment Analysis of Social Media}

\author{\IEEEauthorblockN{Boyang Yan}
\IEEEauthorblockA{\textit{School of Computing and Information Technology} \\
  \textit{University of Wollongong}\\
  Wollongong, Australia\\
  by932@uowmail.edu.au}
\and
\IEEEauthorblockN{Xiaoxia Pu}
\IEEEauthorblockA{\textit{School of Computing and Information Technology} \\
  \textit{University of Wollongong}\\
  Wollongong, Australia\\
  xp816@uowmail.edu.au
}
\and
\IEEEauthorblockN{Xudong Zhang}
\IEEEauthorblockA{\textit{School of Computing and Information Technology} \\
  \textit{University of Wollongong}\\
  Wollongong, Australia\\
  xz944@uowmail.edu.au}
\and
\IEEEauthorblockN{Helene Tran}
\IEEEauthorblockA{\textit{School of Computing and Information Technology} \\
  \textit{University of Wollongong}\\
  Wollongong, Australia\\
  ht185@uowmail.edu.au}
}

\maketitle

\begin{abstract}
\end{abstract}

\begin{IEEEkeywords}
sentiment analysis, machine translation
\end{IEEEkeywords}

\section{Introduction}

\nocite{*}
\bibliographystyle{annotate}
\bibliography{library}

Social Media is becoming more and more popular. There are lots of text comments
on different discussion topics every day.
It would be impossible to analysise the huge amount of data generated manually.
These topics are discussed by speakers of different languages, from different
cultural backgrounds, further complicating any analysis.
Most people enounter language and culture barriers during cross-language communication.
In this paper, the use of machine translation and sentiment analysis tools to
solve this problem of analysing cross-cultural and cross-language data is
explored and discussed.
The aim is for people to be able to understand different language speakers' attitudes (positive or negative), emotions and opinions.\\

\cite{Senn:2009}

Sentiment analysis is useful for analyzing a huge amount of data relating to personal
opinions.
It can be use in the e-business context. For example, a business manager can analysise
customers’ attitudes; whether they like or dislike their product or service.
Governments can also use sentiment analysis to analyze citizens' perspectives.

In a word, sentiment analysis is coming into widespread used.

In this semester, I am firstly focus on conducting literature review about the
current state of Chinese Sentiment Analysis research.

A review article published last year has been identified as relevant
(Haiyun,2017).
As Dr. Haiyun mentioned that English language sentiment analysis research has
undergone major developments in recent years.

Chinese sentiment analysis research has not evolved significantly.

Today, a lot of English language sentiment analysis theories have been
developed.

Also, lots of translation tools are available.

However, nobody working in the two fields of research is undertaking non-English
sentiment analysis.

So, the purpose of this research is to achieve a method for finding which
machine translation service combined with which English sentiment analysis
service can obtain reliable sentiment analysis results for non-English speakers,
who do not have sentiment analysis tools to analyze their own language.

However, Chinese research does not sufficiently represent all of the non-English
speaking world.

So, more information in Hindi, Arabic, Spanish, Portuguese and Japanese needs to
identify.
As a result, this research is proposed to create a testing model for finding the
best-combined mode between English sentiment analysis tools and translation
tools.
There are couples of search terms used for this literature review, such as
sentiment analysis, text mining.

machine translation, text segmentation, text classification, machine learning,
deep learning, neural network, metamorphic testing and adaptive random testing.

In this literature review, it has 2 key journals, which are IEEE and ACM.

The key author is Zhiquan (George) Zhou.

All of reference article will come from books, research articles, review
articles and website in recent 10 years, this research consists of three
components.

Firstly, measuring machine translation service quality based on sentiment
analysis results from both sides.

Secondly, testing sentiment analysis service quality.

Thirdly, finding the best compound mode for machine translation service and
sentiment analysis service.

In the following statement, I will talk about Testing Method based on Metamorphic Testing, Machine Translation testing, Sentiment Analysis Testing and literature review of Experiment Support.

\section{Machine Translation}
I have found two research articles about testing modeling of machine
translation.
Somers (2005, p. 127 -133) argue that using around trip translation method to
detect the quality of machine translation.
For example, testing English to Chinese translation tool.
Firstly, using English to Chinese translation tool translate test data to
Chinese.
Secondly, translation Chinese translated data back to English.
Finally, compare the similarity for two English data set. Another article is
about using third-party language to test the quality of machine translation
(Pesu, 2017). For example, if testing English to Chinese translation tool.
Firstly, random choice an Intermediate third-party language.
Secondly, translation English test data to the third-party language, after
translation third-party language to Chinese.
These two steps are only finished one path. Another path is a translation in
English directly to Chinese.
In the end, the comparison the two paths of results similarity. In this article,
the main finding is Google Translate is the best machine translation. In
addition, there is a tendency to be produced better results in European
languages, which use ANOVA Statistics method getting this conclusion.
In my experiment, I also got Google Translator is the best machine translation compare with Yandex and Baidu.
The three different machine translation testing modeling, we can call the three
different Metamorphic Relations.
So, I have found a research article

Cao 2013

about the effectiveness of metamorphic relations.
Also, when I finished reading all of the details, I have found Two-way ANOVA is
also suitable for part 3 of my research (finding the best compound mode for
machine translation service and sentiment analysis service).

I think that the disadvantages of those three-testing modeling will be involved some of the noise.
It is clear the Round-Trip will be involved translation back path noise. Using
the third language will be involved in third language translation path noise.
My modeling will be involved sentiment analysis tools’ noise. However, my
modeling does not involve any noise from translation tool. I think my modeling
is better than the other two testing modeling. I am total from another aspect
to test translation tool.
\section{Sentiment Analysis Testing}
 In this semester, I have finished experiment for testing Google, Yandex and Baidu machine translation service, also finished experiment for comparison Google and Baidu sentiment analysis tools. For the sentiment analysis, I only finish testing the overview performance. Next semester, I have prepared to test sentiment analysis tools by different components. So, I have found a book (Liu, 2012) about sentiment analysis. According to Liu’s book that text sentiment analysis roughly have 5 steps.
1. Texting segmentation for the separate sentence to a list of keywords
2. Filtering for removing unnecessary keywords that will not add value to sentiment analysis,
Such as is, but, it and so on.
3. Finding the basic words for Convert all infections to their root words.
4. Making Features for Using the root words as features to indicate the positiveness or negativeness
5. The last step is Classifier for the train a classifier to predict positivity.
I will base on these five steps to testing sentiment analysis in next semester.

Testing Step 1 (Sentiment Analysis)
Ramos (2003, p. 133 - 142) claims that Tf-idf, which is an abbreviation for the term Frequency Inverse Document Frequency, is one of words ranking calculation method and a kind of numerical statistic designed to reflect how important a word is to a collection or a corpus of documents.
I think that Tf-idf is useful for testing sentiment analysis first step (texting segmentation). I can look for what is different between Baidu texting segmentation Ranking Group and Google texting segmentation Ranking Group in same test data. If these two rankings are different, I may identificate the quality for texting segmentation.

Testing Method
Accounting to Sethi (2017) said that there are two categorized testing techniques, which are Static Testing and Dynamic Testing. The Dynamic Testing are divided into three categories, which are Functional Testing, Structural testing and Non-Functional Testing. In my research project, I will focus on Functional Testing.

Metamorphic Testing
The proposed research is based on Metamorphic Testing. Metamorphic Testing is for testing function correctness. I have read a research article (Zhou, 2016), I think this article is well-explained for what is Metamorphic Testing. My testing modeling is based on Metamorphic Testing. So, this article is useful for me. As George (2016) said, Metamorphic testing (MT) is a property-based software testing method developed for automated test case generation and automated result verification, based on the effects of some expected properties of the target program. These properties, recognized as metamorphic relations (MRs), serve as essential relations among the inputs and outcomes of multiple executions of the target program. I make a example here to explain Metamorphic Testing. For instance, Test calculator function correctness will be shown if input 1 + 1, and the result will be 2. In this example we can easily make the judgment, correct or not. However, we will not easy to make this judgment quickly if input sin (3.7), and the calculator gives a output.in a generally acknowledged, Sin (3.7) = sin (3.7 + 360) is correct. In metamorphic testing, the name of 3.7 is the test case. The name of 3.7 + 360 is the follow-up test case. Metamorphic Relation is the relationship between two input test cases as well as the two outputs. Metamorphic testing is based on Metamorphic Relation. The two outputs need an existing mathematical relation. In my example, the relation is “=”. I think the advantage of Metamorphic testing (MT) method, which can automate result verification and test case generation. The disadvantage is that cannot detect memory leak or some others insensitivity failure situation. However, Metamorphic Testing is appropriate for testing translation tools and sentiment analysis tools.
Effectiveness of Metamorphic Relations
I have read an article which was written by Zhou in 2013. The main purpose of reading this article is to find the best one among the three testing modelings. This article is based on white-box testing, which have source code, as well as the most important conclusion is if the Metamorphic Relations can get bigger distance (dissimilarity) that will have more chance to detect failures.  In other words, MRs with very different initial and follow-up execution are more likely to detect failures than those with similar initial and follow-up executions. The concept of “difference” are defined in namely coverage Manhattan distance (CMD), frequency Manhattan distance (FMD), and frequency Hamming distance (FHD) in regard to adaptive random testing (ART), where CMD metric on the basis of branch coverage execution profiles performs the best fault-detection effectiveness.
 I think the advantage of this article is suitable for finding the most
 effectiveness of Metamorphic Relations in White-box.
 However, this article is not suitable for Black - Box Testing.
 The reason is Black Box Testing have not source code available, so it cannot calculation the program’s distance. In this research project, my testing modeling have not source code available. So, I have found another research article (Henard,2016)talking about the difference between black-box testing and white-box testing.

White-box VS Black-box
Henard (2016) have done some research for difference between white box testing and black - box testing in 2016. They have two finding is useful in my research black-box testing and white-box testing performance just have a little difference (at most 4% fault detection rate difference). They also found black-box testing and white-box testing the overlap is very high. The first 10% of the prioritized test data already agree on at least 60% of the faults found. As the result, this research article has given me a lot of idea for how similar between white box testing and black box testing. I still have opportunity for compare those three modelings, which one is better.

\section{Experiment Support}
\label{sec:label}

Stanisic (2015) have done a review article about experiment workflow. This review article is not related to my research topic, But very useful for improve research workflow, especially for writing experiment note. Git is version control system, which can rollback to older version of you writing. Emacs org mode is so powerful for you writing. Org-ref is citations, cross-references, indexes, glossaries and Bibtex utilities for org-mode. Org mode also can easier convert to latex format and html format. Even we can write your own emacs lisp for needed function.
In my research, I need collect lots of data. So, I have read a website give me some ideas about how to manage experiment data. My personal opinion, if you write your own programs, such as using c++ or Python, I think the best way is using CSV format. Reasons:
In C++ or Python, there are a lot of free libraries for reading and writing CSV format.
In C++, I have found a library, which name is libxl(http://www.libxl.com/) for reading and writing Excel file but not free.
In Python, there is a open source Excel library, which name is openpyxl, but I have found this library are not suitable for large amount of data operation, because very slow. Openpyxl is a Python library for reading and writing Excel 2010 xlsx/xlsm/xltx/xltm files.
However, Microsoft excel have lots of build-in function for operation data. CSV can convert back to Excel format, if Microsoft Excel build-in function is suitable for your research project, which is better way, it is not necessary for us to rewrite function by self. For example, you write your own coding for collect data in CSV file, after you convert CSV file to excel for draw graphic. When you find Excel have not suitable build-in function for you. You can convert back to CSV.
To sum up, several research literature indicate sentiment analysis is coming into widespread used, but the evidence of the measuring machine translation service quality is critical point, it lies in best compound mode for machine translation service and sentiment analysis service. Functional Testing as main test methods, Metamorphic Testing in cross-language sentiment analysis service are needed. Metamorphic Testing is appropriate for testing translation tools and sentiment analysis tools. Several studies have indicated that black-box testing, and white-box testing may play a part in the effectiveness of metamorphic relations.

\section*{Acknowledgment}
\bibliographystyle{IEEEtran}
\bibliography{library}
\end{document}

### 2018-08-29 print/todoList.tex
backup

% Created 2018-08-11 Sat 15:49
% Intended LaTeX compiler: pdflatex
\documentclass[9pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage[table]{xcolor}
\usepackage[margin=2cm]{geometry}
\author{Boyang}
\date{\today}
\title{Cross-language Sentiment Analysis for Social Media}
\hypersetup{
 pdfauthor={Boyang},
 pdftitle={Testing in Cross-language Sentiment Analysis},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.1 (Org mode 9.1.13)}, 
 pdflang={English}}
\begin{document}

\maketitle

\section{Backgrund}
Social Media becomes more and more popular. There are lots of text comments for discussion different topics everday.
However, all of those topics have discusse by different language spearkers, which have different culture backgraound.
Most of people have language and culture barrier when we doing cross-language communicate with each other.
Manpower is impossible to analysis huge amount of data. So,
We want to using machine trainslation and sentiment analysis tools to solve this problems.
Let people can understand different language speakers' attitudes (positive or negative), emotions and opinions.\\
\underline{\textbf{(Please, finding some of paper to support the backgraound)}}
\section{Purpose}
The purpose of this research is to achieve a method for finding which machine translator service combined with which English sentiment analysis service can obtain reliable sentiment analysis result for non-English speaker, who does not have sentiment analysis tool to analysis their own language.

\section{Todo List}
\subsection{Timetable}
\begin{center}

\begin{tabularx}{\textwidth}{X|X}
  \textbf{Deadline} & \textbf{Part} \\
\hline
20/08/2018 & Annotated bibliography and literature review\\
23/08/2018 & Research Proposal\\
27/08/2018 & Survey - Questionnaires\\
03/09/2018 & Qualitative analysis\\
\end{tabularx}

\end{center}
\subsubsection{detecting advertising in BBS comments (Chinese and English)}
\begin{itemize}
\item fouce on detecting Chinese advertising (Xudong and Xiaoxia can choose this part)
\end{itemize}
detecting advertising in BBS comments or Movies Review, etc
Thinking and research How to measure the quality of detecting advertising modle

\begin{itemize}
\item detecting English advertising
\end{itemize}

\subsubsection{sentiment analysis}
\begin{itemize}
\item what is sentiment analysis: Sentiment analysis model for recognize the test data belong to positive, negative or neutral classification
\item fouce on creating English sentiment analysis model first (using Natural Language Toolkit (NLTK))
\item Others Libary for using on natural language processing: Apache OpenNLP, Stanford NLP suite, Gate NLP library or Gensim.
\item when you finish creating English sentiment analysis model, Thinking about to measure the quality of your model. Testing each part of your model.
\end{itemize}

\begin{enumerate}
\item step of sentiment analysis (English)
\begin{enumerate}
\item Texting segmentation for the separate sentence to a list of keywords
\item Filtering for removing unnecessary keywords that will not add value to sentiment analysis, Such as is, but, it and so on.
\item Finding the basic words for Convert all infections to their root words.
\item Making Features for Using the root words as features to indicate the positiveness or negativeness
\item The last step is Classifier for the train a classifier to predict positivity.
\end{enumerate}
\rowcolors{1}{green}{pink}
\begin{tabularx}{\textwidth}{p{1cm}|X|X|p{2cm}|p{2cm}}
  \textbf{Part} & \textbf{Description} & \textbf{Comment} & \textbf{Undertaker} & \textbf{Signature} \\
  \hline
  Part 1 & Backgrund and detecting advertising & show current social media usage
  amount, demonstrate most of researcher fouce on English sentiment analysis, no
  much people doing non-English sentiment analysis. Detecting Chinese
  advertising & Xiaoxia Pu & \\ \hline
Part 2 & sentiment analysis step 1, 2 and 3 &  & Helene Tran & \\ \hline
Part 3 & sentiment analysis step 4 and 5 &  & Xudong Zhang & \\ \hline
Part 4 & Mechine Translation and Sentiment Analysis Testing Modle &  & Boyang Yan & \\ \hline
\end{tabularx}
\end{enumerate}
\end{document}

### 2018-08-29 submit/paper.tex
backup

@@
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+\usepackage{cite}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \usepackage{textcomp}
-\usepackage[style=authoryear-ibid,backend=biber]{biblatex}
-\usepackage{csquotes}
 \usepackage{xcolor}
-\addbibresource{library.bib}
+\usepackage{tabularx}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \begin{document}
-
 \title{\huge Cross-language Sentiment Analysis for Social Media}
@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+sentiment analysis, machine translation
 \end{IEEEkeywords}
@@
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
+Sentiment analysis is a part of text data mining. The aim of sentiment analysis
+is to determine the attitude of speakers or writers with respect to some topic
+or the overall contextual polarity or emotional reaction to a text document. It is usually equated with
+opinion mining, which involves the use of natural language processing and
+machine learning to ascertain the possibility of positive or negative opinions \cite{sentimentAnalysis}.
+Sentiment analysis is useful for analyzing a huge amount of data relating to personal
+opinions. It can be used in an e-business context. For example, business managers can analysise
+customers' attitudes, as to whether they like or dislike their product or service.
+Also, government can use sentiment analysis to analyze citizen perspectives.
+In a word, sentiment analysis is coming into widespread use.
 
-\section{Ease of Use}
+As Dr. Haiyun mentions, English language sentiment analysis research has
+undergone major developments in recent years \cite{ChineseSentimentAnalysis}.
+However, less research has been undertaken in other languages, such as Chinese.
+Today, a lot of English language sentiment analysis theories have been
+developed. Also, lots of Machine Translation tools are available, such as Google
+translation, Bing translation and Yandex translation.
+Manchine Translation uses computational linguistic programs and natural language
+processing theory \cite{machineTranslation}.
 
-\subsection{Maintaining the Integrity of the Specifications}
-\begin{enumerate}
-\item A citation command in parentheses: \parencite{b1}.
-\item A citation command for use in the flow of text: As \textcite{b1} said \dots
-\item A citation command which automatically switches style depending on location and the option setting in the package declaration (see line 12 in the LaTeX source code).
-In this case, it produces a citation in parentheses: \autocite{b1}.
-\end{enumerate}
+However, nobody working in a combination of these two fields of research has undertaken non-English
+sentiment analysis. Therefore, the research described and discussed in this
+document aimed to create a testing model to find the best-combination of English
+sentiment analysis tools and machine translation tools to obtain reliable
+sentiment analysis results from non-English texts, for non-English speakers who
+do not have such sentiment analysis tools to analyze their own language.
+\section{Literature Review}
+This research consists of three components.
+Firstly, measuring machine translation service quality.
+Secondly, testing sentiment analysis service quality.
+Thirdly, finding the best compound mode for machine translation service and
+sentiment analysis service.
+As a result, this section will fouced on machine translation and sentiment
+analysis.
 
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
+\subsection{Machine Translation}
+There are two research articles about testing modeling of machine translation.
 
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
+\paragraph{Around Trip Translation Method}
+\cite{roundTripTranslation}
+As Somers argue that they establish an around trip translation method for detect
+the quality of machine translation.
+For example, testing English to Chinese translation tool.
+Firstly, using English to Chinese translation tool translate test data to
+Chinese.
+Secondly, translation Chinese translated data back to English.
+Finally, compare the similarity for two English data set.
 
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
+\paragraph{Translation Method}
+Another article is about using third-party language to test the quality of machine
+translation (Pesu, 2017). For example, if testing English to Chinese translation
+tool. Firstly, random choice an Intermediate third-party language. Secondly,
+translation English test data to the third-party language, after translation
+third-party language to Chinese. These two steps are only finished one path.
+Another path is a translation in English directly to Chinese. In the end, the
+comparison the two paths of results similarity. In this article, the main
+finding is Google Translate is the best machine translation. In addition, there
+is a tendency to be produced better results in European languages, which use
+ANOVA Statistics method getting this conclusion. In my experiment, I also got
+Google Translator is the best machine translation compare with Yandex and Baidu.
 
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
+The three different machine translation testing modeling, we can call the three
+different Metamorphic Relations. So, I have found a research article(Cao,2013)
+about the effectiveness of metamorphic relations.
 
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
+Also, when I finished reading all of the details, I have found Two-way ANOVA is also suitable for part 3 of my research (finding the best compound mode for machine translation service and sentiment analysis service).
+I think that the disadvantages of those three-testing modeling will be involved some of the noise.
+ It is clear the Round-Trip will be involved translation back path noise.
+Using the third language will be involved in third language translation path noise.
+My modeling will be involved sentiment analysis tools’ noise.
+However, my modeling does not involve any noise from translation tool.
+I think my modeling is better than the other two testing modeling.
+I am total from another aspect to test translation tool.
 
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
+\section{Method}
+\section{Test Data}
+Total have 46180 movies reviews.
+\begin{tabular}{lrl}
+Ranking & Number of Test Data & Percentage\\
+\hline
+Ranking 10 & 7353 & 15.92 \%\\
+Ramking 20 & 11209 & 24.27 \%\\
+Ranking 30 & 16223 & 35.13 \%\\
+Ranking 40 & 7663 & 16.59 \%\\
+Ranking 50 & 3732 & 8.08 \%\\
+\end{tabular}
 
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
+\section{IQR, Mean, Median, Q1, Q3, lower extreme, upper extreme, mean slope, median slope}
+\subsection{Baidu Chinese Sentiment analysis Positive Probability Base On (Chinese Origin Data)}
+\begin{tabularx}{\textwidth}{ |X|X|X|X|X|X|X|X }
+Ranking & IQR & Mean & Median & Q1 & Q3 & lowerExtreme & upperExtreme\\
+\hline
+10 & 0.3426533 & 0.2404781 & 0.1789910 & 0.0489987 & 0.3916520 & -0.4649812 & 0.9056319\\
+20 & 0.3817485 & 0.2949725 & 0.2489580 & 0.0878135 & 0.4695620 & -0.4848092 & 1.0421847\\
+30 & 0.4504405 & 0.3980354 & 0.3808120 & 0.1516095 & 0.6020500 & -0.5240512 & 1.2777107\\
+40 & 0.5255830 & 0.5123376 & 0.5385910 & 0.2461685 & 0.7717515 & -0.5422060 & 1.5601260\\
+50 & 0.5368080 & 0.5712128 & 0.6188395 & 0.3101650 & 0.8469730 & -0.4950470 & 1.6521850\\
+\end{tabularx}
 
-\subsection{\LaTeX-Specific Advice}
+\begin{tabular}{rr}
+  \hline
+  Mean Slope & Median Slope \\
+  \hline
+  0.008788344 & 0.0116933 \\
+  \hline
+\end{tabular}
 
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is .
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-\begin{figure}[htbp]
-%\centerline{\includegraphics{fig1.png}}
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
-
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
-
-\section*{References}
-
-Please number citations consecutively within brackets . The
-sentence punctuation follows the bracket . Refer simply to the reference
-number, as in ---do not use ``Ref. '' or ``reference '' except at
-the beginning of a sentence: ``Reference  was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' . Papers
-that have been accepted for publication should be cited as ``in press'' .
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation .
-\vspace{12pt}
-
-\printbibliography
+\bibliographystyle{IEEEtran}
+\bibliography{library}
 \end{document}

### 2018-08-29 print/paper.tex
backup

@@
 \bibliography{library}
-
-Social Media is becoming more and more popular. There are lots of text comments
-on different discussion topics every day.
-It would be impossible to analysise the huge amount of data generated manually.
-These topics are discussed by speakers of different languages, from different
-cultural backgrounds, further complicating any analysis.
-Most people enounter language and culture barriers during cross-language communication.
-In this paper, the use of machine translation and sentiment analysis tools to
-solve this problem of analysing cross-cultural and cross-language data is
-explored and discussed.
-The aim is for people to be able to understand different language speakers' attitudes (positive or negative), emotions and opinions.\\
 

### 2018-08-29 submit/paper.tex
backup

@@
 \section{Introduction}
+
+Social Media is becoming more and more popular. There are lots of text comments
+on different discussion topics every day.
+It would be impossible to analysise the huge amount of data generated manually.
+These topics are discussed by speakers of different languages, from different
+cultural backgrounds, further complicating any analysis.
+Most people enounter language and culture barriers during cross-language
+communication.
+In this paper, the use of machine translation and sentiment analysis tools to
+solve this problem of analysing cross-cultural and cross-language data is
+explored and discussed.
 Sentiment analysis is a part of text data mining. The aim of sentiment analysis
@@
 In a word, sentiment analysis is coming into widespread use.
-
 As Dr. Haiyun mentions, English language sentiment analysis research has
@@
 processing theory \cite{machineTranslation}.
-
 However, nobody working in a combination of these two fields of research has undertaken non-English
@@
 do not have such sentiment analysis tools to analyze their own language.
+In the end, everyone to be able to understand different language speakers' attitudes (positive or negative), emotions and opinions.\\
 \section{Literature Review}
@@
 sentiment analysis service.
-As a result, this section will fouced on machine translation and sentiment
-analysis.
+As a result, this section will fouced doing literature review on machine
+translation, Testing methodology and sentiment analysis.
+\subsection{Testing in Machine translation}
+There are two research articles about testing modeling of machine
+translation(MT).
 
-\subsection{Machine Translation}
-There are two research articles about testing modeling of machine translation.
-
-\paragraph{Around Trip Translation Method}
-\cite{roundTripTranslation}
-As Somers argue that they establish an around trip translation method for detect
-the quality of machine translation.
+\paragraph{Around Trip Translation method}
+As Somers argue that they establish an
+around trip translation (RTT) method for detect the quality of machine translation \cite{roundTripTranslation}.
 For example, testing English to Chinese translation tool.
@@
 Finally, compare the similarity for two English data set.
+They also metion two similarity metrics BLEU and F-score, to judge the
+translations. The limitation of RTT modle are it cannot tell which one is good
+MT from all bad MT tools as well as cannot find which sentences are easier for
+translation and which sentences are harder for translation.
 
-\paragraph{Translation Method}
+\paragraph{A monte carlo method for machine translation services}
 Another article is about using third-party language to test the quality of machine
-translation (Pesu, 2017). For example, if testing English to Chinese translation
-tool. Firstly, random choice an Intermediate third-party language. Secondly,
-translation English test data to the third-party language, after translation
-third-party language to Chinese. These two steps are only finished one path.
-Another path is a translation in English directly to Chinese. In the end, the
-comparison the two paths of results similarity. In this article, the main
+translation \cite{thirdPartMachineTranslation}.
+For example, if testing English to Chinese translation tool.
+Firstly, random choice an Intermediate third-party language.
+Secondly, translation English test data to the third-party language, after
+translation third-party language to Chinese.
+These two steps are only finished one path.
+Another path is a translation in English directly to Chinese.
+In the end, the comparison the two paths of results similarity. In this article, the main
 finding is Google Translate is the best machine translation. In addition, there
 is a tendency to be produced better results in European languages, which use
-ANOVA Statistics method getting this conclusion. In my experiment, I also got
-Google Translator is the best machine translation compare with Yandex and Baidu.
+ANOVA Statistics method and Pairwise t tests getting this conclusion.
+In my experiment, I also got Google Translator is the best machine translation compare with Yandex and Baidu.
+
+\subsection{Testing methodology}
+Accounting to Sethi said that there are two categorized testing
+techniques, which are Static Testing and Dynamic Testing. The Dynamic Testing
+are divided into three categories, which are Functional Testing, Structural
+testing and Non-Functional Testing \cite{testingMethodReview}.
+In my research project, I will focus on Functional Testing on this project.
+
+\paragraph{Metamorphic Testing}
+The proposed of this research project is based on Metamorphic Testing.
+Metamorphic Testing is for testing function correctness.
+There is a research article written by Zhou in 2016. This article is
+well-explained for what is Metamorphic Testing.
+As Zhou said, Metamorphic testing (MT) is a property-based software testing
+method developed for automated test case generation and automated result
+verification, based on the effects of some expected properties of the target
+program \cite{zhou2016metamorphic}.
+These properties, recognized as metamorphic relations (MRs), serve as essential
+relations among the inputs and outcomes of multiple executions of the target
+program.
+For instance, test calculator function correctness will be shown if input 1 + 1,
+and the result will be 2. In this example people can easily make the judgment,
+correct or not.
+However, people will not easy to make this judgment quickly if input sin (3.7),
+and the calculator gives a output.
+In a generally acknowledged, Sin (3.7) = sin (3.7 + 360) is correct.
+In metamorphic testing, the name of 3.7 is the test case. The name of 3.7 + 360
+is the follow-up test case.
+Metamorphic Relation is the relationship between two input test cases as well as
+the two outputs.
+Metamorphic testing is based on Metamorphic Relation.
+The two outputs need an existing mathematical relation.
+In this example, the relation is “=”. The advantage of Metamorphic testing (MT)
+method, which can automate result verification and test case generation.
+The disadvantage is that cannot detect memory leak or some others insensitivity
+failure situation.
+However, Metamorphic Testing is appropriate for testing translation tools and
+sentiment analysis tools.
+\subparagraph{Effectiveness of Metamorphic Relations}
+I have read an article which was written by Zhou in 2013.
+The main purpose of reading this article is to find the best one among the three testing modelings.
+This article is based on white-box testing, which have source code, as well as the most important conclusion is if the Metamorphic Relations can get bigger distance (dissimilarity) that will have more chance to detect failures.
+In other words, MRs with very different initial and follow-up execution are more likely to detect failures than those with similar initial and follow-up executions.
+The concept of “difference” are defined in namely coverage Manhattan distance (CMD), frequency Manhattan distance (FMD), and frequency Hamming distance (FHD) in regard to adaptive random testing (ART), where CMD metric on the basis of branch coverage execution profiles performs the best fault-detection effectiveness.
+ I think the advantage of this article is suitable for finding the most effectiveness of Metamorphic Relations in White-box.
+However, this article is not suitable for Black - Box Testing.
+The reason is Black Box Testing have not source code available, so it cannot calculation the program’s distance.
+In this research project, my testing modeling have not source code available.
+So, I have found another research article (Henard，2016)talking about the difference between black-box testing and white-box testing.
+
+\subparagraph{White-box VS Black-box}
+Henard (2016) have done some research for difference between white box testing
+and black - box testing in 2016. They have two finding is useful in my research
+black-box testing and white-box testing performance just have a little
+difference (at most 4 fault detection rate difference). They also found
+black-box testing and white-box testing the overlap is
+very high. The first 10 of the prioritized test data
+already agree on at least 60 of the faults found. As the
+result, this research article has given me a lot of idea
+for how similar between white box testing and black box
+testing. I still have opportunity for compare those three
+modelings, which one is better.
 
@@
 \section{IQR, Mean, Median, Q1, Q3, lower extreme, upper extreme, mean slope, median slope}
-\subsection{Baidu Chinese Sentiment analysis Positive Probability Base On (Chinese Origin Data)}
+\subsection{Baidu Chinese Sentiment analysis Positive Probability Base On
+  (Chinese Origin Data)}
+\begin{wraptable}{r}{0.5\textwidth}
+\caption{A wrapped table going nicely inside the text.}\label{wrap-tab:1}
 \begin{tabularx}{\textwidth}{ |X|X|X|X|X|X|X|X }
@@
 \end{tabularx}
+\end{wraptable}
 
@@
 \end{tabular}
+\section{Questionnaire}
 

### 2018-08-30 submit/paper.tex
backup

@@
 
-Social Media is becoming more and more popular. There are lots of text comments
+Social Media is becoming more and more widely used. There are lots of text comments
 on different discussion topics every day.
-It would be impossible to analysise the huge amount of data generated manually.
+It would be impossible to analyses the huge amount of data generated manually.
 These topics are discussed by speakers of different languages, from different
 cultural backgrounds, further complicating any analysis.
-Most people enounter language and culture barriers during cross-language
+Most people enounter language and cultureal barriers during cross-language
 communication.
@@
 Sentiment analysis is a part of text data mining. The aim of sentiment analysis
-is to determine the attitude of speakers or writers with respect to some topic
+is to determine the attitude of speakers or writers with respect to particular topics
 or the overall contextual polarity or emotional reaction to a text document. It is usually equated with
@@
 Today, a lot of English language sentiment analysis theories have been
-developed. Also, lots of Machine Translation tools are available, such as Google
+developed. Also, a variety of Machine Translation tools is available, such as Google
 translation, Bing translation and Yandex translation.
@@
 However, nobody working in a combination of these two fields of research has undertaken non-English
-sentiment analysis. Therefore, the research described and discussed in this
-document aimed to create a testing model to find the best-combination of English
+sentiment analysis. Therefore, the research described and discussed in this paper aims to create a testing model to find the best-combination of English
 sentiment analysis tools and machine translation tools to obtain reliable
@@
 do not have such sentiment analysis tools to analyze their own language.
-In the end, everyone to be able to understand different language speakers' attitudes (positive or negative), emotions and opinions.\\
+Eventually, everyone will be able to understand different language speakers' attitudes (positive or negative), emotions and opinions.\\
 \section{Literature Review}
-This research consists of three components.
-Firstly, measuring machine translation service quality.
-Secondly, testing sentiment analysis service quality.
-Thirdly, finding the best compound mode for machine translation service and
+This research consists of three components; measuring machine translation
+service quality; testing sentiment analysis service quality;
+finding the best compound mode for machine translation service and
 sentiment analysis service.
-As a result, this section will fouced doing literature review on machine
+As a result, this section will focus on a review of literature review about machine
 translation, Testing methodology and sentiment analysis.
@@
 
-\paragraph{Around Trip Translation method}
-As Somers argue that they establish an
-around trip translation (RTT) method for detect the quality of machine translation \cite{roundTripTranslation}.
-For example, testing English to Chinese translation tool.
-Firstly, using English to Chinese translation tool translate test data to
-Chinese.
-Secondly, translation Chinese translated data back to English.
+\paragraph{Round Trip Translation method}
+As Somers argues, an Around Trip Translation (RTT) method has been establish to
+detect the quality of machine translation \cite{roundTripTranslation}; for example, testing English to Chinese translation tools.
+Firstly, an English to Chinese translation tool is use to translate test data to
+Chinese. It is then used translate Chinese data back to English.
 Finally, compare the similarity for two English data set.
-They also metion two similarity metrics BLEU and F-score, to judge the
-translations. The limitation of RTT modle are it cannot tell which one is good
-MT from all bad MT tools as well as cannot find which sentences are easier for
+They also mention two metrics of similarity, BLEU and F-score, to judge the
+translations. The limitations of RTT model are it cannot distingicush the best
+MT tool from a group of poor MT tools as well as it cannot find which sentences are easier for
 translation and which sentences are harder for translation.
 
-\paragraph{A monte carlo method for machine translation services}
+\paragraph{A Monte Carlo Method for machine translation services}
 Another article is about using third-party language to test the quality of machine
-translation \cite{thirdPartMachineTranslation}.
-For example, if testing English to Chinese translation tool.
-Firstly, random choice an Intermediate third-party language.
+translation \cite{thirdPartMachineTranslation}, for example, if testing an English to Chinese translation tool.
+Firstly, random choose an Intermediate third-party language.
 Secondly, translation English test data to the third-party language, after
-translation third-party language to Chinese.
-These two steps are only finished one path.
-Another path is a translation in English directly to Chinese.
-In the end, the comparison the two paths of results similarity. In this article, the main
-finding is Google Translate is the best machine translation. In addition, there
-is a tendency to be produced better results in European languages, which use
-ANOVA Statistics method and Pairwise t tests getting this conclusion.
-In my experiment, I also got Google Translator is the best machine translation compare with Yandex and Baidu.
+translates the third-party language to Chinese.
+These two steps constitute one path.
+Another path is translation from English directly to Chinese.
+In the end, the two path results need to compare similarity. In this article, the main
+finding is that Google Translate is the best machine translation. In addition,
+the better results to be produced in European languages, use ANOVA Statistics method and Pairwise T tests getting this conclusion.
+In my experiment, I also got Google Translator is the best machine translation
+compare with Yandex and Baidu. Pairwise T tests also can be useful for find best-combination of English
+sentiment analysis tools and machine translation tools to obtain reliable
+sentiment analysis results. The highlight of this model is using third-party
+language, which can decide preference language of machine translation.
 
@@
 \section{Questionnaire}
+\begin{enumerate}
+\item What is your gender? \\
+  O Male O Female O perfer Not to say
+\item What is your age group? \\
+  O <18ys O 18-24ys O 24-30ys O 30-40ys O 40-50ys O >50ys
+\item What are your areas of interest? (many answers possible) \\
+  O Science and Technology O engineering O entertainment O military O politics O
+  law O literature O Other (please specify) .....................
+\item How often do you use social media ?\\
+  O Hourly O Daily O Weekly O monthly O yearly
+\item How long do you use social media each time? \\
+  O time >= 1 hour O time 30 minutes O 1 hour O 10 minutes to 30 minutes O less than 10 minutes
+\item Which social media platforms do you use regularly ? (many answers possible)\\
+  O Facebook O Twitter O YouTube O Instagram O WeChat O LinkedIn O Weibo O I
+  don't use social media O Other (please specify)
+\item Which language(s) can you understand easily ?\\
+  O English O French O Chinese O Spanish O Vietnamese O Arabic O Indian O
+  Russian O German O Other (please specify)
+\item How interested are you in other culture? \\
+  O Extremely interested O Very interested O Somewhat interested O Not so
+  interested O Not at all interested
+\item How willing are you to understand the contents in an foreign language?\\
+  O Very likely O Likely O Neither likely nor unlikely O Unlikely O Very
+  unlikely
 
+\item How often do you read others' opinion ?\\
+  O Always O Usually O Sometimes O Rarely O Never
+
+\item Which machine translation tool do you use most?\\
+  O Google Translation O Microsoft Bing Translation O Yandex Translation O Baidu
+  Translation O Youdao Translation O Other (please specify) .......
+\item Sentiment analysis tool can determine the attitude (positive or negative)
+  of writers, which can be useful for analyzing a huge amount of comments. Are
+  you willing to use this tool to analyze your interests in social
+  media, such as product comments or restaurant review, etc?\\
+  O Very likely O Likely O Neither likely nor unlikely O Unlikely O Very unlikely
+\end{enumerate}
 \bibliographystyle{IEEEtran}

### 2018-08-30 submit/paper.tex
backup

@@
 
-Social Media is becoming more and more widely used. There are lots of text comments
+Social Media has been becoming more and more widely used. There are lots of text comments
 on different discussion topics every day.
@@
 In the end, the two path results need to compare similarity. In this article, the main
-finding is that Google Translate is the best machine translation. In addition,
+finding is that Google Translate is the best machine translation compare with
+Yandex, Youdao as well as Bing. In addition,
 the better results to be produced in European languages, use ANOVA Statistics method and Pairwise T tests getting this conclusion.
@@
 \subsection{Testing methodology}
-Accounting to Sethi said that there are two categorized testing
+Accounting to Sethi, there are two categorized testing
 techniques, which are Static Testing and Dynamic Testing. The Dynamic Testing
@@
 \paragraph{Metamorphic Testing}
-The proposed of this research project is based on Metamorphic Testing.
+This research project is based on Metamorphic Testing.
 Metamorphic Testing is for testing function correctness.
@@
 well-explained for what is Metamorphic Testing.
-As Zhou said, Metamorphic testing (MT) is a property-based software testing
+As Zhou said, Metamorphic Testing (MT) is a property-based software testing
 method developed for automated test case generation and automated result
@@
 The two outputs need an existing mathematical relation.
-In this example, the relation is “=”. The advantage of Metamorphic testing (MT)
-method, which can automate result verification and test case generation.
+In this example, the relation is “=”. However, MR does not must be an equation,
+it also can be a relation.
+The advantage of Metamorphic testing (MT) method; addressing the test oracle
+problem; testing case generation problem.
 The disadvantage is that cannot detect memory leak or some others insensitivity
@@
 sentiment analysis tools.
-\subparagraph{Effectiveness of Metamorphic Relations}
-I have read an article which was written by Zhou in 2013.
-The main purpose of reading this article is to find the best one among the three testing modelings.
+\paragraph{Effectiveness of Metamorphic Relations}
+\cite{cao2013correlation}
+There is another article which was written by Zhou about Effectiveness of
+Metamorphic Relations in 2013.
+The main purpose of reading this article is trying to find which Metamorphic
+Relations can be most efficient detection failures.
+Round Trip Translation and a Monte Carlo Method can be seen as two Metamorphic Relations.
+
 This article is based on white-box testing, which have source code, as well as the most important conclusion is if the Metamorphic Relations can get bigger distance (dissimilarity) that will have more chance to detect failures.
@@
 
-\subparagraph{White-box VS Black-box}
+\paragraph{White-box VS Black-box}
 Henard (2016) have done some research for difference between white box testing

### 2018-09-05 submit/paper.tex
backup

@@
 \usepackage{xcolor}
+\usepackage{hyperref}
 \usepackage{tabularx}
@@
 \begin{document}
-\title{\huge Cross-language Sentiment Analysis for Social Media}
+\title{\huge Metamorphic Testing in Cross-language Sentiment Analysis for Social Media}
 
@@
 \begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
+  There are huge amount of text comments for discussion different topics in Social
+  Media everday. All of those topics have discusse by different language
+  spearkers. Most of people have language and culture barrier when we doing
+  cross-language communicate with each other. However, cross-language opinion
+  mining is useful for global integration. However, most of researches only fouced on
+  English Sentiment Analysis. In this research, using machine
+  trainslation and sentiment analysis tools to solve this problems. Let people
+  can understand different language speakers' attitudes (positive or negative),
+  emotions and opinions. It is based on Metamorphic Testing method to achieve a
+  testing model for finding which machine translator service combined with which
+  English sentiment analysis service can obtain reliable sentiment analysis
+  result for non-English speaker, who does not have sentiment analysis tool to
+  analysis their own language. As a result, people can use Machine Translation
+  and English Sentiment Analysis doing big data analysis in Social Media.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-sentiment analysis, machine translation
+sentiment analysis, machine translation, Metamorphic Testing, Social Media,
+Cross-Language, Cross-Culture
 \end{IEEEkeywords}
@@
 do not have such sentiment analysis tools to analyze their own language.
-Eventually, everyone will be able to understand different language speakers' attitudes (positive or negative), emotions and opinions.\\
+Eventually, everyone will be able to understand different language speakers'
+attitudes (positive or negative), emotions and opinions.\\
+\section{Part A: Annotated bibliography}
+\nocite{*}
+\bibliographystyle{annotate}
+\bibliography{library}
 \section{Literature Review}
@@
 Firstly, an English to Chinese translation tool is use to translate test data to
-Chinese. It is then used translate Chinese data back to English.
+Chinese. It is then used to translate Chinese data back to English.
 Finally, compare the similarity for two English data set.
@@
 Secondly, translation English test data to the third-party language, after
-translates the third-party language to Chinese.
+translating, the third-party language to Chinese.
 These two steps constitute one path.
@@
 Yandex, Youdao as well as Bing. In addition,
-the better results to be produced in European languages, use ANOVA Statistics method and Pairwise T tests getting this conclusion.
+the better results to be produced in European languages compare with Asian languages, use ANOVA Statistics
+method and Pairwise T tests giving this conclusion.
 In my experiment, I also got Google Translator is the best machine translation
-compare with Yandex and Baidu. Pairwise T tests also can be useful for find best-combination of English
+compare with Yandex and Baidu. Pairwise T tests also can be useful for finding best-combination of English
 sentiment analysis tools and machine translation tools to obtain reliable
@@
 As Zhou said, Metamorphic Testing (MT) is a property-based software testing
-method developed for automated test case generation and automated result
+method developed for automated test case generation and automated results
 verification, based on the effects of some expected properties of the target
@@
 and the result will be 2. In this example people can easily make the judgment,
-correct or not.
-However, people will not easy to make this judgment quickly if input sin (3.7),
-and the calculator gives a output.
+is correct or not.
+However, people will not easly make this judgment quickly if input sin (3.7),
+and the calculator gives an output.
 In a generally acknowledged, Sin (3.7) = sin (3.7 + 360) is correct.
@@
 problem; testing case generation problem.
-The disadvantage is that cannot detect memory leak or some others insensitivity
+The disadvantage is that it cannot detect memory leak or some others insensitivity
 failure situation.
@@
 The main purpose of reading this article is trying to find which Metamorphic
-Relations can be most efficient detection failures.
+Relations can be the most efficient detecting failures.
 Round Trip Translation and a Monte Carlo Method can be seen as two Metamorphic Relations.
-
-This article is based on white-box testing, which have source code, as well as the most important conclusion is if the Metamorphic Relations can get bigger distance (dissimilarity) that will have more chance to detect failures.
-In other words, MRs with very different initial and follow-up execution are more likely to detect failures than those with similar initial and follow-up executions.
-The concept of “difference” are defined in namely coverage Manhattan distance (CMD), frequency Manhattan distance (FMD), and frequency Hamming distance (FHD) in regard to adaptive random testing (ART), where CMD metric on the basis of branch coverage execution profiles performs the best fault-detection effectiveness.
- I think the advantage of this article is suitable for finding the most effectiveness of Metamorphic Relations in White-box.
-However, this article is not suitable for Black - Box Testing.
-The reason is Black Box Testing have not source code available, so it cannot calculation the program’s distance.
-In this research project, my testing modeling have not source code available.
-So, I have found another research article (Henard，2016)talking about the difference between black-box testing and white-box testing.
-
+This article is based on white-box testing, which have source code, as well as
+the most important conclusion is if the Metamorphic Relations can get bigger
+distance (dissimilarity) that will have more chance to detect failures.
+In other words, MRs with very different initial and follow-up execution are more
+likely to detect failures than those with similar initial and follow-up
+executions.
+The concept of ``difference'' are defined in namely coverage Manhattan distance
+(CMD), frequency Manhattan distance (FMD), and frequency Hamming distance (FHD)
+in regard to adaptive random testing (ART), where CMD metric on the basis of
+branch coverage execution profiles performs the best fault-detection
+effectiveness.
+The advantage of this article is suitable for finding the most effectiveness of
+Metamorphic Relations in White-box.
+However, this article is not suitable for Black-Box Testing. The reason is
+Black-Box Testing have not source code available, so it cannot calculate the
+program’s distance.
+In this research project, translation tools have NOT source code available, this
+article is not suitable for this research accordingly.
 \paragraph{White-box VS Black-box}
+\cite{henard2016comparing}
+There are another research article written by Henard in 2016. Talking about the difference between black-box testing and white-box testing.
 Henard (2016) have done some research for difference between white box testing
@@
 already agree on at least 60 of the faults found. As the
-result, this research article has given me a lot of idea
-for how similar between white box testing and black box
+result, this research article has given me a lot of ideas of how the similarity between white-box testing and black-box
 testing. I still have opportunity for compare those three
 modelings, which one is better.
+\section{Research Proposal}\footnote{This research proposal is based on Boyang
+  Yan's Master of Research application (research proposal section) in 2017}
+TITLE: Metamorphic Testing in Cross-language Sentiment Analysis for Social Media
+\paragraph{Background and Research Problems}
+Social Media has been becoming more and more widely used. There are lots of text comments
+on different discussion topics every day.
+It would be impossible to analyses the huge amount of data generated manually.
+These topics are discussed by speakers of different languages, from different
+cultural backgrounds, further complicating any analysis.
+Most people enounter language and cultureal barriers during cross-language
+communication.
+In this research, the use of machine translation and sentiment analysis tools to
+solve this problem of analysing cross-cultural and cross-language data is
+explored and discussed.
+Sentiment analysis is a part of text data mining. The aim of sentiment analysis
+is to determine the attitude of speakers or writers with respect to particular topics
+or the overall contextual polarity or emotional reaction to a text document. It is usually equated with
+opinion mining, which involves the use of natural language processing and
+machine learning to ascertain the possibility of positive or negative opinions
+\cite{sentimentAnalysis}.
+Sentiment analysis is useful for analyzing a huge amount of data relating to personal
+opinions. It can be used in an e-business context. For example, business managers can analysise
+customers' attitudes, as to whether they like or dislike their product or service.
+Also, government can use sentiment analysis to analyze citizen perspectives.
+In a word, sentiment analysis is coming into widespread use.
+As Dr. Haiyun mentions, English language sentiment analysis research has
+undergone major developments in recent years \cite{ChineseSentimentAnalysis}.
+However, less research has been undertaken in other languages, such as Chinese.
+Today, a lot of English language sentiment analysis theories have been
+developed. Also, a variety of Machine Translation tools is available, such as Google
+translation, Bing translation and Yandex translation.
+Manchine Translation uses computational linguistic programs and natural language
+processing theory \cite{machineTranslation}.
+However, nobody working in a combination of these two fields of research has undertaken non-English
+sentiment analysis. Therefore, the research described and discussed in this paper aims to create a testing model to find the best-combination of English
+sentiment analysis tools and machine translation tools to obtain reliable
+sentiment analysis results from non-English texts, for non-English speakers who
+do not have such sentiment analysis tools to analyze their own language.
+Eventually, everyone will be able to understand different language speakers'
+attitudes (positive or negative), emotions and opinions.\\
+The purpose of the study have two aspects.
+The first aims of this research is to compare and analysis Google, Youdao, Baidu, Bing and
+Yandex translation tools, which one is the best machine translation tool.
+Second aim is creating a testing model to find the best-combination of English
+sentiment analysis tools and machine translation tools to obtain reliable
+sentiment analysis results.
+Third aim is to create our own sentiment analysis model for
+recognizing English data belonging to positive, negative, neutral or mix
+classification. It is building by VADER, NLTK, LIWC, ANEW or the General Inquirer.
+\paragraph{Critical Review of Literature}
 
-The three different machine translation testing modeling, we can call the three
-different Metamorphic Relations. So, I have found a research article(Cao,2013)
-about the effectiveness of metamorphic relations.
+\paragraph{Aims and Objectives}
+The aim for this research is to achieve a method to find out which combination
+between machine translation tools and English sentiment analysis model can
+obtain the result, which is the most reliable and efficient, for those
+non-English speakers, to fill the blank and gap of lacking of cross-language
+sentiment analysis tool.
+The main aim can be divided into 4 sub-aims.
+\begin{enumerate}
+  \item Advertisement Detection \\
+Detect advertisements and junk contents among mass of data from social media
+texts. Removing unimportant data can both reduce the amount of the size of whole
+dataset to save processing time, and get rid of contents that is of no use to
+our sentiment analysis, which can be also regarded as noise data.
+  \item Data Preprocessing and Feature Extraction
+Preprocessing data is to segment texts into words and select those words which
+is helpful and sensitive in sentiment analysis. E.g. keywords, important
+punctuation marks, emotion symbols. Also, normalization operations will be taken
+to convert the keywords into it root form, which can reduce the size of lexicons
+of models to a large extend. Then, extracting features of those data being
+preprocessed as inputs for sentiment analysis model built by us.
+  \item Sentiment Analysis Modelling
+Develop a model for sentiment analysis which includes a lexicon placing emphasis on social media texts and a machine learning model for analyzing sentiment.
+The lexicon should consider about the main feature of social media texts below:
+short-text styled, sparsity of contents and concluding emoticons. This can make
+our model performs better than the other ones which focus on general texts.
+For the machine learning model, we aim to design a model which considers about
+efficiency, accuracy and reliability.
+  \item Cross-language Translation and Model Testing
+For our source of data coming from social media which is in different languages,
+finding a better performed tool for translation is of vital importance. We aim
+to find the best performed tool for each respective combination of languages, so
+that we can have closer meaning according to the origin language.
 
-Also, when I finished reading all of the details, I have found Two-way ANOVA is also suitable for part 3 of my research (finding the best compound mode for machine translation service and sentiment analysis service).
-I think that the disadvantages of those three-testing modeling will be involved some of the noise.
- It is clear the Round-Trip will be involved translation back path noise.
-Using the third language will be involved in third language translation path noise.
-My modeling will be involved sentiment analysis tools’ noise.
-However, my modeling does not involve any noise from translation tool.
-I think my modeling is better than the other two testing modeling.
-I am total from another aspect to test translation tool.
+With the final text data, testing should be designed to test the real
+performance of the model we build. And based on the results of testing, we can
+have optimization on relevant domains of our research.
 
-\section{Method}
-\section{Test Data}
-Total have 46180 movies reviews.
-\begin{tabular}{lrl}
-Ranking & Number of Test Data & Percentage\\
-\hline
-Ranking 10 & 7353 & 15.92 \%\\
-Ramking 20 & 11209 & 24.27 \%\\
-Ranking 30 & 16223 & 35.13 \%\\
-Ranking 40 & 7663 & 16.59 \%\\
-Ranking 50 & 3732 & 8.08 \%\\
-\end{tabular}
+\end{enumerate}
 
-\section{IQR, Mean, Median, Q1, Q3, lower extreme, upper extreme, mean slope, median slope}
-\subsection{Baidu Chinese Sentiment analysis Positive Probability Base On
-  (Chinese Origin Data)}
-\begin{wraptable}{r}{0.5\textwidth}
-\caption{A wrapped table going nicely inside the text.}\label{wrap-tab:1}
-\begin{tabularx}{\textwidth}{ |X|X|X|X|X|X|X|X }
-Ranking & IQR & Mean & Median & Q1 & Q3 & lowerExtreme & upperExtreme\\
-\hline
-10 & 0.3426533 & 0.2404781 & 0.1789910 & 0.0489987 & 0.3916520 & -0.4649812 & 0.9056319\\
-20 & 0.3817485 & 0.2949725 & 0.2489580 & 0.0878135 & 0.4695620 & -0.4848092 & 1.0421847\\
-30 & 0.4504405 & 0.3980354 & 0.3808120 & 0.1516095 & 0.6020500 & -0.5240512 & 1.2777107\\
-40 & 0.5255830 & 0.5123376 & 0.5385910 & 0.2461685 & 0.7717515 & -0.5422060 & 1.5601260\\
-50 & 0.5368080 & 0.5712128 & 0.6188395 & 0.3101650 & 0.8469730 & -0.4950470 & 1.6521850\\
-\end{tabularx}
-\end{wraptable}
+\section{Survey - Questionnaire}
 
-\begin{tabular}{rr}
-  \hline
-  Mean Slope & Median Slope \\
-  \hline
-  0.008788344 & 0.0116933 \\
-  \hline
-\end{tabular}
-\section{Questionnaire}
+Link : \hyperlink{https://www.surveymonkey.com/r/GHBDPBL}{https://www.surveymonkey.com/r/GHBDPBL}
+
+\paragraph{}
+The following questionnaire on Survey Monkey composed of 10 questions is used for our research work :
+
+\begin{enumerate}
+    \setlength\itemsep{1em}
+    \item What is your gender ?
+    \begin{enumerate}
+        \item Male
+        \item Female
+        \item Other
+    \end{enumerate}
+    \textit{Initial Code : Gender}
+
+    \item What are your areas of interest ? (many answers possible)
+    \begin{enumerate}
+        \item Sport
+        \item Music
+        \item Watching Videos / Films
+        \item Reading
+        \item Cooking
+        \item Doing Shopping
+        \item Chatting
+        \item Playing Video Games
+        \item Other (please specify)
+    \end{enumerate}
+    \textit{Initial Code : Interest areas}
+
+    \item How often do you use social media ?
+    \begin{enumerate}
+        \item Always
+        \item Usually
+        \item Sometimes
+        \item Rarely
+        \item Never
+    \end{enumerate}
+    \textit{Initial Code : Frequency of social media use}
+
+    \item Which social media do you use regularly ? (many answers possible)
+    \begin{enumerate}
+        \item Facebook
+        \item Twitter
+        \item YouTube
+        \item Instagram
+        \item WeChat
+        \item LinkedIn
+        \item Weibo
+        \item I don't use social media
+        \item Other (please specify)
+    \end{enumerate}
+    \textit{Initial Code : Types of social media}
+    \item Which language(s) can you read ?
+    \begin{enumerate}
+        \item English
+        \item French
+        \item Chinese
+        \item Spanish
+        \item Vietnamese
+        \item Arabic
+        \item Indian
+        \item Russian
+        \item German
+        \item Other (please specify)
+    \end{enumerate}
+    \textit{Initial Code : Language skills}
+
+    \item Are you interested in other cultures ?
+    \begin{enumerate}
+        \item Extremely interested
+        \item Very interested
+        \item Somewhat interested
+        \item Not so interested
+        \item Not at all interested
+    \end{enumerate}
+    \textit{Initial Code : Attitude towards culture}
+
+    \item Are you willing to try to understand a comment in an unknown language ?
+    \begin{enumerate}
+        \item Very likely
+        \item Likely
+        \item Neither likely nor likely
+        \item Unlikely
+        \item Very unlikely
+    \end{enumerate}
+    \textit{Initial Code : Behavior towards unknown languages}
+
 \begin{enumerate}

### 2018-09-05 submit/paper.tex
backup

@@
 \usepackage{cite}
+\usepackage{adjustbox}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \begin{abstract}
-  There are huge amount of text comments for discussion different topics in Social
-  Media everday. All of those topics have discusse by different language
-  spearkers. Most of people have language and culture barrier when we doing
-  cross-language communicate with each other. However, cross-language opinion
-  mining is useful for global integration. However, most of researches only fouced on
-  English Sentiment Analysis. In this research, using machine
-  trainslation and sentiment analysis tools to solve this problems. Let people
-  can understand different language speakers' attitudes (positive or negative),
-  emotions and opinions. It is based on Metamorphic Testing method to achieve a
+  Huge amounts of text comments are posted on different topics in Social
+  Media everday. These topics are discussed in different languages by different language
+  speakers. Most people encounter language and culture barriers when engaging in
+  cross-language communication. Cross-language opinion
+  mining is useful for global integration. However, most research only focuses on
+  English language sentiment analysis, but little research has been conducted on
+  sentiment analysis in languages other than English. This research explores using machine
+  trainslation and sentiment analysis tools to fill this gap. The research
+  identifies a conbination of tools which will enable people to understand different language speakers' attitudes (positive or negative),
+  emotions and opinions. This research is  based on the Metamorphic Testing method to establish a
   testing model for finding which machine translator service combined with which
   English sentiment analysis service can obtain reliable sentiment analysis
-  result for non-English speaker, who does not have sentiment analysis tool to
-  analysis their own language. As a result, people can use Machine Translation
-  and English Sentiment Analysis doing big data analysis in Social Media.
+  results for non-English speakers who do not have sentiment analysis tools to
+  analysis their own language. As a result, people will able to use Machine Translation
+  and English Sentiment Analysis to conduct big data analysis in multi-language Social Media.
 \end{abstract}
@@
 \section{Part A: Annotated bibliography}
-\nocite{*}
-\bibliographystyle{annotate}
-\bibliography{library}
+
 \section{Literature Review}
@@
 Metamorphic Testing is for testing function correctness.
-There is a research article written by Zhou in 2016. This article is
-well-explained for what is Metamorphic Testing.
-As Zhou said, Metamorphic Testing (MT) is a property-based software testing
+A research article written by Zhou in 2016 clearly explains what Metamorphic
+Testing is.
+As Zhou explains, Metamorphic Testing (MT) is a property-based software testing
 method developed for automated test case generation and automated results
@@
 These properties, recognized as metamorphic relations (MRs), serve as essential
-relations among the inputs and outcomes of multiple executions of the target
+relations between the inputs and outcomes of multiple executions of the target
 program.
-For instance, test calculator function correctness will be shown if input 1 + 1,
-and the result will be 2. In this example people can easily make the judgment,
-is correct or not.
-However, people will not easly make this judgment quickly if input sin (3.7),
-and the calculator gives an output.
+For instance, calculator function correctness will be established if the input is 1 + 1,
+and the result is 2. In this example people can easily make the judgment,
+whether the calculator is functioning correctly or not.
+However, people will not be able to easily make this judgment if the input is sin (3.7).
 In a generally acknowledged, Sin (3.7) = sin (3.7 + 360) is correct.
@@
 modelings, which one is better.
-\section{Research Proposal}\footnote{This research proposal is based on Boyang
-  Yan's Master of Research application (research proposal section) in 2017}
-TITLE: Metamorphic Testing in Cross-language Sentiment Analysis for Social Media
-\paragraph{Background and Research Problems}
+\pagebreak
+\pagebreak
+\section{Research Proposal \protect\footnote{This research proposal is based on
+    Boyang Yan's Master of Research application (research proposal section) in
+    2017}}
+\subsection{TITLE}
+Metamorphic Testing in Cross-language Sentiment Analysis for Social Media
+\subsection{Background and Research Problems}
 Social Media has been becoming more and more widely used. There are lots of text comments
@@
 classification. It is building by VADER, NLTK, LIWC, ANEW or the General Inquirer.
-\paragraph{Critical Review of Literature}
+\subsection{Critical Review of Literature}
 
-\paragraph{Aims and Objectives}
-The aim for this research is to achieve a method to find out which combination
+\subsection{Aims and Objectives}
+The aim for this research is to achieve a method to find out the combination
 between machine translation tools and English sentiment analysis model can
@@
 our sentiment analysis, which can be also regarded as noise data.
-  \item Data Preprocessing and Feature Extraction
+  \item Data Preprocessing and Feature Extraction \\
 Preprocessing data is to segment texts into words and select those words which
@@
 preprocessed as inputs for sentiment analysis model built by us.
-  \item Sentiment Analysis Modelling
+  \item Sentiment Analysis Modelling \\
 Develop a model for sentiment analysis which includes a lexicon placing emphasis on social media texts and a machine learning model for analyzing sentiment.
@@
 efficiency, accuracy and reliability.
-  \item Cross-language Translation and Model Testing
+  \item Cross-language Translation and Model Testing \\
 For our source of data coming from social media which is in different languages,
@@
 
-\section{Survey - Questionnaire}
+\subsection{The procedure of the study}
+\begin{enumerate}
+\item {Survey} \\
+  The research conducts a survey to different languages backgrounds people,
+  about what they thinking about globalization, does they want to know different
+  cultural backgrounds people opinions and attitudes. Does they enounter language and cultureal barriers during cross-language
+communication. The purpose of survey is Machine Translation tools and Sentiment
+analysis Tools are useful for people daily life and established connection
+between different cultural people communication.
+\item{Getting test data}\\
+  if in the survey, we can get most of people enounter language and
+  cultureal barriers and insterest in others culture, we can start getting movie
+  reviews data from social media website for finding the best compound mode for machine translation service and
+  sentiment analysis services
+
+\item Testing Machine translation services quality and Sentiment Analysis
+  services quality \\
+  In this part fouce on testing Yandex, Baidu, Google Machine Translation tools,
+  as well as, Baidu, Google sentiment analysis tools. This is testing model,
+  which is according to Metamorphic Testing Method.
+  \begin{minipage}[t]{\linewidth}
+          \raggedright
+          \adjustbox{valign=t}{%
+            \includegraphics[width=.8\linewidth]{./img/testingModel.png}%
+          }
+          \medskip
+  \end{minipage}
+When we testing Machine Translation. We need assuming sentiment analysis tools
+are profect correct. We can compare correlation coefficient between both side of
+sentiment analysis results for getting which machine translation are better.
+There is an example for testing Chinese to English machine translation.
+\begin{enumerate}
+  \item Using Google, Baidu, Yandex translation tools, translated original Chinese data to English data
+  \item Using same sentiment analysis tool analysis original chinese dataset and
+    translated dataset
+  \item Calculate correlation coefficient between Chinese sentiment analysis
+    results and English sentiment analysis results
+  \item Compare correlation coefficient values. if value is bigger than others,
+    we can say this translation tool, which use in original dataset to English
+    dataset, can achieve better results than others.
+  \end{enumerate}
+For testing sentiment analysis tools, we can using same model. We need assuming
+Machine Translation tools are profect correct. If right side of sentiment
+analysis result is opposite attitude with left side of sentiment analysis
+result. We can say we are detected one failure.
+\item {Finding the best compound mode for machine translation service and
+    sentiment analysis services} \\
+  In this part, we totally have 6 kinds of compound model, which are Google
+  translation with Google sentiment analysis; Yandex translation with Google
+  sentiment analysis; Baidu translation with Google sentiment analysis; Google
+  translation with Baidu sentiment analysis; Yandex translation with Baidu
+  sentiment analysis and Baidu translation with Baidu sentiment analysis. we can
+  using mean-square error (MSE) and Receiver operating characteristic (ROC)
+  compare with user rate get the best compound model.
+\item {Create own sentiment analysis model} \\
+  Accounting to Liu said, creating sentiment analysis model have five steps. I will basis
+  on this five steps for create my own model \cite{liu2012survey}.
+  \begin{enumerate}
+    \item{GetTerms - Reduce review to the list of keywords}
+    \item{Filtering - Remove unnecessary keywords that will not add value for
+        sentiment analysis, such as is, but, it etc}
+    \item{Find the Base Word - Convert all inflections to their root word}
+    \item{Make Features - Use the root words as features to indicate the
+        positiveness or negativeness}
+    \item{Classifier - Train a classifier to predict positivity}
+
+  \end{enumerate}
+\end{enumerate}
+\paragraph{Implications or significance of the problem}
+Social Media has been becoming more and more widely used. Accounting to Perrin's
+survey, there are only $7\%$ American adults are use social media in 2005.
+However, social media usage increase rapily, there are $65\%$ American adults are use
+social media untill 2015 \cite{perrin2015social}. In our survey, we also find most of people
+are insterest in different language speakers' opinions and attitudes. In
+addition,
+Most people enounter language and cultureal barriers during cross-language
+communication.
+As Dr. Haiyun mentions, English language sentiment analysis research has
+undergone major developments in recent years \cite{ChineseSentimentAnalysis}.
+However, less research has been undertaken in other languages, such as Chinese.
+Today, a lot of English language sentiment analysis theories have been
+developed. Also, a variety of Machine Translation tools is available, such as Google
+translation, Bing translation and Yandex translation.
+Manchine Translation uses computational linguistic programs and natural language
+processing theory \cite{machineTranslation}.
+However, nobody working in a combination of these two fields of research has undertaken non-English
+sentiment analysis. Therefore, the research described and discussed in this paper aims to create a testing model to find the best-combination of English
+sentiment analysis tools and machine translation tools to obtain reliable
+sentiment analysis results from non-English texts, for non-English speakers who
+do not have such sentiment analysis tools to analyze their own language.
+Eventually, everyone will be able to understand different language speakers'
+attitudes (positive or negative), emotions and opinions.\\
+\paragraph{Expected Outcomes}
+
+\section{Survey - Questionnaire}\label{survey}
 
@@
     \textit{Initial Code : Behavior towards unknown languages}
+       \item How often do you read others' opinion in social media posts ?
+    \begin{enumerate}
+        \item Always
+        \item Usually
+        \item Sometimes
+        \item Rarely
+        \item Never
+    \end{enumerate}
+    \textit{Initial Code : Interest in others' opinion}
 
+    \item Which machine translation tool do you mostly use ?
     \begin{enumerate}
-\item What is your gender? \\
-  O Male O Female O perfer Not to say
-\item What is your age group? \\
-  O <18ys O 18-24ys O 24-30ys O 30-40ys O 40-50ys O >50ys
-\item What are your areas of interest? (many answers possible) \\
-  O Science and Technology O engineering O entertainment O military O politics O
-  law O literature O Other (please specify) .....................
-\item How often do you use social media ?\\
-  O Hourly O Daily O Weekly O monthly O yearly
-\item How long do you use social media each time? \\
-  O time >= 1 hour O time 30 minutes O 1 hour O 10 minutes to 30 minutes O less than 10 minutes
-\item Which social media platforms do you use regularly ? (many answers possible)\\
-  O Facebook O Twitter O YouTube O Instagram O WeChat O LinkedIn O Weibo O I
-  don't use social media O Other (please specify)
-\item Which language(s) can you understand easily ?\\
-  O English O French O Chinese O Spanish O Vietnamese O Arabic O Indian O
-  Russian O German O Other (please specify)
-\item How interested are you in other culture? \\
-  O Extremely interested O Very interested O Somewhat interested O Not so
-  interested O Not at all interested
-\item How willing are you to understand the contents in an foreign language?\\
-  O Very likely O Likely O Neither likely nor unlikely O Unlikely O Very
-  unlikely
+        \item Google Translation
+        \item Microsoft Bing Translation
+        \item Yandex Translation
+        \item Baidu Translation
+        \item Youdao Translation
+        \item Other (please specify)
+    \end{enumerate}
+    \textit{Initial Code : Types of translation tools}
 
-\item How often do you read others' opinion ?\\
-  O Always O Usually O Sometimes O Rarely O Never
+    \item Sentiment analysis tool can determine the attitude (positive or negative) of writers, which can be useful for analyzing a huge amount of comments.
+Are you willing to use this tool for analyzing your interest topic in social media, such as product comments or restaurant review, etc?
+    \begin{enumerate}
+        \item Very likely
+        \item Likely
+        \item Neither likely nor likely
+        \item Unlikely
+        \item Very unlikely
+    \end{enumerate}
+    \textit{Initial Code : Attitude towards sentiment analysis}
 
-\item Which machine translation tool do you use most?\\
-  O Google Translation O Microsoft Bing Translation O Yandex Translation O Baidu
-  Translation O Youdao Translation O Other (please specify) .......
-\item Sentiment analysis tool can determine the attitude (positive or negative)
-  of writers, which can be useful for analyzing a huge amount of comments. Are
-  you willing to use this tool to analyze your interests in social
-  media, such as product comments or restaurant review, etc?\\
-  O Very likely O Likely O Neither likely nor unlikely O Unlikely O Very unlikely
 \end{enumerate}
+
 \bibliographystyle{IEEEtran}

### 2018-10-26 submit/paper.tex
new

@@
   English language sentiment analysis, but little research has been conducted on
-  sentiment analysis in languages other than English. This research explores using machine
-  trainslation and sentiment analysis tools to fill this gap. The research
-  identifies a conbination of tools which will enable people to understand different language speakers' attitudes (positive or negative),
+  sentiment analysis in languages other than English. This research explores
+  this gap using machine translation and sentiment analysis tools. The research
+  identifies a combination of tools which will enable people to understand different language speakers' attitudes (positive or negative),
   emotions and opinions. This research is  based on the Metamorphic Testing method to establish a
@@
   results for non-English speakers who do not have sentiment analysis tools to
-  analysis their own language. As a result, people will able to use Machine Translation
+  analyse their own language. As a result, people will be able to use Machine Translation
   and English Sentiment Analysis to conduct big data analysis in multi-language Social Media.
@@
 on different discussion topics every day.
-It would be impossible to analyses the huge amount of data generated manually.
+It would be impossible to analyse the huge amount of data generated manually.
 These topics are discussed by speakers of different languages, from different
@@
 Sentiment analysis is useful for analyzing a huge amount of data relating to personal
-opinions. It can be used in an e-business context. For example, business managers can analysise
+opinions. It can be used in an e-business context. For example, business managers can analyse
 customers' attitudes, as to whether they like or dislike their product or service.
-Also, government can use sentiment analysis to analyze citizen perspectives.
+Also, government can use sentiment analysis to analyse citizen perspectives.
 In a word, sentiment analysis is coming into widespread use.
@@
 Today, a lot of English language sentiment analysis theories have been
-developed. Also, a variety of Machine Translation tools is available, such as Google
+developed. Also, a variety of Machine Translation tools are available, such as Google
 translation, Bing translation and Yandex translation.
@@
 sentiment analysis results from non-English texts, for non-English speakers who
-do not have such sentiment analysis tools to analyze their own language.
+do not have such sentiment analysis tools to analyse their own language.
 Eventually, everyone will be able to understand different language speakers'
@@
 sentiment analysis service.
-As a result, this section will focus on a review of literature review about machine
+As a result, this section will focus on a review of literature about machine
 translation, Testing methodology and sentiment analysis.
@@
 detect the quality of machine translation \cite{roundTripTranslation}; for example, testing English to Chinese translation tools.
-Firstly, an English to Chinese translation tool is use to translate test data to
+Firstly, an English to Chinese translation tool is used to translate test data to
 Chinese. It is then used to translate Chinese data back to English.
-Finally, compare the similarity for two English data set.
+Finally, there is a comparsion of the similarity of these two English data sets.
 They also mention two metrics of similarity, BLEU and F-score, to judge the
-translations. The limitations of RTT model are it cannot distingicush the best
+translations. The limitations of RTT model are it cannot distinguish the best
 MT tool from a group of poor MT tools as well as it cannot find which sentences are easier for
@@
 \paragraph{A Monte Carlo Method for machine translation services}
-Another article is about using third-party language to test the quality of machine
+Another article wirtten by Pesu et.al (2018) about using third-party language to test the quality of machine
 translation \cite{thirdPartMachineTranslation}, for example, if testing an English to Chinese translation tool.
-Firstly, random choose an Intermediate third-party language.
-Secondly, translation English test data to the third-party language, after
-translating, the third-party language to Chinese.
+Firstly, an Intermediate third-party language is randomly choosen.
+Secondly, translate the English test data to the third-party language, then
+translate the third-party language to Chinese.
 These two steps constitute one path.
@@
 In the end, the two path results need to compare similarity. In this article, the main
-finding is that Google Translate is the best machine translation compare with
-Yandex, Youdao as well as Bing. In addition,
-the better results to be produced in European languages compare with Asian languages, use ANOVA Statistics
+finding is that Google Translate is the best machine translation compared with
+Yandex, Youdao as well as Bing. In addition, Pesu et.al (2018) found that
+the better results produced in European languages compared with Asian languages, use ANOVA Statistics
 method and Pairwise T tests giving this conclusion.
-In my experiment, I also got Google Translator is the best machine translation
-compare with Yandex and Baidu. Pairwise T tests also can be useful for finding best-combination of English
+In this experiment, Google Translator is the best machine translation
+compared with Yandex and Baidu. Pairwise T tests also can be useful for finding best-combination of English
 sentiment analysis tools and machine translation tools to obtain reliable
@@
 \subsection{Testing methodology}
-Accounting to Sethi, there are two categorized testing
+According to Sethi (2017), there are two categorized testing
 techniques, which are Static Testing and Dynamic Testing. The Dynamic Testing
@@
 testing and Non-Functional Testing \cite{testingMethodReview}.
-In my research project, I will focus on Functional Testing on this project.
+In the current research project the focus is on Functional Testing.
 
@@
 The two outputs need an existing mathematical relation.
-In this example, the relation is “=”. However, MR does not must be an equation,
+In this example, the relation is “=”. However, MR could be an equation,
 it also can be a relation.

### 2018-10-26 test.R

@@ -309,11 +309,61 @@ write.csv(upperExtreme, file = "GoogleSentimentAnalysisBaseOnBaiduTranslatedData
 
 
 
+#Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data.
+info <-
+  data %>% group_by(ranking) %>% 
+  summarise(IQR=IQR(Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data.), Mean=mean(Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data.), Median=median(Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data.), Q1=quantile (Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data., probs=0.25), Q3=quantile(Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data., probs=0.75))
+
+lowerExtreme <- info$Q1 - 1.5 * info$IQR
+upperExtreme <- info$Q3 + 1.5 * info$IQR
+info <- cbind(info, lowerExtreme, upperExtreme)
+rm(lowerExtreme, upperExtreme)
+
+#slope first Argument: vector values of independent variable, usually time. Second argument: vector values of dependent variable, usually concentration
+meanSlope <- lm(info$Mean ~ info$ranking)$coeff[2]
+medianSlope <- lm(info$Median ~ info$ranking)$coeff[2]
+
+meanSlope
+medianSlope
+info
 
 
+#Google.English.sentiment.analysis.score.base.on.Google.translated.data.
+info <-
+  data %>% group_by(ranking) %>% 
+  summarise(IQR=IQR(Google.English.sentiment.analysis.score.base.on.Google.translated.data.), Mean=mean(Google.English.sentiment.analysis.score.base.on.Google.translated.data.), Median=median(Google.English.sentiment.analysis.score.base.on.Google.translated.data.), Q1=quantile (Google.English.sentiment.analysis.score.base.on.Google.translated.data., probs=0.25), Q3=quantile(Google.English.sentiment.analysis.score.base.on.Google.translated.data., probs=0.75))
+
+lowerExtreme <- info$Q1 - 1.5 * info$IQR
+upperExtreme <- info$Q3 + 1.5 * info$IQR
+info <- cbind(info, lowerExtreme, upperExtreme)
+rm(lowerExtreme, upperExtreme)
+
[…]

### 2018-12-20 toBrain/paper.tex
backup

%% bare_conf_compsoc.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE Computer
%% Society conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. The IEEE's font choices and paper sizes can   ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

\documentclass[conference,compsoc]{IEEEtran}
% Some/most Computer Society conferences require the compsoc mode option,
% but others may want the standard conference format.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference,compsoc]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
\usepackage{graphicx}
\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  \usepackage[nocompress]{cite}
\else
  % normal IEEE
  \usepackage{cite}
\fi
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.
%
% Note that some packages require special options to format as the Computer
% Society requires. In particular, Computer Society  papers do not use
% compressed citation ranges as is done in typical IEEE papers
% (e.g., [1]-[4]). Instead, they list every citation separately in order
% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
% package with the nocompress option which is supported by cite.sty v4.0
% and later.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a sans serif font rather
% than the serif font used in traditional IEEE formatting and thus the need
% to invoke different subfig.sty package options depending on whether
% compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Metamorphic Testing in Cross-language Sentiment Analysis for Social Media}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Boyang Yan}
  \IEEEauthorblockA{PCL Research Center of Networks and Communications\\
    Peng Cheng Laboratory\\Shenzhen, China\\
    Email: yanby@pcl.ac.cn}
\and
\IEEEauthorblockN{XXXXXXXXX}
\IEEEauthorblockA{XXXXXXXXXXX\\
Springfield, USA\\
Email: XXXXXXX}}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page (and note that there is less available width in this regard for
% compsoc conferences compared to traditional conferences), use this
% alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
  A huge amount of text comments are posted on different topics in Social Media every day. These topics are discussed in different languages by different language speakers. Most people encounter language and culture barriers when engaging in cross-language communication. Cross-language opinion mining is useful for global integration. However, most research only focuses on English language sentiment analysis, but little research has been conducted on sentiment analysis in languages other than English. This research explores using machine translation and sentiment analysis tools to fill this gap. The research identifies a combination of tools which will enable people to understand different language speakers’ attitudes (positive or negative), emotions and opinions. This research is based on the Metamorphic Testing method to establish a testing model for finding which machine translator service combined with which English sentiment analysis service can obtain reliable sentiment analysis results for non-English speakers who do not have sentiment analysis tools to analysis their own language. As a result, people will able to use Machine Translation and English Sentiment Analysis to conduct big data analysis in multi-language Social Media.
\end{abstract}

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
Social Media has been becoming more and more widely used. There are lots of text comments on different discussion topics every day. It would be impossible to analyses the huge amount of data generated manually. These topics are discussed by speakers of different languages, from different cultural backgrounds, further complicating any analysis. Most people encounter language and cultural barriers during cross-language communication.
In this research, the use of machine translation and sentiment analysis tools to solve this problem of analyzing cross-cultural and cross-language data is explored and discussed. Sentiment analysis is a part of text data mining. The aim of sentiment analysis is to determine the attitude of speakers or writers with respect to particular topics or the overall contextual polarity or emotional reaction to a text document. It is usually equated with opinion mining, which involves the use of natural language processing and machine learning to ascertain the possibility of positive or negative opinions [1]. Sentiment analysis is useful for analyzing a huge amount of data relating to personal opinions. It can be used in an e-business context. For example, business managers can analysis customers’ attitudes, as to whether they like or dislike their product or service. Also, government can use sentiment analysis to analyze citizen perspectives.
In a word, sentiment analysis is coming into widespread use. As Dr. Haiyun
mentions, English language sentiment analysis research has undergone major
developments in recent years [2]. However, less research has been undertaken in
other languages, such as Chinese. Today, a lot of English language sentiment
analysis theories have been developed. Also, a variety of Machine Translation
tools is available, such as Google translation, Bing translation and Yandex
translation. Machine Translation uses computational linguistic programs and
natural language processing theory [3]. However, nobody working in a combination
of these two fields of research has undertaken non-English sentiment analysis.
Therefore, the research described and discussed in this paper aims to create a
testing model to find the best-combination of English sentiment analysis tools
and machine translation tools to obtain reliable sentiment analysis results from
non-English texts, for non-English speakers who do not have such sentiment
analysis tools to analyze their own language. Eventually, everyone will be able
to understand different language speakers’ attitudes (positive or negative),
emotions and opinions. The purpose of the study have two aspects. The first aims
of this research is to compare and analysis Google, Youdao, Baidu, Bing and
Yandex translation tools, which one is the best machine translation tool. Second
aim is creating a testing model to find the best-combination of English
sentiment analysis tools and machine translation tools to obtain reliable
sentiment analysis results. Third aim is to create our own sentiment analysis
model for recognizing English data belonging to positive, negative, neutral or
mix classification.

\section{Critical Review of the Literature}
This research consists of three components; measuring machine translation service quality; testing sentiment analysis service quality; finding the best compound mode for machine translation service and sentiment analysis service. As a result, this section will focus on a review of literature review about machine translation, testing methodology and sentiment analysis.
\subsection{Testing in Machine translation}
there are two research articles about testing modeling of machine translation
(MT).

\subsubsection{Round Trip Translation method}
As Somers argues, an Around Trip Translation (RTT) method has been establish to detect the quality of machine translation [4]; for example, testing English to Chinese translation tools. Firstly, an English to Chinese translation tool is use to translate test data to Chinese. It is then used to translate Chinese data back to English. Finally, compare the similarity for two English data set. They also mention two metrics of similarity, BLEU and F-score, to judge the translations. The limitations of RTT model are it cannot distinguish the best MT tool from a group of poor MT tools as well as it cannot find which sentences are easier for translation and which sentences are harder for translation.

\subsubsection{A Monte Carlo Method for machine translation services}
Another article is about using third-party language to test the quality of
machine translation [5], for example, if testing an English to Chinese
translation tool. Firstly, random choose an Intermediate third-party language.
Secondly, translation English test data to the third-party language, after
translating, the third-party language to Chinese. These two steps constitute one
path. Another path is translation from English directly to Chinese. In the end,
the two path results need to compare similarity. In this article, the main
finding is that Google Translate is the best machine translation compare with
Yandex, Youdao as well as Bing. In addition, the better results to be produced
in European languages compare with Asian languages, use ANOVA Statistics method
and Pairwise T tests giving this conclusion. In my experiment, I also got Google
Translator is the best machine translation compare with Yandex and Baidu.
Pairwise T tests also can be useful for finding best-combination of English
sentiment analysis tools and machine translation tools to obtain reliable
sentiment analysis results. The highlight of this model is using third-party
language, which can decide preference language of machine translation.

\section{Testing methodology}
Accounting to Sethi, there are two categorized testing techniques, which are
Static Testing and Dynamic Testing. The Dynamic Testing are divided into three
categories, which are Functional Testing, Structural testing and Non-Functional
Testing [6]. In my research project, I will focus on Functional Testing on this
project.

\subsubsection{Metamorphic Testing}
a)This research project is based on Metamorphic Testing. Metamorphic Testing is for testing function correctness. A research article written by Zhou in 2016 clearly explains what Metamorphic Testing is. As Zhou explains, Metamorphic Testing (MT) is a property-based software testing method developed for automated test case generation and automated results verification, based on the effects of some expected properties of the target program [7]. These properties, recognized as metamorphic relations (MRs), serve as essential relations between the inputs and outcomes of multiple executions of the target program. For instance, calculator function correctness will be established if the input is 1 + 1, and the result is 2. In this example people can easily make the judgment, whether the calculator is functioning correctly or not. However, people will not be able to easily make this judgment if the input is sin (3.7). In a generally acknowledged, Sin (3.7) = sin (3.7 + 360) is correct. In metamorphic testing, the name of 3.7 is the test case. The name of 3.7 + 360 is the follow-up test case. Metamorphic Relation is the relationship between two input test cases as well as the two outputs.
Metamorphic testing is based on Metamorphic Relation. The two outputs need an
existing mathematical relation. In this example, the relation is “=”. However,
MR does not must be an equation, it also can be a relation. The advantage of
Metamorphic testing (MT) method; addressing the test oracle problem; testing
case generation problem. The disadvantage is that it cannot detect memory leak
or some others insensitivity failure situation. However, Metamorphic Testing is
appropriate for testing translation tools and sentiment analysis tools.

\subsubsection{Effectiveness of Metamorphic Relations}
[8] there is another article which was written by Zhou about Effectiveness of
Metamorphic Relations in 2013. The main purpose of reading this article is
trying to find which Metamorphic Relations can be the most efficient detecting
failures. Round Trip Translation and a Monte Carlo Method can be seen as two
Metamorphic Relations. This article is based on white box testing, which have
source code, as well as the most important conclusion is if the Metamorphic
Relations can get bigger distance (dissimilarity) that will have more chance to
detect failures. In other words, MRs with very different initial and follow-up
execution are more likely to detect failures than those with similar initial and
follow-up executions. The concept of “difference” are defined in namely coverage
Manhattan distance (CMD), frequency Manhattan distance (FMD), and frequency
Hamming distance (FHD) in regard to adaptive random testing (ART), where CMD
metric on the basis of branch coverage execution profiles performs the best
fault detection effectiveness. The advantage of this article is suitable for
finding the most effectiveness of Metamorphic Relations in White-box. However,
this article is not suitable for Black Box Testing. The reason is Black-Box
Testing have not source code available, so it cannot calculate the program’s
distance. In this research project, translation tools have NOT source code
available, this article is not suitable for this research accordingly.

\subsubsection{White-box VS Black-box}
There is another research article written by Henard in 2016. Talking about the
difference between black-box testing and white-box testing. Henard (2016) have
done some research for difference between white box testing and black - box
testing in 2016. They have two finding is useful in my research black-box
testing and white-box testing performance just have a little difference (at most
4 fault detection rate difference). They also found black box testing and
white-box testing the overlap is very high. The first 10 of the prioritized test
data already agree on at least 60 of the faults found. As the result, this
research article has given me a lot of ideas of how the similarity between white
box testing and black-box testing. I still have opportunity for compare those
three modeling’s, which one is better [9].

\section{Objectives and Scope}
The aim for this research is to achieve a method to find out the combination between machine translation tools and English sentiment analysis model can obtain the result, which is the most reliable and efficient, for those non-English speakers, to fill the blank and gap of lacking of cross-language sentiment analysis tool. The main aim can be divided into 4 sub-aims.
I.	Advertisement Detection Detect advertisements and junk contents among mass of data from social media texts. Removing unimportant data can both reduce the amount of the size of whole dataset to save processing time, and get rid of contents that is of no use to our sentiment analysis, which can be also regarded as noise data.
II.	Data Preprocessing and Feature Extraction Preprocessing data is to segment texts into words and select those words which is helpful and sensitive in sentiment analysis. E.g. keywords, important punctuation marks, emotion symbols. Also, normalization operations will be taken to convert the keywords into it root form, which can reduce the size of lexicons of models to a large extend. Then, extracting features of those data being preprocessed as inputs for sentiment analysis model built by us.
III.	Sentiment Analysis Modelling Develop a model for sentiment analysis which includes a lexicon placing emphasis on social media texts and a machine learning model for analyzing sentiment. The lexicon should consider about the main feature of social media texts below: short-text styled, sparsity of contents and concluding emoticons. This can make our model performs better than the other ones which focus on general texts. For the machine learning model, we aim to design a model which considers about efficiency, accuracy and reliability.
IV.	Cross-language Translation and Model Testing For our source of data coming
from social media which is in different languages, finding a better performed
tool for translation is of vital importance. We aim to find the best performed
tool for each respective combination of languages, so that we can have closer
meaning according to the origin language. With the final text data, testing
should be designed to test the real performance of the model we build. And based
on the results of testing, we can have optimization on relevant domains of our
research.

\section{Methodology and Procedure of the Study}
d)Getting test data: getting movie reviews data from social media website for finding the best compound mode for machine translation service and sentiment analysis services.
e)Testing Machine translation services quality and Sentiment Analysis services quality --- In this part focus on testing Yandex, Baidu, Google Machine Translation tools, as well as, Baidu, Google sentiment analysis tools. This is testing model, which is according to Metamorphic Testing Method. When we testing Machine Translation, we need to assume sentiment analysis tools perfectly correct. We can compare correlation coefficient between both sides of sentiment analysis results for getting which machine translation are better. There is an example for testing Chinese to English machine translation.
I.	Using Google, Baidu, Yandex translation tools, translated original Chinese data to English data.
II.	Using same sentiment analysis tool analysis original Chinese dataset and translated dataset.
III.	Calculate correlation coefficient between Chinese sentiment analysis results and English sentiment analysis results.
IV.	Compare correlation coefficient values. If value is bigger than others, we can say this translation tool, which use in original dataset to English dataset, can achieve better results than others.
For testing sentiment analysis tools, we can using same model. We need assuming Machine Translation tools are prefect correct. If right side of sentiment analysis result is opposite attitude with left side of sentiment analysis result. We can say we are detected one failure.
f)Finding the best compound mode for machine translation service and sentiment analysis services In this part, we totally have 6 kinds of compound model, which are Google translation with Google sentiment analysis; Yandex translation with Google sentiment analysis; Baidu translation with Google sentiment analysis; Google translation with Baidu sentiment analysis; Yandex translation with Baidu sentiment analysis and Baidu translation with Baidu sentiment analysis. We can using mean-square error (MSE) and Receiver operating characteristic (ROC) compare with user rate get the best compound model.
g)Create own sentiment analysis model Accounting to Liu said, creating sentiment analysis model have five steps. I will basis on this five steps for create my own model [10].
i) Get Terms - Reduce review to the list of keywords
ii) Filtering - Remove unnecessary keywords that will not add value for sentiment analysis, such as is, but, it etc.
iii) Find the Base Word - Convert all inflections to their root word
iv) Make Features - Use the root words as features to indicate the positiveness or negativeness
v) Classifier - Train a classifier to predict positivity.

\section{Implications and Significance of the Problem}
Social Media has been becoming more and more widely used. Accounting to Perrin’s survey, there are only 7% American adults are use social media in 2005. However, social media usage increase rapidly, there are 65% American adults are use social media until 2015 [11].
we also find most of people are interest in different language speakers’
opinions and attitudes. In addition, most people encounter language and cultural
barriers during cross-language communication. As Dr. Haiyun mentions, English
language sentiment analysis research has undergone major developments in recent
years [2]. However, less research has been undertaken in other languages, such
as Chinese. Today, a lot of English language sentiment analysis theories have
been developed. Also, a variety of Machine Translation tools is available, such
as Google translation, Bing translation and Yandex translation. Machine
Translation uses computational linguistic programs and natural language
processing theory [3]. However, nobody working in a combination of these two
fields of research has undertaken non-English sentiment analysis. Therefore, the
research described and discussed in this paper aims to create a testing model to
find the best-combination of English sentiment analysis tools and machine
translation tools to obtain reliable sentiment analysis results from non-English
texts, for non-English speakers who do not have such sentiment analysis tools to
analyze their own language. Eventually, everyone will be able to understand
different language speakers’ attitudes (positive or negative), emotions and
opinions.

\section{Expected Outcomes}
Testing Model: giving the result about which machine translation tool can achieve more accurate translated result. I guess Google > Yandex > Baidu, my model also can finding which of these sentence are hardly for machine translation.
Maybe, all of machine translation tools will change the human being’s attitude (positive and passive attitudes trend to neutral).
For movie review part, User can give impartial rate for movie review, because my testing model for finding the best compound mode for machine translation service and sentiment analysis services dependent on user rate. If user rates are impartial. I can get credible conclusion for which one is the best compound mode. I can use same compound mode to analysis others data.
My testing model can widely use in e-business aspect contributed to
globalization.

\section{Test Data}
Total have 46180 movies reviews.
\begin{center}
  \begin{tabular}{lrl}
    Ranking & Number of Test Data & Percentage\\
    \hline
    Ranking 10 & 7353 & 15.92 \%\\
    Ramking 20 & 11209 & 24.27 \%\\
    Ranking 30 & 16223 & 35.13 \%\\
    Ranking 40 & 7663 & 16.59 \%\\
    Ranking 50 & 3732 & 8.08 \%\\
  \end{tabular}
\end{center}

\section{IQR, Mean, Median, Q1, Q3, lower extreme, upper extreme, mean slope, median slope}
\subsection{Baidu Chinese Sentiment analysis Positive Probability Base On (Chinese Origin Data)}
\begin{center}
\begin{tabular}{rrrrrrrr}
Ranking & IQR & Mean & Median & Q1 & Q3 & lowerExtreme & upperExtreme\\
\hline
10 & 0.3426533 & 0.2404781 & 0.1789910 & 0.0489987 & 0.3916520 & -0.4649812 & 0.9056319\\
20 & 0.3817485 & 0.2949725 & 0.2489580 & 0.0878135 & 0.4695620 & -0.4848092 & 1.0421847\\
30 & 0.4504405 & 0.3980354 & 0.3808120 & 0.1516095 & 0.6020500 & -0.5240512 & 1.2777107\\
40 & 0.5255830 & 0.5123376 & 0.5385910 & 0.2461685 & 0.7717515 & -0.5422060 & 1.5601260\\
50 & 0.5368080 & 0.5712128 & 0.6188395 & 0.3101650 & 0.8469730 & -0.4950470 & 1.6521850\\
\end{tabular}
\end{center}
\begin{itemize}
\item Mean Slope
\end{itemize}
0.008788344
\begin{itemize}
\item Median Slope
\end{itemize}
0.0116933
\subsection{Baidu Sentiment analysis Positive Probability Base On (Google Translated Data)}
\label{sec:org0f265ba}
\begin{center}
\begin{tabular}{rrrrrrrr}
ranking & IQR & Mean & Median & Q1 & Q3 & lowerExtreme & upperExtreme\\
\hline
10 & 0.0992950 & 0.5109406 & 0.512129 & 0.4495650 & 0.5488600 & 0.3006225 & 0.6978025\\
20 & 0.1083630 & 0.5229484 & 0.518486 & 0.4562780 & 0.5646410 & 0.2937335 & 0.7271855\\
30 & 0.1311445 & 0.5396073 & 0.528391 & 0.4674360 & 0.5985805 & 0.2707192 & 0.7952972\\
40 & 0.1795885 & 0.5673052 & 0.543921 & 0.4839135 & 0.6635020 & 0.2145307 & 0.9328848\\
50 & 0.1873947 & 0.5882316 & 0.557420 & 0.5017473 & 0.6891420 & 0.2206551 & 0.9702341\\
\end{tabular}
\end{center}

\begin{itemize}
\item Mean Slope
\end{itemize}
0.001989388
\begin{itemize}
\item Median Slope
\end{itemize}
0.00116017
\subsection{Baidu Sentiment analysis Positive Probability Base On (Yandex Translated Data)}
\label{sec:orga60a215}
\begin{itemize}
\item Mean Slope
\end{itemize}
0.002034071
\begin{itemize}
\item Median Slope
\end{itemize}
0.00139647
\begin{center}
\begin{tabular}{rrrrrrrr}
ranking & IQR & Mean & Median & Q1 & Q3 & lowerExtreme & upperExtreme\\
\hline
10 & 0.1095430 & 0.5180638 & 0.515600 & 0.4527060 & 0.5622490 & 0.2883915 & 0.7265635\\
20 & 0.1132460 & 0.5348823 & 0.524710 & 0.4697750 & 0.5830210 & 0.2999060 & 0.7528900\\
30 & 0.1437290 & 0.5512503 & 0.532877 & 0.4769425 & 0.6206715 & 0.2613490 & 0.8362650\\
40 & 0.1861070 & 0.5825192 & 0.555963 & 0.4933645 & 0.6794715 & 0.2142040 & 0.9586320\\
50 & 0.1965927 & 0.5959489 & 0.569797 & 0.5031990 & 0.6997917 & 0.2083099 & 0.9946809\\
\end{tabular}
\end{center}
\subsection{Baidu Sentiment analysis Positive Probability Base On (Baidu Translated Data)}
\label{sec:org4c768b6}
\begin{itemize}
\item Mean Slope
\end{itemize}
0.002024859
\begin{itemize}
\item Median Slope
\end{itemize}
0.00135257
\begin{center}
\begin{tabular}{rrrrrrrr}
ranking & IQR & Mean & Median & Q1 & Q3 & lowerExtreme & upperExtreme\\
\hline
10 & 0.0998390 & 0.5242141 & 0.5189600 & 0.4636380 & 0.563477 & 0.3138795 & 0.7132355\\
20 & 0.1116160 & 0.5328661 & 0.5240450 & 0.4693390 & 0.580955 & 0.3019150 & 0.7483790\\
30 & 0.1476325 & 0.5502528 & 0.5343010 & 0.4763575 & 0.623990 & 0.2549087 & 0.8454388\\
40 & 0.1813430 & 0.5819689 & 0.5544210 & 0.4933320 & 0.674675 & 0.2213175 & 0.9466895\\
50 & 0.1975785 & 0.6009056 & 0.5714005 & 0.5055505 & 0.703129 & 0.2091828 & 0.9994968\\
\end{tabular}
\end{center}
\subsection{Google Chinese Sentiment Analysis Score Base On (origin Data)}
\begin{itemize}
\item Mean Slope
\end{itemize}
0.01635146
\begin{itemize}
\item Median Slope
\end{itemize}
0.016
\begin{center}
\begin{tabular}{rrrrrrrr}
ranking & IQR & Mean & Median & Q1 & Q3 & lowerExtreme & upperExtreme\\
\hline
10 & 0.7 & -0.2344349 & -0.2 & -0.6 & 0.1  & -1.65 & 1.15 \\
20 & 0.7 & -0.1092783 & 0.0 & -0.5 & 0.2 & -1.55 & 1.25 \\
30 & 0.7 & 0.1289959 & 0.1 & -0.2 & 0.5 & -1.25 & 1.55 \\
40 & 0.7 & 0.3244682 & 0.4  & 0.0 & 0.7 & -1.05 & 1.75 \\
50 & 0.8 & 0.3662647 & 0.4 & 0.0 & 0.8 & -1.2 & 2.00 \\
\end{tabular}
\end{center}

\subsection{Google English Sentiment Analysis Score Base On (Google Translated Data)}
\begin{itemize}
\item Mean Slope
  0.0153968
\end{itemize}
\begin{itemize}
\item Median Slope
  0.015
\end{itemize}

\begin{center}
\begin{tabular}{rrrrrrrr}
ranking & IQR & Mean & Median & Q1 & Q3 & lowerExtreme & upperExtreme\\
\hline
10 & 0.7 & -0.33609411 & -0.4 & -0.7 & 0.0 & -1.75 & 1.05\\
20 & 0.6 & -0.23656883 & -0.2 & -0.6 & 0.0 & -1.5 & 0.90\\
30 & 0.6 & -0.05040375 & 0.0 & -0.4 & 0.2 & -1.3 & 1.10\\
40 & 0.6 & 0.15573535 & 0.1 & -0.1 & 0.5 & -1.00 & 1.40\\
50 & 0.6 & 0.23759378 & 0.2 & 0.0 & 0.6 & -0.90 & 1.50\\
\end{tabular}
\end{center}

\subsection{Google English Sentiment Analysis Score Base On (Yandex Translated Data)}
\begin{itemize}
\item Mean Slope
  0.01467965
\end{itemize}
\begin{itemize}
\item Median Slope
  0.015
\end{itemize}

\begin{center}
\begin{tabular}{rrrrrrrr}
ranking & IQR & Mean & Median & Q1 & Q3 & lowerExtreme & upperExtreme\\
\hline
10 & 0.7 & -0.33472052 & -0.4 & -0.7 & 0.0 & -1.75 & 1.05 \\
20 & 0.6 & -0.22842359 & -0.2 & -0.6 & 0.0 & -1.5 & 0.90 \\
30 & 0.6 & -0.05227147 & 0.0 & -0.4 & 0.2 & -1.3 & 1.10\\
40 & 0.6 & 0.14357301 & 0.1 & -0.1 & 0.5 & -1.00 & 1.40\\
50 & 0.6 & 0.21326367 & 0.2 & 0.0 & 0.6 &-0.90 & 1.50\\
\end{tabular}
\end{center}

\subsection{Google English Sentiment Analysis Score Base On (Baidu Translated Data)}
\label{sec:org56003d4}
\begin{itemize}
\item Mean Slope
\end{itemize}
0.01418969
\begin{itemize}
\item Median Slope
\end{itemize}
0.012
\begin{center}
\begin{tabular}{rrrrrrrr}
ranking & IQR & Mean & Median & Q1 & Q3 & lowerExtreme & upperExtreme\\
\hline
10 & 0.7 & -0.28185775 & -0.3 & -0.7 & 0.0 & -1.75 & 1.05\\
20 & 0.5 & -0.18345972 & -0.1 & -0.5 & 0.0 & -1.25 & 0.75\\
30 & 0.6 & -0.01048511 & 0.0 & -0.3 & 0.3 & -1.20 & 1.20\\
40 & 0.6 & 0.17350907 & 0.1 & -0.1 & 0.5 & -1.00 & 1.40\\
50 & 0.6 & 0.24914255 & 0.2 & 0.0 & 0.6 & -0.90 & 1.50\\
\end{tabular}
\end{center}
\section{Assessing Machine translation tool quality}
\label{sec:org20f5e88}

\subsection{Method}
\label{sec:org73e9c86}
\begin{enumerate}
\item Compare correlation coefficient between Chinese sentiment analysis results and English sentiment analysis results by each
\begin{enumerate}
\item Using Google, Baidu, Yandex translation tools, translated original Chinese data to English data
\item Using same sentiment analysis tool analysis original chinese dataset and translated dataset
\item Calculate correlation coefficient between Chinese sentiment analysis results and English sentiment analysis results
\item Compare correlation coefficient values. if value is bigger than others, we can say this translation tool, which use in original dataset to English dataset, can achieve better results than others.
\end{enumerate}
\end{enumerate}
\subsubsection{Result}
\label{sec:org938a23f}
\begin{itemize}
\item Base on Google sentiment analysis tool
\end{itemize}
\begin{center}
\begin{tabular}{llll}
 & Google Score for Google translated data & Google Score for Yandex translated data & Google Score Baidu translated data\\
\hline
Gooogle Score for origin data & 0.512 (Pearson Correlations)  p-value: 0.0 & 0.506 (Pearson Correlations) p-value: 0.0 & 0.490 (Pearson Correlations)  p-value: 0.0\\
Google Score for origin data & 0.381 (Kendall Correlations)  p-value: 0.0 & 0.375 (Kendall Correlations) p-value: 0.0 & 0.363 (Kendall Correlations) p-value: 0.0\\
Google Score for origin data & 0.504 (Spearman Correlations) p-value: 0.0 & 0.497 (Spearman Correlations) p-value: 0.0 & 0.482 (Spearman Correlations) p-value: 0.0\\
Gooogle Score for origin data & 0.512 (Point Biserial) p-value: 0.0 & 0.506 (Point Biserial) p-value: 0.0 & 0.490 (Point Biserial) p-value: 0.0\\
\end{tabular}
\end{center}

\begin{itemize}
\item Google translation tool quality > Yandex translation tool quality > Baidu translation tool quality
\end{itemize}
\begin{itemize}
\item Base on Baidu sentiment analysis tool
\end{itemize}
\begin{center}
\begin{tabular}{llll}
 & Baidu Positive Probability for Google translated data & Baidu Positive Probability for Yandex translated data & Baidu Positive Probability for Baidu translated data\\
\hline
Baidu Positive Probability for origin data & 0.288 (Pearson Correlations)  p-value: 0.0 & 0.280 (Pearson Correlations)  p-value: 0.0 & 0.237 (Pearson Correlations)   p-value: 0.0\\
Baidu Positive Probability for origin data & 0.188 (Kendall Correlations)  p-value: 0.0 & 0.174 (Kendall Correlations) p-value: 0.0 & 0.146 (Kendall Correlations) p-value:0.0\\
Baidu Positive Probability for origin data & 0.271 (Spearman Correlations)  p-value: 0.0 & 0.249 (Spearman Correlations) p-value: 0.0 & 0.210 (Spearman Correlations) p-value: 0.0\\
Baidu Positive Probability for origin data & 0.288 (Point Biserial) p-value: 0.0 & 0.280 (Point Biserial) p-value: 0.0 & 0.237 (Point Biserial) p-value: 0.0\\
\end{tabular}
\end{center}

\begin{itemize}
\item Google translation tool quality > Yandex translation tool quality > Baidu translation tool quality
\end{itemize}
\begin{center}
\includegraphics[width=.9\linewidth]{../img/heatmap.png}
\end{center}

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}

% Note that the IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.
% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
% labels, the optional argument to \subfloat must be present. If a
% subcaption is not desired, just leave its contents blank,
% e.g., \subfloat[].

% An example of a floating table. Note that, for IEEE style tables, the
% \caption command should come BEFORE the table and, given that table
% captions serve much like titles, are usually capitalized except for words
% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
% and up, which are usually not capitalized unless they are the first or
% last word of the caption. Table text will default to \footnotesize as
% the IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that the IEEE does not put floats in the very first column
% - or typically anywhere on the first page for that matter. Also,
% in-text middle ("here") positioning is typically not used, but it
% is allowed and encouraged for Computer Society conferences (but
% not Computer Society journals). Most IEEE journals/conferences use
% top floats exclusively. 
% Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the
% \fnbelowfloat command of the stfloats package.

\section{Conclusion}
The conclusion goes here.

% conference papers do not normally have an appendix

% use section* for acknowledgment
\ifCLASSOPTIONcompsoc
  % The Computer Society usually uses the plural form
  \section*{Acknowledgments}
\else
  % regular IEEE prefers the singular form
  \section*{Acknowledgment}
\fi

The authors would like to thank...

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

% that's all folks
\end{document}

### 2019-01-18 icse/paper.tex
add veen image

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Difficult Text Analysis of Machine Translation Services base on
  Metamorphic Testing in Social Media}

\author{\IEEEauthorblockN{1\textsuperscript{st} Boyang Yan}
\IEEEauthorblockA{\textit{Research Center of Network and Communications} \\
\textit{Peng Cheng Laboratory}\\
Shenzhen, China \\
yanby@pcl.ac.cn}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address}
}

\maketitle

\begin{abstract}
  A huge amount of text comments are posted on different topics in Social Media
  every day. These topics are discussed in different languages by different
  language speakers. Most people encounter language and culture barriers when
  engaging in cross-language communication.
  Cross-language machine translation is useful for global integration.
  However, most of people are chosen human translation services.
  The reason is human translation services are accuracy and reliable compare
  with machine translation.
  Most research only focuses on ranking the quantity of machine translation
  services but little research has conducted on difficult translation text
  evaluation.
  This research explores what kind of text is difficult to translate for machine
  translation services base on movie comments data. It is useful for improve the quality
  of machine translation services to fill this research gap.
  This research is based on the Metamorphic Testing method to establish a
  testing model which using machine translation service translate original test
  dataset from one language to another language. After, using sentiment analysis
  tool to analyize original test dataset and translated dataset, the results
  should be same polarization (positive or negative). If the results are
  opposite polarization, that means this sentence is difficult for machine
  translation.
  As a result, people will able to use this testing model finding difficult
  sentences and doing specific optimiztion.
\end{abstract}

\begin{IEEEkeywords}
  Metamorphic Testing, machine translation, sentiment analysis, machine
  translation quantity testing, evaluation of machine translation services difficult
\end{IEEEkeywords}

\section{Introduction}
Machine translation services has been becoming more and more widely used, also
more and more popular. Most people encounter language and cultural barriers
during cross-language communication. There are lots of text and documents on different languages need
to translation every day. It would be impossible to translation the huge amount
of data generated manually. Nowadays, there are lots of machine translation
tools are available in the world, such as Google translation, Bing translation,
Yandex, Baidu translation and Youdao translation and so on. In this research,
only compare and evaluation Google translation, Yandex translation and Baidu
translation difficults. Those three translation tools are typical and the most
widespread to used. Google translation tool come from American, Yandex come from
Russia, and Baidu come from China. Accounting to Pesu said machine translation
tools can product better results on European languages compare with Asian
language \cite{pesu2018monte}. So, Chinese to English translation tool is the main
kind of translation languages to analysis translation difficults in the paper.
Evaluation of machine translation services difficults usually need language
expert, who need well-known both languages, to participate. However, language
expert also involves human emotional judgment. Automatic assessment human
language is naturally difficult because of without a test oracle \cite{zhou2016metamorphic}.
In this paper, achieving a testing modle to automatic assessment
without language expert.
Metamorphic testing(MT) is one of property-based software quality testing
method, which alreadly be appoved effective for addressing the non-oracle
problem, such as testing the quality of search engine and the quality of
Unmanned Aerial Vehicle(UAV) flight control application and so on.
Therefore, decideing metamorphic testing to find machine translation services
difficults in non-oracle sitation.
And more specifically, this research raise two questions.
\begin{itemize}
  \item Q1: What is current sitation of the quantity of Chinese to English
    machine translation?
  \item Q2: What is current machine translation difficults between Chinese and English?
\end{itemize}

The rest of paper is organized as three parts. Firstly, domonstration the
quantity of Chinese to English translation services, which are Google
translation, Yandex translation and Baidu translation. This part addresses Q1.
secondly, describtion testing model about finding the difficults of machine
translation.
Thirdly, analyzes the experimental results and discussion. This part will
answer Q2.

\section{domonstration the current quantity of Chinese to English translation services}

\subsection{Test Sample}
All of test sample came from Douban, one of biggest social networking service
platforms in China. This social website attracts more than one hundred million
active visitors per month, and has amassed over sixty-five million registered
users. We then employ the Douban public Application Programming Interfaces
(APIs) to access Chinses-written comments. A typical data structure of harvested
comment is shown as a tuple: [Rating, Raw comments]. Totally, comments have got
46180 in the corpus. User rating total have 5 groups, which are 10, 20, 30, 40
and 50, from negative to positive.
The test sample distribution diagram on below.
\centerline{\includegraphics[width=0.3\paperwidth]{./img/ratingHis.png}}
As you can see, the majority of comments allocate on rating 30. In addition,
there have got more negative comments compare with positive comments.

\subsection{Testing procedures}
\begin{enumerate}
  \item using three of machine translation services to translate Chinese
    original movie comments to English translated movie comments.
    $$P_{(Origin Data)} \rightarrow P^{\prime}_{(Google Translation)}$$
    $$P_{(Origin Data)} \rightarrow P^{\prime}_{(Yandex Translation)}$$
    $$P_{(Origin Data)} \rightarrow P^{\prime}_{(Baidu Translation)}$$
  \item Using Google sentiment analysis tool to analysis $P_{(Origin Data)}$,
    $P^{\prime}_{(Google Translation)}$, $ P^{\prime}_{(Yandex Translation)}$ and $
    P^{\prime}_{(Baidu Translation)}$. Google sentiment analysis APIs will get 2
    values, which are Score and Manitude. The range of Score is between -1 and
    1. If Score more close to 1 means this movie comment more positive, as well
    as, if Score more close to -1 means this movie comment more negative.
  \item Using user rating values (10, 20, 30, 40 or 50) to check Google
    Sentiment Analysis(SA) results $P_{(Origin Data)} $ is True or False. For example, user rating = 10 and Google Chinese SA score between -1
    and -0.6 (mean True) user ranking = 10 and Google Chinese SA score bigger
    than -0.6 (mean False). The decideing True table on below. Else Not in True
    table all False.
    \begin{center}
      \begin{tabular}{|c|c|c|c|}
        \hline
        user rating & Google SA score & True/False \\
        \hline\hline
        10 & $[ \, -1, -0.4 ] \,$ & True \\
        \hline
        20 & $[ \, -0.8, 0 ] \,$ & True \\
        \hline
        30 & $[ \, -0.4, 0.4 ] \,$ & True \\
        \hline
        40 & $[ \, 0, 0.8 ] \,$ & True \\
        \hline
        50 & $[ \, 0.4, 1 ] \,$ & True \\
        \hline
      \end{tabular}
    \end{center}
  \item Using those True or False values as vector combining with Google English
    SA scores (based on $P^{\prime}_{(Google Translation)}$), Google English SA
    scores (based on $ P^{\prime}_{(Yandex Translation)}$) and Google English SA
    scores (based on $P^{\prime}_{(Baidu Translation)}$) draw 3 Receiver operating
    characteristic (ROC) graphics and 3 Precision-recall curves (PRC) graphics.

    ROC curve is often used in evaluation the clinical performance of a
    biochemical test. The ROC curve is based on a series of different binary
    classifier with the true positive rate (sensitivity) as the Y-axis and the
    false positive rate (1-specificity) as the X-axis \cite{ROC}. The traditional
    evaluation must be divided into two categories, and then statistical
    analysis is performed. The ROC curve is different from the traditional
    evaluation method. Instead, an intermediate state is allowed. The test
    results can be divided into multiple ordered classifications then
    statistically analyzed. However, visual interpretation and comparisons of
    ROC curves based on imbalanced data sets can be misleading. An alternative
    to a ROC curve is a precision-recall curve (PRC). PRC might be a better
    choice for imbalanced datasets \cite{davis2006relationship}.
    \includegraphics[width=0.35\paperwidth]{./img/ROCandPRC.png}
    This graphic show those three of machine translation tools all achieve poor
    translation results.
  \item Calculate Area Under The Curve (AUC) values for ROC and PRC.
    \begin{table}[h]
      \caption {Google Translation}
    \begin{center}
      \begin{tabular}{|c|c|}
        \hline
        Curve Types & AUCs \\
        \hline\hline
        ROC & 0.5307797 \\
        \hline
        PRC & 0.5328503 \\
        \hline
      \end{tabular}
    \end{center}
  \end{table}\\

   \begin{table}[h]
      \caption {Yandex Translation}
    \begin{center}
      \begin{tabular}{|c|c|}
        \hline
        Curve Types & AUCs \\
        \hline\hline
        ROC & 0.5251734 \\
        \hline
        PRC & 0.5322736 \\
        \hline
      \end{tabular}
    \end{center}
  \end{table}\\

  \begin{table}[h]
      \caption {Baidu Translation}
    \begin{center}
      \begin{tabular}{|c|c|}
        \hline
        Curve Types & AUCs \\
        \hline\hline
        ROC & 0.5258386 \\
        \hline
        PRC & 0.5302736 \\
        \hline
      \end{tabular}
    \end{center}
  \end{table}\\

  The AUC is between 1.0 and 0.5. The better diagnostic effect will be close to 1.
  \begin{itemize}
  \item AUC has lower accuracy from 0.5 to 0.7
  \item AUC has a certain accuracy from 0.7 to 0.9
  \item AUC has higher accuracy at above 0.9
  \end{itemize}
  When AUC=0.5, it means that the diagnostic method is completely ineffective
  and has no diagnostic value \cite{baiduROC}.
\begin{itemize}
\item For ROC AUCS: It shows \textbf{Google Translation tool} better than
  \textbf{Baidu Translation tool} better than \textbf{Yandex Translation tool}
\item For PRC AUCS: It shows \textbf{Googl Translation tool} better than
  \textbf{Yandex Translation tool} better than \textbf{Baidu Translation tool}
\end{itemize}

\begin{itemize}
\item The number of true value: 23042
\item The number of false value: 23138
\end{itemize}

Alought the dataset is looks balanced, ROC diagram can be trusted. The ranking
of machine translation services' quantity are NOT reliable. The reason is three of translation services
have lower accuracy. In another word, working not properly correct.

\subsection{finding the difficults of machine translation}

\end{enumerate}

\bibliographystyle{IEEEtran}
\bibliography{library}
\end{document}

### 2019-01-18 ROC/PRandROCGoogle.R

@@ -1,4 +1,4 @@
-
+library(ggplot2)
 library(precrec)
 library(knitr)
 
@@ -48,7 +48,7 @@ for (index in c(1:length(dataCopy) ) )
     }
     else{
       dataCopy[index] <- TRUE#FALSE
-      falseCount <- falseCount + 1530
+      falseCount <- falseCount + 1
     }
   }
   else if (data$ranking[index] == 50){

### 2019-01-18 ROC/new.R

@@ -4,63 +4,43 @@ library(knitr)
 
 data <- read.csv(file="goodDataLatest.csv",head=TRUE,sep=",")
 
-ref <- seq(-1, 1, 2 / 5 )
-shif <- 0.2
 dataCopy <- data$Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data.
 trueCount <- 0
 falseCount <- 0
 
 for (index in c(1:length(dataCopy) ) )
 {
-  if (data$ranking[index] == 10){
-    if (dataCopy[index] >= ref[1] - shif && dataCopy[index] <= ref[2] + shif){
-      dataCopy[index] <- FALSE#TRUE
+  if (data$ranking[index] == 10 || data$ranking[index] == 20){
+    if (dataCopy[index] >= -1 && dataCopy[index] <= -0.3){
+      dataCopy[index] <- TRUE
       trueCount <- trueCount + 1
     }
     else{
-      dataCopy[index] <- TRUE#FALSE
-      falseCount <- falseCount + 1
-    }
-  }else if (data$ranking[index] == 20){
-    if (dataCopy[index] >= ref[2] - shif && dataCopy[index] <= ref[3] + shif){
-      dataCopy[index] <- FALSE#TRUE
-      trueCount <- trueCount + 1
-    }
-    else{
-      dataCopy[index] <- TRUE#FALSE
+      dataCopy[index] <- FALSE
       falseCount <- falseCount + 1
     }
   }
   else if (data$ranking[index] == 30){
-    if (dataCopy[index] >= ref[3] - shif && dataCopy[index] <= ref[4] + shif){
-      dataCopy[index] <- FALSE#TRUE
+    if (dataCopy[index] >= -0.3 && dataCopy[index] <= 0.3){
+      dataCopy[index] <- TRUE
       trueCount <- trueCount + 1
     }
     else{
-      dataCopy[index] <- TRUE#FALSE
+      dataCopy[index] <- FALSE
       falseCount <- falseCount + 1
     }
   }
-  else if (data$ranking[index] == 40){
-    if (dataCopy[index] >= ref[4] - shif && dataCopy[index] <= ref[5] + shif){
-      dataCopy[index] <- FALSE#TRUE
+  else if (data$ranking[index] == 40 || data$ranking[index] == 50){
+    if (dataCopy[index] >= 0.3 && dataCopy[index] <= 1){
+      dataCopy[index] <- TRUE
[…]

### 2019-01-18 hist/rankingHist.R

@@ -1,0 +1,27 @@
+install.packages("ggplot2")
+
+library(ggplot2)
+data <- read.csv(file="goodDataLatest.csv",head=TRUE,sep=",")
+
+x <- seq(10, 50, length.out=50)
+df <- with(data, data.frame(x = x, y = dnorm(x, mean(ranking), sd(ranking))))
+
+ggplot(data=data, aes(data$ranking)) + 
+  geom_histogram(col="red", 
+                 aes(fill=..count..),
+                 position="identity",
+                 binwidth = 10
+                 ) +
+  scale_fill_gradient("Count", low = "green", high = "red") +
+  labs(title="Histogram for User Rating") +
+  labs(x="User Rating", y="Count") + 
+  theme(plot.title = element_text(hjust = 0.5))
+
+  geom_line(data = df, aes(x = x, y = y), color = "red")
+
+
+
+
+x <- seq(64, 74, length.out=100)
+df <- with(Galton, data.frame(x = x, y = dnorm(x, mean(parent), sd(parent))))
+p + geom_line(data = data, aes(x = x, y = y), color = "red")

### 2019-01-18 oneSideWithAnotherSideOpposite.R

@@ -1,28 +1,495 @@
+install.packages('VennDiagram')
+install.packages('dplyr')
+install.packages('rtf')
+install.packages('NonCompart')
+install.packages('ncar')
+install.packages('gsubfn')
+library(gsubfn)#multi-argument returns
 library(magrittr)
 library(dplyr)
+
 library(rtf)
 library(NonCompart)
 library(ncar)
-install.packages('VennDiagram')
+
 library(VennDiagram)
 
 
 data <- read.csv(file="goodDataLatest.csv",head=TRUE,sep=",")
 data$ID <- seq.int(nrow(data))
 
+ran = c(0.7, -0.7)
+
 #Google sentiment analysis(Google translation)
 googleSentimentAnalysisGoogleTranslation <- data %>% select(ID, Chinese.origin.data, Google.translated.data, Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data., Google.English.sentiment.analysis.score.base.on.Google.translated.data.) %>%
-  filter( ((Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data. > 0.5) & (Google.English.sentiment.analysis.score.base.on.Google.translated.data. < -0.5)) | ((Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data. < -0.5) & (Google.English.sentiment.analysis.score.base.on.Google.translated.data. > 0.5)) )
+  filter( ((Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data. > ran[1]) & (Google.English.sentiment.analysis.score.base.on.Google.translated.data. < ran[2])) | ((Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data. < ran[2]) & (Google.English.sentiment.analysis.score.base.on.Google.translated.data. > ran[1])) )
 
 
 #Google sentiment analysis(Baidu translation)
 googleSentimentAnalysisBaiduTranslation <- data %>% select(ID, Chinese.origin.data, Baidu.translated.data, Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data., Google.English.sentiment.analysis.score.base.on.Baidu.translated.data.) %>%
[…]

### 2019-01-20 icse/paper.tex
backup

@@
     than -0.6 (mean False). The decideing True table on below. Else Not in True
-    table all False.
+    table all False.\\
     \begin{center}
@@
   \end{table}\\
-
    \begin{table}[h]
@@
    \end{table}\\
-
   \begin{table}[h]
@@
   \end{table}\\
-
   The AUC is between 1.0 and 0.5. The better diagnostic effect will be close to 1.
@@
     \item For PRC AUCS: It shows \textbf{Googl Translation tool} better than
-  \textbf{Yandex Translation tool} better than \textbf{Baidu Translation tool}
+      \textbf{Yandex Translation tool} better than \textbf{Baidu Translation
+        tool}
   \end{itemize}
@@
 
+\end{enumerate}
 Alought the dataset is looks balanced, ROC diagram can be trusted. The ranking
@@
 \subsection{finding the difficults of machine translation}
+\subsection{Testing procedures}
+\begin{enumerate}
+    \item using three of machine translation services to translate Chinese
+    original movie comments to English translated movie comments.
+    $$P_{(Origin Data)} \rightarrow P^{\prime}_{(Google Translation)}$$
+    $$P_{(Origin Data)} \rightarrow P^{\prime}_{(Yandex Translation)}$$
+    $$P_{(Origin Data)} \rightarrow P^{\prime}_{(Baidu Translation)}$$
+  \item Using Google sentiment analysis tool to analysis $P_{(Origin Data)}$,
+    $P^{\prime}_{(Google Translation)}$, $ P^{\prime}_{(Yandex Translation)}$ and $
+    P^{\prime}_{(Baidu Translation)}$. The result are $SA_{(Origin Data)}$,
+    $SA^{\prime}_{(Google Translation)}$, $ SA^{\prime}_{(Yandex Translation)}$ and $
+    SA^{\prime}_{(Baidu Translation)}$
+  \item This three of relations should NOT be opposite attitude
+\begin{itemize}
+  \item R1: $$SA_{(Origin Data)} \longleftrightarrow SA^{\prime}_{(Google Translation)}$$
+  \item R2: $$SA_{(Origin Data)} \longleftrightarrow SA^{\prime}_{(Yandex Translation)}$$
+  \item R3: $$SA_{(Origin Data)} \longleftrightarrow SA^{\prime}_{(Baidu Translation)}$$
+\end{itemize}
 
 \end{enumerate}
+
+\subsection{Analysis}
+R1, R2 and R3 have got failures decideing by one side greater than 0.7 and
+another side smaller than -0.7. In this paper, using veen diagram for show
+failures distribution.
+  \begin{table}[h]
+    \caption {Translation Failures Distribution}
+    \begin{center}
+      \begin{tabular}{|c|c|}
+        \hline
+        Types & Number Of Failures \\
+        \hline\hline
+        google Translation & 137\\
+        \hline
+        Yandex & 129 \\
+        \hline
+        Baidu & 134 \\
+        \hline
+        $Google \cap Baidu$ & 38 \\
+        \hline
+        $Google \cap Yandex$ & 46 \\
+        \hline
+        $Yandex \cap Baidu$ & 37 \\
+        \hline
+        $Yandex \cap Baidu \cap Google$ & 17 \\
+        \hline
+      \end{tabular}
+    \end{center}
+  \end{table}\\
+
+\includegraphics[width=0.35\paperwidth]{./img/veen.png}
 

### 2019-01-22 icse/paper.tex
backup

@@
 In this paper, achieving a testing modle to automatic assessment
-without language expert.
-Metamorphic testing(MT) is one of property-based software quality testing
-method, which alreadly be appoved effective for addressing the non-oracle
-problem, such as testing the quality of search engine and the quality of
-Unmanned Aerial Vehicle(UAV) flight control application and so on.
+without language expert. Metamorphic testing(MT) is one of property-based
+software quality testing method, which alreadly be appoved effective for
+addressing the non-oracle problem, such as testing the quality of search engine
+and the quality of Unmanned Aerial Vehicle(UAV) flight control application and so on.
 Therefore, decideing metamorphic testing to find machine translation services
@@
 answer Q2.
+
+\section{Background}
+\subsection{Metamorphic Testing}
+Metamorphosis Testing(MT) a method for generating test cases, as well as test
+results verification. The most importance component is the metamorphic
+relation(MR). MR is the target application's necessary properties of function in relation to multiple
+inputs and their expected outputs. When people want to assess the
+the accuracy of $\sin$ function. For example, $\sin(2.7)$ is very difficult to
+make a correctness judgment from mathematics aspect. If using Metamorphic
+Testing method to testing $\sin$ function will reduce computational costs and
+more efficient.
+\begin{enumerate}
+\item set a Metamorphic relation: such as $\sin(\alpha) = \cos(\frac{\pi}{2} - \alpha)$
+\item
+
+\end{enumerate}
+However, when using
+Metamorphic Testing method set a metamorphic relation, which is  will less cost . If  make a correctness judgment
+
+which are expected relations among the inputs and
+outputs of multiple executions of the intended program’s functionality.
+
+are an approach for generating both test cases and test results. A central element is a set of metamorphosis
+relationships, which are necessary properties of the objective function or the algorithm in relation to multiple inputs and their expected
+outputs.
+
+Since its first publication, we have witnessed a rapidly increasing body of work examining metamorphic testing from
+various perspectives, including metamorphic relation identification, test case generation, integration with other software engineering
+techniques, and the validation and evaluation of software systems.
+
+In software testing, an inability to determine if software is behaving
+correctly, or producing the correct output, is called the oracle problem [1]. Metamorphic testing (MT) is an approach that can alleviate
+the oracle problem [6, 10], MT has been investigated and adopted by
+a growing number of researchers and practitioners [7, 16, 20, 21, 28],
+successfully uncovering software problems, even in extensively
+tested systems [8, 9, 19]. Central to MT is a set of metamorphic
+relations (MRs), which are expected relations among the inputs and
+outputs of multiple executions of the intended program’s functionality. Instead of examining the behaviour or output for an individual
+input, MT checks the SUT against selected MRs, with violations of
+an MR indicating the presence of a fault.
+An example MR for a database management system is that the
+system should return the same results for a query with the search
+condition “A and B” and a query with the search condition “B and
+A”.
+\subsection{Sentiment Analysis}
 

### 2019-01-23 icse/paper.tex
backup

@@
 results verification. The most importance component is the metamorphic
-relation(MR). MR is the target application's necessary properties of function in relation to multiple
-inputs and their expected outputs. When people want to assess the
-the accuracy of $\sin$ function. For example, $\sin(2.7)$ is very difficult to
+relation (MR). MR is the target application's necessary properties of function in relation to multiple
+inputs and their expected outputs.
+In software testing research field, an incapacity to decide, software product
+the correct output, is called the oracle problem. This usually means cannot
+provide exact correctness reference data. such as, machine translation. Huge and
+complexity systems is very common, no
+When people want to assess the the accuracy of $\sin$ function. For example, $\sin(2.7)$ is very difficult to
 make a correctness judgment from mathematics aspect. If using Metamorphic
 Testing method to testing $\sin$ function will reduce computational costs and
-more efficient.
-\begin{enumerate}
-\item set a Metamorphic relation: such as $\sin(\alpha) = \cos(\frac{\pi}{2} - \alpha)$
-\item
-
+more efficient. There is a testing procedures' example for $\sin$ function.
+\begin{enumerate}\label{itm:procedures}
+\item set a Metamorphic Relation: such as $$\sin(\alpha) = \cos(\frac{\pi}{2} - \alpha)$$
+\item $\sin(2.7)$ and $\cos(\frac{\pi}{2} - 2.7)$ should have same output, if the
+  outputs are different. We can say, the failure have been detected.
 \end{enumerate}
-However, when using
-Metamorphic Testing method set a metamorphic relation, which is  will less cost . If  make a correctness judgment
-
-which are expected relations among the inputs and
-outputs of multiple executions of the intended program’s functionality.
-
-are an approach for generating both test cases and test results. A central element is a set of metamorphosis
-relationships, which are necessary properties of the objective function or the algorithm in relation to multiple inputs and their expected
-outputs.
-
-Since its first publication, we have witnessed a rapidly increasing body of work examining metamorphic testing from
-various perspectives, including metamorphic relation identification, test case generation, integration with other software engineering
-techniques, and the validation and evaluation of software systems.
+However, when using \ref{itm:procedures}'s testing procedures. someone maybe
+ask, $\cos$ function also not reliable, how can use a unreliable function to
+test another function's correctness. There have the boundedness. However, both
+function have got failures at same time, that is small probability event.
 

### 2019-01-24 density.R
backup

@@ -1,0 +1,103 @@
+install.packages("sm")
+
+attach(mtcars)
+library(sm)
+mtcars
+data <- read.csv(file="goodDataLatest.csv",head=TRUE,sep=",")
+d <- density(data$ranking)
+plot(d, main="Kernel Density of Three different Machine Translation Tools")
+polygon(d, col="red", border="blue")
+
+
+d <- density(data$Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data.)
+plot(d, main="Kernel Density of Three different Machine Translation Tools")
+polygon(d, border="blue")
+
+
+d <- density(data$Google.English.sentiment.analysis.score.base.on.Google.translated.data.)
+plot(d, main="Kernel Density of Three different Machine Translation Tools")
+polygon(d, border="blue")
+
+d <- density(data$Google.English.sentiment.analysis.score.base.on.Yandex.translated.data.)
+plot(d, main="Kernel Density of Three different Machine Translation Tools")
+polygon(d, border="blue")
+
+d <- density(data$Google.English.sentiment.analysis.score.base.on.Baidu.translated.data.)
+plot(d, main="Kernel Density of Three different Machine Translation Tools")
+polygon(d, border="blue")
+
+
+
+
+mpg
+# create value labels 
+cyl.f <- factor(cyl, levels= c(4,6,8),
+                labels = c("4 cylinder", "6 cylinder", "8 cylinder")) 
+
+# plot densities 
+sm.density.compare(mpg, cyl, xlab="Miles Per Gallon")
+title(main="MPG Distribution by Car Cylinders")
+
+# add legend via mouse click
+colfill<-c(2:(2+length(levels(cyl.f)))) 
+legend(locator(1), levels(cyl.f), fill=colfill)
+###########################################################################
+new <- data.frame(matrix(ncol = 2, nrow = 0))
+DFlable <- c("data", "lable")
+colnames(new) <- DFlable
+
+#chinese
+index <- 1
+while (index < length(data$Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data.)) {
+  df <- data.frame(data = data$Google.Chinese.sentiment.analysis.score.base.on.Chinese.origin.data.[index], lable = "Chinese")
+  new <- rbind(new, df)
+  index = index + 1
+}
+#Google
+index <- 1
+while (index < length(data$Google.English.sentiment.analysis.score.base.on.Google.translated.data.)) {
[…]

### 2019-01-24 icse/paper.tex
backup

@@
 \usepackage{xcolor}
+\usepackage{CJKutf8}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \begin{document}
-
+\begin{CJK*}{UTF8}{gbsn}
 \title{Difficult Text Analysis of Machine Translation Services base on
@@
 
+\subsection{Language Analysis}
+翻译质量评价总结
+
+主要问题在于以下几个方面：
+第一、词汇问题：
+Google translation:
+1.Error points语序混乱,滥用词汇和用法不正确，顺序混乱，Missing vocabulary,Improper selection of words,The words are raw.
+例如sententChinese“2013最后一场电影 就为恶心画一句号吧”，Sentent
+GoogleTranslation“Let's take a look at the last movie of 2013.”The translation
+is fragmented and incomplete，The wrong translation of words refers to the
+emotional color and stylistic misinterpretation of words。 应翻译为“ The last
+movie is a full stop for nausea in 2013.”
+
+3 of then
+比如,“这片子真垃圾 就最后一点看起来比较有新意”GoogleTranslation和YandexTranslation都翻译了原文“ innovative”。但baiduTranslation用了“new”。
+
+google and baidu
+2.Translation error with noun ，misuse and incorrect usage,Sequential chaos。例如sententChinese“想法不错，可惜节奏把握的不好”，baiduTranslation“The idea is good, but the rhythm of the rhythm is not good”.应翻译为”The idea is good, but it is pity that the rhythm is not good”.
+
+all 3
+没那么烂，比春晚好
+3.Misinterpretation of professional terms and literary terms.比如“春晚”GoogleTranslation准确翻译为 “Spring Festival Gala”，但是YandexTranslation错误地翻译为“show ”。错误地翻译baiduTranslation用了“spring”。
+
+********************************************************************************
+4.望文生意
+google only
+比如“片子没你们说的那么难看”GoogleTranslation翻译为“the film did not you say so ugly”这个“难看”不可翻译为“ugly”，应该翻译为“Boring”；再如，“冯导的电影是非真多”不可以翻译成“Feng's film is not true”，应翻译为“there are a lot of dispute in Feng's film ”。Translation error with noun这个“是非”不可翻译为“is not true”和“right and wrong”,应翻译为“dispute”.
+
+5.目标语背景知识缺乏
+google only
+An expression habit that is not suitable for English,Statement is not smooth，
+比如GoogleTranslation当提到“戴高帽子”时，不可翻译为“wear that tall hat”，应翻译为“Flattery”.
+
+6.词语的感情色彩、语体误译。
+all 3
+Word color misinterpretation refers to the emotional color of words, stylistic
+misinterpretation.原文“很写实，已经不是电影了，明明就是戏剧化的焦点访谈节目，披
+露这个社会这个世界和一些人的嘴脸和生活…”中“嘴脸”这个词,三个翻译软件都翻译为
+“face”根据文中的原意,应该改译“Ugly face;Lewd appearance.”
+!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+第二、Grammatical errors
+1.Sequence disorder、Improper location of attributive、Improper position of adverbial (improper location of time adverbial, place adverbial and other adverbial)、Improper location of clauses.Ingredients are incomplete.The subject is incomplete, the predicate is incomplete, the attributive is incomplete, the adverbial is incomplete, the object is incomplete, etc.
+
+3 all
+比如，原文“明明是搞笑片最后弄成了教育片”baiduTranslation翻译为“It's a funny movie that finally makes an education film”.“that”improper collocation of the main guest Illogical.应该翻译为“Obviously it is a comedy,but it  made into education films finally”;
+GoogleTranslation翻译为“Think of a bad movie, but did not expect to be able to
+rot to this point”;YandexTranslation都翻译了原文“ Thought is a bad film, just
+didn't think it could be rotten to the point ”。baiduTranslation用了“That is a
+bad film, but did not expect to come to this rotten”。三种翻译工具都共同存在的问
+题是“I do think the it is a bad moive,but I did not expect to be able to rot to
+this point”Sequence disorder and Ingredients are incomplete（The subject is
+incomplete）;
+
+google only
+原文“为贪污腐败和商业大俗片辩护的一部元素太多深度太浅的电影”,GoogleTranslation原译“An  element too deep and too shallow to justify corruption and commercial tyranny.”改译“it is a film with too shallow meaning and max lot of element for defend corruption and commercial tyranny”
+
+google only
+2.句子结构方面问题.句子成分残缺不全,语序混乱.
+GoogleTranslation“几小杯葡萄汁，很不新鲜”，错误地翻译为“A few small cups of
+grape juice, very fresh”，应该翻译为“A few small cups of grape juice, it is not
+very fresh”;
+
+GoogleTranslation原句“个人意见，如果想看的同学们可以去买各种打折团购
+之类的票，因为真心不值票价”，错误地翻译为“Personal opinion, if you want to see
+the students can buy all kinds of discount buy tickets, because the true
+worthless fare”，应该翻译为“Personal opinion, if students who want to see the
+film  can buy all kinds of discount tickets, because it is worthless fare”.
+
+baiduTranslation原句“前半段还不错~讽刺的意味很重，最后的道歉有点多余了”，错误地
+翻译为“The first half was good - the irony was very heavy, and the last apology
+was a little redundant”.“-”Improper location of clauses.和“and”The misuse of
+conjunctions应该翻译为“The first half was good with heavy  irony，but the last
+apology was a little redundant”.
+
+3.句子结构方面问题.表示因果关系不清
+GoogleTranslation原文“我是个温和的人，实在是不忍心给太少的星。。。”原译“I am a
+gentle person, and I really do not have the heart to give too few stars. . .”改
+译“I can not ignorant conscience to give too few stars,because I am a gentle
+person”.An expression habit that is not suitable for English,Statement is not
+smooth。
+
+GoogleTranslation原文“为贪污腐败和商业大俗片辩护的一部元素太多深度太浅的电影”,原
+译“An  element too deep and too shallow to justify corruption and commercial
+tyranny.”改译“it is a film with too shallow meaning and max lot of element for
+defend corruption and commercial tyranny”.
+
+\section{Conclusion}
+Google Translation, Yandex Translation and Baidu Translation are basically
+fluent and understandable. However, all of three translation services have get the
+individual words are not properly selected and the language expression does not
+conform to the natural speaking. Some of the mistranslations almost overlap.
+
+\section{analysis of causes}
+Although the length of the movie commentary sentences is short, the vocabulary
+is not difficult and the sentences' structure seems simple, there have got
+lots of colloquial speech and many of words are not formal, which is the main
+reason for the low quality of translation results. Lots of compound
+sentence is hidded. It is more difficult for intelligent machines translation
+services.
+
+\section{future work}
+Due to the differences way of thinking between Chinese and English languages. In
+addition, cultural differences and the limitation of translation corpus.
+Machine translation tools have serious language problems. Machine translation
+researchers must be work with linguistic researchers, who should be paid more
+attention to the corpus, lexical analysis and grammatical analysis.
+
+\section{consideration and suggestion}
+
 \bibliographystyle{IEEEtran}
 \bibliography{library}
+\end{CJK*}
 \end{document}

### 2019-01-25 icse/paper.tex
25.1 backup

@@
   dataset from one language to another language. After, using sentiment analysis
-  tool to analyize original test dataset and translated dataset, the results
+  tool to analyize original test dataset and translated datasets, the results
   should be same polarization (positive or negative). If the results are
@@
   Metamorphic Testing, machine translation, sentiment analysis, machine
-  translation quantity testing, evaluation of machine translation services difficult
+  translation quantity testing, evaluation of machine translation services
+  difficult, natural language
 \end{IEEEkeywords}
@@
 Machine translation services has been becoming more and more widely used, also
-more and more popular. Most people encounter language and cultural barriers
+more and more popular. In especial, machine translation system has significantly increased
+international trade\cite{brynjolfsson2018does}.
+Most people encounter language and cultural barriers
 during cross-language communication. There are lots of text and documents on different languages need
@@
 widespread to used. Google translation tool come from American, Yandex come from
-Russia, and Baidu come from China. Accounting to Pesu said machine translation
+Russia, and Baidu come from China. This three tools all come from the top three
+powerful country. Accounting to Pesu said machine translation
 tools can product better results on European languages compare with Asian
@@
 software quality testing method, which alreadly be appoved effective for
-addressing the non-oracle problem, such as testing the quality of search engine
+addressing the oracle problem, such as testing the quality of search engine
 and the quality of Unmanned Aerial Vehicle(UAV) flight control application and so on.
@@
 \subsection{Metamorphic Testing}
-Metamorphosis Testing(MT) a method for generating test cases, as well as test
-results verification. The most importance component is the metamorphic
-relation (MR). MR is the target application's necessary properties of function in relation to multiple
-inputs and their expected outputs.
+Metamorphosis Testing (MT) is a method for generating test cases, as well as test
+results verification \cite{zhou2017introduction}. The most importance component is the metamorphic
+relation (MR) \cite{chen2003fault}. MR is the target application's necessary
+properties of function in relation to multiple inputs and their expected outputs.
+MT has been researched through more and more researchers constantly strive
+toward and adopted by industries and organizations such as Adobe, NASA and the
+National Institute of Standards and Technology \cite{zhou2018metamorphic}.
 In software testing research field, an incapacity to decide, software product
-the correct output, is called the oracle problem. This usually means cannot
-provide exact correctness reference data. such as, machine translation. Huge and
-complexity systems is very common, no
+the correct output, is called the oracle problem \cite{brown2018metamorphic}.
+This usually means cannot provide exact correctness reference data. such as,
+machine translation. Huge and complexity systems, does not have
+reference data for proving function's correctness, is very common.
 When people want to assess the the accuracy of $\sin$ function. For example, $\sin(2.7)$ is very difficult to
@@
 \item $\sin(2.7)$ and $\cos(\frac{\pi}{2} - 2.7)$ should have same output, if the
-  outputs are different. We can say, the failure have been detected.
+  outputs are different. We can say, this MR have been break, maybe the failure
+  have been detected.
 \end{enumerate}
-However, when using \ref{itm:procedures}'s testing procedures. someone maybe
+However, when using \ref{itm:procedures}'s testing procedures. Someone maybe
 ask, $\cos$ function also not reliable, how can use a unreliable function to
@@
 function have got failures at same time, that is small probability event.
+\subsection{Sentiment Analysis}
+Sentiment analysis is a part of text data mining. The aim of sentiment analysis
+is to determine the attitude of speakers or writers with respect to particular
+topics or the overall contextual polarity or emotional reaction to a text
+document. It is usually equated with opinion mining, which involves the use of
+natural language processing and machine learning to ascertain the possibility of
+positive or negative opinions \cite{yadollahi2017current}. Sentiment analysis is useful for analyzing a
+huge amount of data relating to personal opinions. It can be used in an
+e-business context. For example, business managers can analysis customers’
+attitudes, as to whether they like or dislike their product or service. Also,
+government can use sentiment analysis to analyze citizen perspectives.
+In this paper, we will using Google Sentiment Analysis tool to prove the the
+quantity of Machine Translation. The details of Testing Modle will talk in \ref{testingModle} .
 
-In software testing, an inability to determine if software is behaving
-correctly, or producing the correct output, is called the oracle problem [1]. Metamorphic testing (MT) is an approach that can alleviate
-the oracle problem [6, 10], MT has been investigated and adopted by
-a growing number of researchers and practitioners [7, 16, 20, 21, 28],
-successfully uncovering software problems, even in extensively
-tested systems [8, 9, 19]. Central to MT is a set of metamorphic
-relations (MRs), which are expected relations among the inputs and
-outputs of multiple executions of the intended program’s functionality. Instead of examining the behaviour or output for an individual
-input, MT checks the SUT against selected MRs, with violations of
-an MR indicating the presence of a fault.
-An example MR for a database management system is that the
-system should return the same results for a query with the search
-condition “A and B” and a query with the search condition “B and
-A”.
-\subsection{Sentiment Analysis}
-
-\section{domonstration the current quantity of Chinese to English translation services}
+\section{domonstration the current quantity of Chinese to English translation
+  services} \label{currentQuantity}
 
 \subsection{Test Sample}
-All of test sample came from Douban, one of biggest social networking service
+All of test sample came from Douban\footnote{Douban Website:
+  https://www.douban.com/}, one of biggest social networking service
 platforms in China. This social website attracts more than one hundred million
 active visitors per month, and has amassed over sixty-five million registered
-users. We then employ the Douban public Application Programming Interfaces
+users \cite{doubanStat}. We then employ the Douban public Application Programming Interfaces
 (APIs) to access Chinses-written comments. A typical data structure of harvested
@@
 The test sample distribution diagram on below.
-\centerline{\includegraphics[width=0.3\paperwidth]{./img/ratingHis.png}}
+\begin{figure}[h]
+  \centering
+\includegraphics[width=0.3\paperwidth]{./img/ratingHis.png}
+\caption{User Rating Histogram}
+\label{fig:userRatingHistogram}
+\end{figure}
 As you can see, the majority of comments allocate on rating 30. In addition,
@@
 
-\subsection{Testing procedures}
+\subsection{Testing procedures} \label{testingModle}
+\begin{figure}[h]
+  \centering
+\includegraphics[width=0.35\paperwidth]{./img/model.png}
+\caption{Testing Procedures}
+\label{fig:testingProcedures}
+\end{figure}
+One the below, will explain more details for figure \ref{fig:testingProcedures}.
+
 \begin{enumerate}
@@
     1. If Score more close to 1 means this movie comment more positive, as well
-    as, if Score more close to -1 means this movie comment more negative.
-  \item Using user rating values (10, 20, 30, 40 or 50) to check Google
-    Sentiment Analysis(SA) results $P_{(Origin Data)} $ is True or False. For example, user rating = 10 and Google Chinese SA score between -1
+    as, if Score more close to -1 means this movie comment more negative. In
+    this paper, we have not analysis Manitude, which for distinction mix and neutral.
+  \item\label{itm:testingProcedure3} Using user rating values (10, 20, 30, 40 or 50) to check Google
+    Sentiment Analysis(SA) results $P_{(Origin Data)} $ is True or False. For
+    example, user rating = 10 and Google Chinese SA score between -1
     and -0.6 (mean True) user ranking = 10 and Google Chinese SA score bigger
-    than -0.6 (mean False). The decideing True table on below. Else Not in True
-    table all False.\\
+    than -0.6 (mean False). The decideing True table on below.\\
+     \begin{table}[h]
+      \caption {The Range of Score: True/ False}
      \begin{center}
@@
         50 & $[ \, 0.4, 1 ] \,$ & True \\
+        \hline \hline
+        10 & $( \, -0.4, 1 ] \,$ & False \\
+        \hline
+        20 & $[ \, -1, -0.8) \,$ & False \\
+        \hline
+        20 & $( \, -0.8, 1] \,$ & False \\
+        \hline
+        30 & $[ \, -1, -0.4) \,$ & False \\
+        \hline
+        30 & $( \, 0.4, 1] \,$ & False \\
+        \hline
+        40 & $[ \, -1, 0) \,$ & False \\
+        \hline
+        40 & $( \, 0.8, 1] \,$ & False \\
+        \hline
+        50 & $[ \, -1, 0.4) \,$ & False \\
+        \hline
         \hline
@@
     \end{center}
+  \end{table}
+
+    As you can see, the Google SA score ranges have got some overlap because
+    overlap can decrease the results, machine translation evaluation
+    correctness, influence by the accuracy of Google Sentiment Analysis tool.
   \item Using those True or False values as vector combining with Google English
@@
     ROC curve is often used in evaluation the clinical performance of a
-    biochemical test. The ROC curve is based on a series of different binary
+    biochemical test \cite{zweig1993receiver}. The ROC curve is based on a
+    series of different binary
     classifier with the true positive rate (sensitivity) as the Y-axis and the
@@
     choice for imbalanced datasets \cite{davis2006relationship}.
-    \includegraphics[width=0.35\paperwidth]{./img/ROCandPRC.png}
     This graphic show those three of machine translation tools all achieve poor
     translation results.
+\begin{figure}[h]
+  \centering
+    \includegraphics[width=0.35\paperwidth]{./img/ROCandPRC.png}
+\caption{ROC and PRC graphics}
+\label{fig:ROCandPRC}
+\end{figure}
   \item Calculate Area Under The Curve (AUC) values for ROC and PRC.
@@
     \end{center}
-  \end{table}\\
+  \end{table}
    \begin{table}[h]
@@
      \end{center}
-   \end{table}\\
+   \end{table}
   \begin{table}[h]
@@
   \end{table}\\
-  The AUC is between 1.0 and 0.5. The better diagnostic effect will be close to 1.
-  \begin{itemize}
-  \item AUC has lower accuracy from 0.5 to 0.7
-  \item AUC has a certain accuracy from 0.7 to 0.9
-  \item AUC has higher accuracy at above 0.9
-  \end{itemize}
+  The AUC is between 1.0 and 0.5. The better diagnostic effect will be close to
+  1. The ranking of accuracy is show on Table: \ref{accuracyJudgment}\\\\
+  \begin{table}[h]\label{accuracyJudgment}
+    \caption {ROC and PRC accuracy judgment}
+     \begin{center}
+       \begin{tabular}{|c|c|}
+         \hline
+         AUC value & Accuracy \\
+         \hline\hline
+         $[ \, 0.5, 0.7] \,$ & lower accuracy \\
+         \hline
+         $[ \, 0.7, 0.9] \,$ & certain accuracy \\
+         \hline
+         $[ \, 0.9, 1] \,$ & higher accuracy \\
+         \hline
+       \end{tabular}
+     \end{center}
+   \end{table}
   When AUC=0.5, it means that the diagnostic method is completely ineffective
   and has no diagnostic value \cite{baiduROC}.
-  \begin{itemize}
-  \item For ROC AUCS: It shows \textbf{Google Translation tool} better than
-    \textbf{Baidu Translation tool} better than \textbf{Yandex Translation tool}
-    \item For PRC AUCS: It shows \textbf{Googl Translation tool} better than
-      \textbf{Yandex Translation tool} better than \textbf{Baidu Translation
-        tool}
-  \end{itemize}
+\end{enumerate}
+  \subsection{Current Translation Tool Results Analysis}
+  In the testing Procedures \ref{itm:testingProcedure3}, which is the judgment of Google Chinese
+    Sentiment Analysis(SA) results is True or False, there are totally have find
+    23042 of true value, as well as 23138 of false value. Alought the dataset is
+    looks balanced, ROC diagram can be trusted. The ranking of machine
+    translation services' quantity are NOT reliable. The reason is three of
+    translation services have lower accuracy. In another word, working not
+    properly correct. However, there are still have the ranking of machine
+    translation services' quantity on the below.
+\subsubsection{For ROC AUCS}
+\textbf{It shows Google Translation tool better than Baidu Translation tool better than Yandex Translation tool}
+\subsubsection{For PRC AUCS}
+\textbf{It shows Googl Translation tool better than Yandex Translation tool better than Baidu Translation tool}
 
-\begin{itemize}
-\item The number of true value: 23042
-\item The number of false value: 23138
-\end{itemize}
-
-\end{enumerate}
-Alought the dataset is looks balanced, ROC diagram can be trusted. The ranking
-of machine translation services' quantity are NOT reliable. The reason is three of translation services
-have lower accuracy. In another word, working not properly correct.
-
-\subsection{finding the difficults of machine translation}
+\section{finding the difficults of machine translation}
 \subsection{Testing procedures}
-\begin{enumerate}
-    \item using three of machine translation services to translate Chinese
-    original movie comments to English translated movie comments.
-    $$P_{(Origin Data)} \rightarrow P^{\prime}_{(Google Translation)}$$
-    $$P_{(Origin Data)} \rightarrow P^{\prime}_{(Yandex Translation)}$$
-    $$P_{(Origin Data)} \rightarrow P^{\prime}_{(Baidu Translation)}$$
-  \item Using Google sentiment analysis tool to analysis $P_{(Origin Data)}$,
-    $P^{\prime}_{(Google Translation)}$, $ P^{\prime}_{(Yandex Translation)}$ and $
-    P^{\prime}_{(Baidu Translation)}$. The result are $SA_{(Origin Data)}$,
-    $SA^{\prime}_{(Google Translation)}$, $ SA^{\prime}_{(Yandex Translation)}$ and $
-    SA^{\prime}_{(Baidu Translation)}$
-  \item This three of relations should NOT be opposite attitude
-\begin{itemize}
-  \item R1: $$SA_{(Origin Data)} \longleftrightarrow SA^{\prime}_{(Google Translation)}$$
-  \item R2: $$SA_{(Origin Data)} \longleftrightarrow SA^{\prime}_{(Yandex Translation)}$$
-  \item R3: $$SA_{(Origin Data)} \longleftrightarrow SA^{\prime}_{(Baidu Translation)}$$
-\end{itemize}
-
-\end{enumerate}
-
+The first two step is same with, showing the current quantity of Machine
+Translation Tools in Section \ref{currentQuantity}. Which are get translated
+datasets and sentiment analysis for 4 datasets(Chinese Origin dataset, Yandex
+translation dataset, Google translation dataset and Baidu translation dataset).
+The only different is filting all of opposite polarization (very positive or
+very negative) datasets and create three of Metamorphic Relation (MR).
+\subsubsection{MR1}
+$$SA_{(Origin Data)} \approx SA^{\prime}_{(Google Translation)}$$
+\subsubsection{MR2}
+$$SA_{(Origin Data)} \approx SA^{\prime}_{(Yandex Translation)}$$
+\subsubsection{MR3}
+$$SA_{(Origin Data)} \approx SA^{\prime}_{(Baidu Translation)}$$
 \subsection{Analysis}
-R1, R2 and R3 have got failures decideing by one side greater than 0.7 and
+MR1, MR2 and MR3 have got failures decideing by one side greater than 0.7 and
 another side smaller than -0.7. In this paper, using veen diagram for show
 failures distribution.
+\includegraphics[width=0.35\paperwidth]{./img/veen.png}
+
   \begin{table}[h]
@@
   \end{table}\\
-
-\includegraphics[width=0.35\paperwidth]{./img/veen.png}
 

### 2019-01-28 icse/paper.tex
28.1 backup

@@
 \begin{CJK*}{UTF8}{gbsn}
-\title{Difficult Text Analysis of Machine Translation Services base on
-  Metamorphic Testing in Social Media}
+\title{The paradox of Machine Translation base on Sentiment Analysis polarity:
+  using Metamorphic Testing}
 
@@
 A huge amount of text comments are posted on different topics in Social Media
-  every day. These topics are discussed in different languages by different
-  language speakers. Most people encounter language and culture barriers when
-  engaging in cross-language communication.
-  Cross-language machine translation is useful for global integration.
-  However, most of people are chosen human translation services.
-  The reason is human translation services are accuracy and reliable compare
-  with machine translation.
-  Most research only focuses on ranking the quantity of machine translation
-  services but little research has conducted on difficult translation text
-  evaluation.
-  This research explores what kind of text is difficult to translate for machine
-  translation services base on movie comments data. It is useful for improve the quality
-  of machine translation services to fill this research gap.
-  This research is based on the Metamorphic Testing method to establish a
-  testing model which using machine translation service translate original test
-  dataset from one language to another language. After, using sentiment analysis
-  tool to analyize original test dataset and translated datasets, the results
-  should be same polarization (positive or negative). If the results are
-  opposite polarization, that means this sentence is difficult for machine
-  translation.
-  As a result, people will able to use this testing model finding difficult
-  sentences and doing specific optimiztion.
+ every day. These topics are discussed in different languages by
+ different language speakers. It is necessary for people to use machine
+ translation tools in global integration. However, accuracy and reliable of
+ machine translation tools services is paying close attention by users. The
+ quantity of machine translation services and difficult translation text
+ evaluation have been a hot area of research for several years. It is important
+ for improving the quality of machine translation services to narrow the
+ research gap. The purpose of the paper is to explore what kind of text is
+ difficult to translate for machine translation services base on movie comments
+ data in Douban Movie Community Website. Metamorphic Testing is main method for
+ establishing a testing model which using Google Sentiment Analysis tool to
+ analyze original Chinese movie comments dataset and English translated
+ datasets, which are Google Translation dataset, Yandex Translation dataset and
+ Baibu Translation dataset, both side (Chinese and English) should be same
+ emotional polarization (positive or negative). If the results are opposite
+ polarization, that means this sentence is difficult for machine translation. As
+ a result, people will able to use this testing model finding difficult
+ sentences and doing specific optimiztion. The research result shows that the
+ three translation tools overall quality are poor based on Receiver operating
+ characteristic(ROC) curve and precision-recall curve (PRC).
+ In addition, there are outstanding language problems in machine translation,
+ computer science researchers must be combined with linguistic researchers, so
+ further research of Machine translation should pay enough attention to
+ linguistics research, the expansion of corpus, vocabulary differentiation,
+ grammatical analysis and so on, should be deeply and comprehensively studied.
+
 \end{abstract}
@@
 \begin{IEEEkeywords}
-  Metamorphic Testing, machine translation, sentiment analysis, machine
+  Metamorphic Testing, machine translation, MT4MT, sentiment analysis, machine
   translation quantity testing, evaluation of machine translation services
-  difficult, natural language
+  difficult, natural language, Receiver operating characteristic(ROC) curve,
+  precision-recall curve (PRC)
 \end{IEEEkeywords}
@@
 \section{Introduction}
-Machine translation services has been becoming more and more widely used, also
-more and more popular. In especial, machine translation system has significantly increased
-international trade\cite{brynjolfsson2018does}.
-Most people encounter language and cultural barriers
-during cross-language communication. There are lots of text and documents on different languages need
+Most people encounter language and cultural barriers during cross-language
+communication. There are lots of text and documents on different languages need
 to translation every day. It would be impossible to translation the huge amount
@@
 tools are available in the world, such as Google translation, Bing translation,
-Yandex, Baidu translation and Youdao translation and so on. In this research,
-only compare and evaluation Google translation, Yandex translation and Baidu
-translation difficults. Those three translation tools are typical and the most
-widespread to used. Google translation tool come from American, Yandex come from
-Russia, and Baidu come from China. This three tools all come from the top three
-powerful country. Accounting to Pesu said machine translation
-tools can product better results on European languages compare with Asian
-language \cite{pesu2018monte}. So, Chinese to English translation tool is the main
-kind of translation languages to analysis translation difficults in the paper.
-Evaluation of machine translation services difficults usually need language
-expert, who need well-known both languages, to participate. However, language
-expert also involves human emotional judgment. Automatic assessment human
-language is naturally difficult because of without a test oracle \cite{zhou2016metamorphic}.
-In this paper, achieving a testing modle to automatic assessment
-without language expert. Metamorphic testing(MT) is one of property-based
-software quality testing method, which alreadly be appoved effective for
-addressing the oracle problem, such as testing the quality of search engine
-and the quality of Unmanned Aerial Vehicle(UAV) flight control application and so on.
-Therefore, decideing metamorphic testing to find machine translation services
-difficults in non-oracle sitation.
-And more specifically, this research raise two questions.
+Yandex, Baidu translation and Youdao translation and so on. Machine translation
+services has been becoming more and more widely used, also more and more
+popular. It is necessary for global integration to use Cross-language machine
+translation tools. In especial, machine translation system has significantly
+increased international trade \cite{brynjolfsson2018does}. Most research only
+focuses on ranking the quantity of machine translation services in some field
+\cite{pesu2018monte, aiken2010efficacy, koehn2006manual, somers2005round,
+  shigenobu2007evaluation} but little research has conducted on difficult
+translation text evaluation. In this paper, all of testing data (Origin Chinese
+dataset) from DOUBAN, which is an Social Media website about books, movies,
+music, to study the translation quality of different translation tools.
+Douban film is China's largest and most authoritative
+film sharing and comment community \cite{Douban}.
+Social Media has been becoming more and more widely used.
+Accounting to Perrin’s survey, there are only $7%$ American adults are use
+social media in 2005. However, social media usage increase rapidly, there are
+$65%$ American adults are use social media until 2015 \cite{perrin2015social}.
+Social Media website comment text from the language word level has its unique
+style, such as the text has colloquial vocabulary for the convenience of
+expression. At present, it is urgent to carry out in-depth study
+on this field, which may open up the new field of theoretical research.
+In this study, we only fouced on three of Machine Translation tools, which are
+Google, Yandex and Baidu.
+Google translation tool come from American, Yandex come from Russia, and Baidu
+come from China. This three tools all come from the top three powerful country.
+Accounting to Pesu said machine translation tools can product better results on
+European languages compare with Asian language \cite{pesu2018monte}. So, form
+Chinese to English translation tool is the main kind of translation languages to
+analysis translation difficults in the paper. Evaluation of machine translation
+services difficults usually need language expert, who need well-known both languages, to
+participate. However, language expert also involves human emotional judgment.
+Automatic assessment human language is naturally difficult because of without a
+test oracle \cite{zhou2016metamorphic}. In this paper, achieving a testing modle to automatic
+assessment without language expert. Metamorphic testing(MT) is one of
+property-based software quality testing method, which alreadly be appoved
+effective for addressing the oracle problem, such as testing the quality of
+search engine and the quality of Unmanned Aerial Vehicle(UAV) flight control
+application and so on. Therefore, decideing metamorphic testing to find machine
+translation services difficults in non-oracle sitation. And more specifically,
+this research raise two questions.
+
 \begin{itemize}
@@
 The rest of paper is organized as three parts. Firstly, domonstration the
-quantity of Chinese to English translation services, which are Google
-translation, Yandex translation and Baidu translation. This part addresses Q1.
+quantity of Chinese to English translation services. This part addresses Q1.
 secondly, describtion testing model about finding the difficults of machine
-translation.
-Thirdly, analyzes the experimental results and discussion. This part will
+translation. Thirdly, analyzes the experimental results and discussion. This part will
 answer Q2.
@@
 \includegraphics[width=0.35\paperwidth]{./img/veen.png}
-
   \begin{table}[h]
@@
     \end{center}
-  \end{table}\\
+  \end{table}\\\\
 
-\subsection{Language Analysis}
-翻译质量评价总结
+\section{Language Analysis}
+Google Translation, Yandex Translation and Baibu Translation are created by
+different countries for different audiences, that is to say, the users of groups
+are different. But Google Translation, Yandex Translation and Baidu Translation
+exist lexical and grammatical problems, and some mistranslation is almost
+coincide. The following aspects are the main common problems.
+\subsection{Vocabulary Errors}
+ The points of mistake are mainly manifested as the abuse of vocabulary,
+ incorrect usage, the chaotic sequence, missing vocabulary,as well as improper
+ selection of words.\\
+ Examples:
+ \subsubsection{fragmention sentence}
+\begin{itemize}
+\item Chinese \underline{Origin Movie comment} is:
+  \begin{center}
+    ``2013最后一场电影 就为恶心画一句号吧''
+  \end{center}
+\item The \underline{correct of the translation} is:\\
+    ``This is the last movie in 2013. Let's make a full stop for all of nauseating  movie''
+\item The \underline{Google Translation} is:
+  \begin{center}
+    ``Let's take a look at the last movie of 2013''
+  \end{center}
+\end{itemize}
+  This is extremely negative comment. The hidded meaning is, this is nauseating
+  movie. The Google translated sentence is fragmented and incomplete only
+  translated the first part of original sentence.
 
-主要问题在于以下几个方面：
-第一、词汇问题：
-Google translation:
-1.Error points语序混乱,滥用词汇和用法不正确，顺序混乱，Missing vocabulary,Improper selection of words,The words are raw.
-例如sententChinese“2013最后一场电影 就为恶心画一句号吧”，Sentent
-GoogleTranslation“Let's take a look at the last movie of 2013.”The translation
-is fragmented and incomplete，The wrong translation of words refers to the
-emotional color and stylistic misinterpretation of words。 应翻译为“ The last
-movie is a full stop for nausea in 2013.”
+ \subsubsection{misunderstand of vocabulary}
+\begin{itemize}
+\item Chinese \underline{Origin Movie comment} is:
+  \begin{center}
+    ``这片子真垃圾 就最后一点看起来比较有新意''
+  \end{center}
+\item The \underline{correct of the translation} is:\\
+  ``This is really crap movie. However, the last part of movie is considerable innovative.
+\item The \underline{Google Translation} is:\\
+  ``This piece of real garbage on the last point looks more innovative''
+\item The \underline{Yandex Translation} is:\\
+  ``This film is really garbage it finally looks relatively new''
+\item The \underline{Baidu Translation} is:\\
+  ``The film is really garbage and it looks new at the last point.''
+\end{itemize}
+The original Chinese sentence front part is negative, but the back half sentence
+is positive. This three of machine translation tools have got lots of vocabulary
+misunderstand. such as, $$ movie \rightarrow piece $$ $$last\ part\ of\ movie \rightarrow finally\
+or\ the\ last\ point$$
 
-3 of then
-比如,“这片子真垃圾 就最后一点看起来比较有新意”GoogleTranslation和YandexTranslation都翻译了原文“ innovative”。但baiduTranslation用了“new”。
+Besides,
+\begin{itemize}
+\item Chinese \underline{Origin Movie comment} is:
+  \begin{center}
+    ``剧本不好，梗比较生硬，有点无厘头。''
+  \end{center}
+\item The \underline{correct of the translation} is:\\
+  ``The scenario is not good, the punchline of movie is stiff and a little bit
+  does not make sense.''
+\item The \underline{Google Translation} is:\\
+  ``The script is not good, terrier stiffer, a bit nonsense.''
+\item The \underline{Yandex Translation} is:\\
+  ``The script is bad, stem relatively stiff, a bit does not make sense.''
+\item The \underline{Baidu Translation} is:\\
+  ``The script is not good, the stem is relatively stiff, a little silly.''
+\end{itemize}
+The original Chinese sentence is clear negative. All of three tools have got
+problem with punchline of movie, ``梗'' is the internet lingo word. All of tools
+need to improve the Internet lingo words. In addition, three of translation
+tools also have got others misinterpretation of professional terms and literary
+terms. such as ``春晚'' (Spring Festival Gala Show).
 
-google and baidu
-2.Translation error with noun ，misuse and incorrect usage,Sequential chaos。例如sententChinese“想法不错，可惜节奏把握的不好”，baiduTranslation“The idea is good, but the rhythm of the rhythm is not good”.应翻译为”The idea is good, but it is pity that the rhythm is not good”.
+\subsection{Grammatical Errors}
+The machine translation have got lots of grammatical mistake, such as sequence
+disorder, improper location of adverbial attributive. The subject, the
+predicate, the attributive, the adverbial, and the object is incomplete, etc.
+\subsubsection{Illogical connect}
+\begin{itemize}
+\item Chinese \underline{Origin Movie comment} is:
+  \begin{center}
+    ``明明是搞笑片最后弄成了教育片''
+  \end{center}
+\item The \underline{correct of the translation} is:\\
+  ``Obviously it is a comedy,but it made into educational films finally''
+\item The \underline{Baidu Translation} is:\\
+  ``It's a funny movie that finally makes an education film''
+\end{itemize}
+The ``that'' is illogical to connect Subject part and subordinate clause.
+\subsubsection{Incomplete ingredients}
+Origin Chinese sentence is ``中间确实无聊得很，但是结尾不赖''. The original
+sentence meaning ``It's really boring in the middle part, but it's not bad at
+the end''. The Yandex Translation ``The middle of really boring very, however at the end''.
+\subsubsection{Sequence Disorder}
+``想过是烂片，只是没想到能烂到这种地步，太应付了，一个星期拍完的吧''
+Google
+``Think of a bad movie, but did not expect to be able to rot to this point, too
+coping, a week finished it''
+Yandex
+``Thought is a bad film, just didn't think it could be rotten to the point where
+too cope with, a week finished.''
+baidu
+``That is a bad film, but did not expect to come to this rotten, too for a week, finished.''
 
-all 3
-没那么烂，比春晚好
-3.Misinterpretation of professional terms and literary terms.比如“春晚”GoogleTranslation准确翻译为 “Spring Festival Gala”，但是YandexTranslation错误地翻译为“show ”。错误地翻译baiduTranslation用了“spring”。
+The problem of sentence structure.Incomplete sentence composition, confusion of
+words order.
 
-********************************************************************************
-4.望文生意
-google only
-比如“片子没你们说的那么难看”GoogleTranslation翻译为“the film did not you say so ugly”这个“难看”不可翻译为“ugly”，应该翻译为“Boring”；再如，“冯导的电影是非真多”不可以翻译成“Feng's film is not true”，应翻译为“there are a lot of dispute in Feng's film ”。Translation error with noun这个“是非”不可翻译为“is not true”和“right and wrong”,应翻译为“dispute”.
+For example, original sentence meaning”A few small cups of grape
+juice, it is not very fresh”.GoogleTranslation ”A few small cups of grape juice,
+very fresh”in completely different meaning;
 
-5.目标语背景知识缺乏
-google only
-An expression habit that is not suitable for English,Statement is not smooth，
-比如GoogleTranslation当提到“戴高帽子”时，不可翻译为“wear that tall hat”，应翻译为“Flattery”.
+Take another example,original
+sentence meaning “ The first story is good, but the other is too
+contrived”.
+YandexTranslation”On the first story good the other is too
+contrived”;
 
-6.词语的感情色彩、语体误译。
-all 3
-Word color misinterpretation refers to the emotional color of words, stylistic
-misinterpretation.原文“很写实，已经不是电影了，明明就是戏剧化的焦点访谈节目，披
-露这个社会这个世界和一些人的嘴脸和生活…”中“嘴脸”这个词,三个翻译软件都翻译为
-“face”根据文中的原意,应该改译“Ugly face;Lewd appearance.”
-!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-第二、Grammatical errors
-1.Sequence disorder、Improper location of attributive、Improper position of adverbial (improper location of time adverbial, place adverbial and other adverbial)、Improper location of clauses.Ingredients are incomplete.The subject is incomplete, the predicate is incomplete, the attributive is incomplete, the adverbial is incomplete, the object is incomplete, etc.
+Besides,For example,original sentence meaning “The first half was
+good with heavy irony, but the last apology was a little
+redundant”.
 
-3 all
-比如，原文“明明是搞笑片最后弄成了教育片”baiduTranslation翻译为“It's a funny movie that finally makes an education film”.“that”improper collocation of the main guest Illogical.应该翻译为“Obviously it is a comedy,but it  made into education films finally”;
-GoogleTranslation翻译为“Think of a bad movie, but did not expect to be able to
-rot to this point”;YandexTranslation都翻译了原文“ Thought is a bad film, just
-didn't think it could be rotten to the point ”。baiduTranslation用了“That is a
-bad film, but did not expect to come to this rotten”。三种翻译工具都共同存在的问
-题是“I do think the it is a bad moive,but I did not expect to be able to rot to
-this point”Sequence disorder and Ingredients are incomplete（The subject is
-incomplete）;
+BaiduTranslation”The first half was good - the irony was very heavy,
+and the last apology was a little redundant”. Improper location of clauses”-”.
+The misuse of conjunctions”and”.
 
-google only
-原文“为贪污腐败和商业大俗片辩护的一部元素太多深度太浅的电影”,GoogleTranslation原译“An  element too deep and too shallow to justify corruption and commercial tyranny.”改译“it is a film with too shallow meaning and max lot of element for defend corruption and commercial tyranny”
+The problem of sentence structure.Causality is unclear. For example,original
+sentence meaning "I can not ignorant conscience to give too few stars,because I
+am a gentle person”.GoogleTranslation "I am a gentle person, and I really do not
+have the heart to give too few stars. . .”
 
-google only
-2.句子结构方面问题.句子成分残缺不全,语序混乱.
-GoogleTranslation“几小杯葡萄汁，很不新鲜”，错误地翻译为“A few small cups of
-grape juice, very fresh”，应该翻译为“A few small cups of grape juice, it is not
-very fresh”;
+Take another example,original sentence meaning “Bad,I will never see Feng
+Xiaogang's movie again.”  YandexTranslation “Sucks, feel Feng Xiaogang movie
+later never to see.”
 
-GoogleTranslation原句“个人意见，如果想看的同学们可以去买各种打折团购
-之类的票，因为真心不值票价”，错误地翻译为“Personal opinion, if you want to see
-the students can buy all kinds of discount buy tickets, because the true
-worthless fare”，应该翻译为“Personal opinion, if students who want to see the
-film  can buy all kinds of discount tickets, because it is worthless fare”.
+从以上以豆瓣电影评论为分析对象来讨论这三个翻译软件的译文共同的问题，从整体上看，
+无论是用词还是语法都一定的错误导致许多译文意思不准确，内容残缺，结构错误。
 
-baiduTranslation原句“前半段还不错~讽刺的意味很重，最后的道歉有点多余了”，错误地
-翻译为“The first half was good - the irony was very heavy, and the last apology
-was a little redundant”.“-”Improper location of clauses.和“and”The misuse of
-conjunctions应该翻译为“The first half was good with heavy  irony，but the last
-apology was a little redundant”.
+ From the overall points of view, above the Douban film review as the analysis
+ object to discuss GoogleTranslation, YandexTranslation and BaiduTranslation
+ tools common problems, whether the usage of words or grammar are a certain
+ error caused by many translation inaccurate meaning, incomplete content, and
+ the wrong structure.
 
-3.句子结构方面问题.表示因果关系不清
-GoogleTranslation原文“我是个温和的人，实在是不忍心给太少的星。。。”原译“I am a
-gentle person, and I really do not have the heart to give too few stars. . .”改
-译“I can not ignorant conscience to give too few stars,because I am a gentle
-person”.An expression habit that is not suitable for English,Statement is not
-smooth。
+ The reasons are colloquial language characters of Douban film review text and
+ insufficient machine vocabulary.Although the length of the movie commentary
+ sentences is short, the vocabulary is not difficult and the sentences’structure
+ seems simple, there have got lots of colloquial speech and many of words are
+ not formal, which is the main reason for the low quality of translation
+ results. Lots of compound sentence is hidded. It is more difficult for
+ intelligent machines translation services.Although the length of the movie
+ commentary sentences is short, the vocabulary is not difficult and the
+ sentences’structure seems simple, there have got lots of colloquial speech and
+ many of words are not formal, which is the main reason for the low quality of
+ translation results. Lots of compound sentence is hidded. It is more difficult
+ for intelligent machines translation services.
 
-GoogleTranslation原文“为贪污腐败和商业大俗片辩护的一部元素太多深度太浅的电影”,原
-译“An  element too deep and too shallow to justify corruption and commercial
-tyranny.”改译“it is a film with too shallow meaning and max lot of element for
-defend corruption and commercial tyranny”.
-
-\section{Conclusion}
-Google Translation, Yandex Translation and Baidu Translation are basically
-fluent and understandable. However, all of three translation services have get the
-individual words are not properly selected and the language expression does not
-conform to the natural speaking. Some of the mistranslations almost overlap.
-
-\section{analysis of causes}
  Although the length of the movie commentary sentences is short, the vocabulary
@@
 
+Although the online translation text comments and review is short in length, but
+more colloquial is serious, the use of words is not standard, so vocabulary
+translation is more difficult.Although the sentence structure seems simple, but
+hides the compound sentence, but the sentence pattern is rich and
+complex.Besides,Differences in thinking between Chinese and English is more
+difficult for intelligent machines, which is the main difficulty in the quality
+difficulties of translation
+
+ \section{Conclusion and Limitations}
+In general, Google Translation, Yandex Translation and Baidu Translation tools
+can still translate the basic meaning of a sentence. They are basically fluent
+and understandable. However, all of three Machine Translation tools are poor
+quality and similar. As you can seen, this tesing model is possible to detected Machine
+Translation failures without language expert. But, there have got limitation in
+the accuracy of Sentment Analysis tool, which difficult to distinguish minimal
+change of emotion. As a results, this testing model will missing most of Machine
+Translation failures, particularly, neutral emotional sentences. This tesing
+model is good for decideing strong emotion sentences translation correctness.
+Accounding to failures of machine translated sentence. The main problem is all
+of three translation services have get the individual words are not properly
+selected and the language expression does not conform to the natural speaking.
+They do not recognize the characteristics of colloquial text. Some of the
+mistranslations are almost overlap. So it is not possible to correctly handle
+the special meaning of certain common words in a particular text. And the
+colloquial language of movie comments should adopt different translation methods
+in order to perfect the content of the translation. It is still necessary to
+strengthen the processing of sentence structure and translation expression.
+
 \section{future work}
 Due to the differences way of thinking between Chinese and English languages. In
-addition, cultural differences and the limitation of translation corpus.
-Machine translation tools have serious language problems. Machine translation
+addition, cultural differences and the limitation of translation corpus. Machine
+translation tools have serious language problems. Machine translation
 researchers must be work with linguistic researchers, who should be paid more
 attention to the corpus, lexical analysis and grammatical analysis.
-
-\section{consideration and suggestion}
 

### 2019-02-01 icse/paper.tex
backup 01.02 12:32

@@
 Social Media has been becoming more and more widely used.
-Accounting to Perrin’s survey, there are only $7%$ American adults are use
+Accounting to Perrin's survey, there are only $7\%$ of American adults are use
 social media in 2005. However, social media usage increase rapidly, there are
-$65%$ American adults are use social media until 2015 \cite{perrin2015social}.
+$65\%$ American adults are use social media until 2015 \cite{perrin2015}.
 Social Media website comment text from the language word level has its unique
@@
 and 50, from negative to positive.
-The test sample distribution diagram on below.
-\begin{figure}[h]
+The test sample distribution diagram on below.\\
+\begin{wrapfigure}
   \centering
   \includegraphics[width=0.3\paperwidth]{./img/ratingHis.png}
-\caption{User Rating Histogram}
   \label{fig:userRatingHistogram}
-\end{figure}
+\end{wrapfigure}\\
+
 As you can see, the majority of comments allocate on rating 30. In addition,
@@
     than -0.6 (mean False). The decideing True table on below.\\
-     \begin{table}[h]
+     \begin{table}[h!]
       \caption {The Range of Score: True/ False}
@@
 \subsubsection{Sequence Disorder}
+\begin{itemize}
+\item Chinese \underline{Origin Movie comment} is:
+  \begin{center}
     ``想过是烂片，只是没想到能烂到这种地步，太应付了，一个星期拍完的吧''
-Google
-``Think of a bad movie, but did not expect to be able to rot to this point, too
-coping, a week finished it''
-Yandex
+  \end{center}
+\item The \underline{correct of the translation} is:\\
+  ``I was have thought this is worse movie, but did not think it could be worse
+  like this. It's working perfunctorily. Is it only using one week to finish all?''
+\item The \underline{Google Translation} is:\\
+  ``Think of a bad movie, but did not expect to be able to rot to this point,
+  too coping, a week finished it''
+\item The \underline{Yandex Translation} is:\\
   ``Thought is a bad film, just didn't think it could be rotten to the point where
 too cope with, a week finished.''
-baidu
+\item The \underline{Baidu Translation} is:\\
   ``That is a bad film, but did not expect to come to this rotten, too for a week, finished.''
+\end{itemize}
+This is not only have professional terms word translation problem. This
+translation have incomplete sentence composition and confusion of words order.
 
-The problem of sentence structure.Incomplete sentence composition, confusion of
-words order.
-
-For example, original sentence meaning”A few small cups of grape
-juice, it is not very fresh”.GoogleTranslation ”A few small cups of grape juice,
-very fresh”in completely different meaning;
-
-Take another example,original
-sentence meaning “ The first story is good, but the other is too
-contrived”.
-YandexTranslation”On the first story good the other is too
-contrived”;
-
-Besides,For example,original sentence meaning “The first half was
-good with heavy irony, but the last apology was a little
-redundant”.
-
-BaiduTranslation”The first half was good - the irony was very heavy,
-and the last apology was a little redundant”. Improper location of clauses”-”.
-The misuse of conjunctions”and”.
-
-The problem of sentence structure.Causality is unclear. For example,original
-sentence meaning "I can not ignorant conscience to give too few stars,because I
-am a gentle person”.GoogleTranslation "I am a gentle person, and I really do not
-have the heart to give too few stars. . .”
-
-Take another example,original sentence meaning “Bad,I will never see Feng
-Xiaogang's movie again.”  YandexTranslation “Sucks, feel Feng Xiaogang movie
-later never to see.”
-
-从以上以豆瓣电影评论为分析对象来讨论这三个翻译软件的译文共同的问题，从整体上看，
-无论是用词还是语法都一定的错误导致许多译文意思不准确，内容残缺，结构错误。
-
- From the overall points of view, above the Douban film review as the analysis
- object to discuss GoogleTranslation, YandexTranslation and BaiduTranslation
- tools common problems, whether the usage of words or grammar are a certain
+From the overall points of view, above of movie comments as the analysis
+object to discuss Google Translation, Yandex Translation and Baidu Translation
+tools have got common problems. The usage of words or grammar are a certain
 error caused by many translation inaccurate meaning, incomplete content, and
@@
 
- The reasons are colloquial language characters of Douban film review text and
- insufficient machine vocabulary.Although the length of the movie commentary
- sentences is short, the vocabulary is not difficult and the sentences’structure
- seems simple, there have got lots of colloquial speech and many of words are
- not formal, which is the main reason for the low quality of translation
- results. Lots of compound sentence is hidded. It is more difficult for
- intelligent machines translation services.Although the length of the movie
- commentary sentences is short, the vocabulary is not difficult and the
- sentences’structure seems simple, there have got lots of colloquial speech and
- many of words are not formal, which is the main reason for the low quality of
- translation results. Lots of compound sentence is hidded. It is more difficult
- for intelligent machines translation services.
-
- Although the length of the movie commentary sentences is short, the vocabulary
-is not difficult and the sentences' structure seems simple, there have got
-lots of colloquial speech and many of words are not formal, which is the main
-reason for the low quality of translation results. Lots of compound
-sentence is hidded. It is more difficult for intelligent machines translation
-services.
-
-Although the online translation text comments and review is short in length, but
+The reasons are colloquial language characters of Douban film review comments and
+insufficient machine translation vocabulary collection library. Although the
+online translation text comments and review is short in length, but
 more colloquial is serious, the use of words is not standard, so vocabulary
-translation is more difficult.Although the sentence structure seems simple, but
+translation is more difficult. Although the sentence structure seems simple, but
 hides the compound sentence, but the sentence pattern is rich and
-complex.Besides,Differences in thinking between Chinese and English is more
+complex. Besides,Differences in thinking between Chinese and English is more
 difficult for intelligent machines, which is the main difficulty in the quality
